### 2022-03-02 demo-eswc22/paper.tex
first cut of the eswc demo paper

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
%\usepackage{fullpage}
%\usepackage{setspace}
%\onehalfspacing
\usepackage{listings}
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{BLAST: Block Applications for Things}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Michael Freund\inst{1}\orcidID{0000-0003-1601-9331} \and
Thomas Wehr\inst{1}\orcidID{0000-0002-0678-5019} \and
Andreas Harth\inst{1,2}\orcidID{0000-0002-0702-510X}}
%
\authorrunning{M. Freund et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Fraunhofer Institute for Integrated Circuits IIS, Nürnberg, Germany 
\email{firstname.lastname@iis.fraunhofer.de}\\
\and
Friedrich–Alexander University Erlangen-Nürnberg, Nürnberg, Germany}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  An open research challenge in the deployment of digital twins is the interaction with humans.
  To facilitate this, we have created a digital twin based on Web of Things technology and a block-based visual programming language and execution environment called BLAST.
  We show that BLAST can be used to create programs that interact with a digital twin and IoT devices to control and monitor a process.

\keywords{Block-based Programming \and Web of Things.}
\end{abstract}
%
%
%
\setcounter{footnote}{0}
\section{Introduction}
IoT devices can be used for state monitoring, energy consumption analysis, simulation and intelligent optimization \cite{CIMINO2019103130}.
However, there are still some research challenges that need to be overcome.
According to Semeraro et al. \cite{SEMERARO2021103469}, the main research challenges in implementing a DT are in the areas of architecture, interoperability, and  interaction capabilities.

Architecture refers to the fact that no design standard currently exists, so different DTs use varying technologies, interfaces, and communication protocols.
A reference architecture could contribute to the flexibility and reusability of DTs.
Interoperability includes a DT's ability to capture a multi-stage product lifecycle, which requires collecting data from external sources and from other companies.
However, to achieve this, data exchange between multiple DTs must be enabled.
The area of interaction capabilities refers to the fact that Digital Twins will not be involved in any important decisions without humans. Therefore, humans should find it easy to interact with DTs. 
Some other authors have also suggested that human-computer interaction is an open research question that needs to be resolved before widespread deployment of DTs in industry \cite{KUEHNER20211227}.

In this paper, we want to address the problem of human-digital twin interaction.
Semeraro et al. \cite{SEMERARO2021103469} propose in this context to focus on the development of the Digital Twin so that it is able to interact smoothly with humans.
Our proposed solution follows this approach.
We have described a digital twin using RDF and ontologies in human and machine-readable form.
However, our solution includes another perspective to improve human-DT interaction.
We developed an easy-to-use interaction interface for humans with digital twins based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}}.
To show the feasibility of this approach, we developed and implemented a demonstrator for a commissioning process as a proof of concept.

\section{Block-based Visual Programming}
The programming languages currently in use are primarily text-based and are difficult to access for laypersons without prior knowledge.
One possible approach to improve accessibility and simplify the creation of computer programs are so-called Visual Programming Languages (VPL).
VPLs do not require the user to enter any text, they are instead based on graphical elements like blocks, tables or diagrams.
Programs are created by arranging the available graphical elements in the correct order.
The block-based approach of VPLs has become established in recent years, especially as an entry point for novice programmers.

Bau et al. \cite{1011453015455} pointed out that block-based programming languages teach programming concepts in a simple way due to an intuitive and friendly user interface and that after using block-based languages it is much easier for users to switch to traditional text-based languages.

The basic idea of the block-based approach is that predefined blocks with images or text are arranged into programs by using the drag-and-drop principle.
Blocks can be geometrically aligned with other compatible blocks, like in a jigsaw puzzle, to form complex programs.
Since blocks can only be arranged in the correct way, no syntax errors can occur \cite{10.11453341221}.
The created block programs can be translated into any predefined programming language, resulting in a normal source code. 
The block-based approach can be used not only for learning programming concepts, but also for more complex problems.
For example, it has been shown that block languages can be successfully used in programming industrial robots \cite{8120406} or executing SPARQL queries \cite{7369012}.
Both areas, which normally require advanced programming skills.

\section{BLAST - Block Applications For Things}
Due to the success of block-based languages in different challenging areas, we have developed our own block language based on Google's Blockly\footnote{https://developers.google.com/blockly} library.
Blockly is a pure JavaScript library for creating block-based languages and editors.
Our block-based language simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols such as Bluetooth or HTTP.
We have named our block language ''Block Applications For Things'', or BLAST for short (See figure \ref{fig1}).
The browser-based BLAST uses web Bluetooth to communicate with IoT devices, custom control and command blocks, and generates JavaScript code that can be used by any JavaScript interpreter.
To interact with the IoT devices, BLAST requires custom drivers for each device, which represent an extended form of the WoT TD and contain the metadata and interaction affordances as well as the JavaScript code needed for communication.

\begin{figure}
\includegraphics[width=\textwidth]{BL2.PNG}
\caption{Graphical user interface of the BLAST programming environment.} \label{fig1}
\end{figure}

When choosing the vocabulary for our block-based language BLAST, we resorted to a mixture of natural language and computer language \cite{8120404}.
This means that in BLAST, the blocks are arranged into readable sentences, as in a natural language, but the blocks also contain a few technical programming terms, such as ''repeat while true'' instead of ''forever''.
This makes the BLAST vocabulary both understandable for beginners, but still flexible.

BLAST includes standards from other programming languages such as loops, functions, and variables, but also WoT and IoT related blocks that can be grouped under the three interaction affordances Properties, Actions, and Events.
Properties of connected IoT devices can be read and written, actions refer to long-running processes that can be initiated and events are asynchronous and based on the ''Event Conditon Action'' (ECA) rule.
If an event occurs, the condition is checked and if necessary the corresponding action is executed.
Furthermore, it is possible to send HTTP requests with arbitrary header and body or load knowledge graphs from a URI and execute SPARQL queries on the records, which allows interaction with read-write linked data APIs or other REST APIs.
If the available blocks are not sufficient to implement a desired functionality, there is a block in which native JavaScript code can be entered.
This block makes almost everything that is possible in JavaScript also possible in BLAST.

\section{Supported Devices and Services}

To demonstrate how BLAST can interact with WoT devices, we provide a Web of Things abstraction over devices communicating with Bluetooth Low Energy and USB HID.
We also provide access to online APIs related to speech input and output.

\begin{center}
\begin{tabular}{ |c|c|c| } 
 \hline
 cell1 & cell2 & cell3 \\ 
 cell4 & cell5 & cell6 \\ 
 cell7 & cell8 & cell9 \\ 
 \hline
\end{tabular}
\end{center}

\section{Conclusion}
As IoT devices become more and more relevant in the industrial environment, it is essential to investigate how the interaction between humans and the IoT devices can be seamlessly implemented.
So far, papers have tended to take the approach of simplifying the programming of devices.

In contrast, the solution proposed in this paper incorporates another perspective, the user perspective.
In addition to creating a digital twin in human- and machine-readable form based on Semantic Web technologies, we explored the use of an easy-to-use block-based programming environment to interact with devices.
For this purpose, we built a demonstrator based on Lego. Using the picking process depicted by the demonstrator, we were able to use BLAST control and simultaneously monitor the running process.
With the help of the experimental setup, we were able to demonstrate that block-based languages are fundamentally suitable for interacting with DTs and IoT devices.
In testing the performance of BLAST, we also found that the execution speed is slower, but only by 51,04 percent.
Based on the accessibility and usability benefits, the approach of using block languages to interact with DTs should be pursued.

We are currently working on a way to execute the created BLAST program independently of browsers.
To this end, we are developing an execution environment that can load BLAST programs, convert them to JavaScript, and execute them as a server.
In the future, it would enrich BLAST if there was a way to consume WoT TDs and derive interaction possibilities, which would allow BLAST to interact with any WoT device.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{references}
%

\end{document}

### 2022-03-02 demo-eswc22/paper.tex
added notes

@@
 
-To demonstrate how BLAST can interact with WoT devices, we provide a Web of Things abstraction over devices communicating with Bluetooth Low Energy and USB HID.
+To demonstrate how BLAST can interact with WoT devices, we provide a Web of Things abstraction over devices communicating with Bluetooth Low Energy and USB Human Interface Device (HID) Class.
 We also provide access to online APIs related to speech input and output.
@@
 
+@@@Web Bluetooth has certain restrictions (security, reading RSSI), server should not have these restrictions.
+
 %

### 2022-03-03 examples/web/dist/app.js
remove console.log

@@ -36996,7 +36996,6 @@ const startEventChecker = function() {
   
   // Initiate States interpreter.
   stateInterpreter = new Interpreter('');
-  console.log(stateInterpreter);
   stateInterpreter.getStateStack()[0].scope = (0,_blast_interpreter_js__WEBPACK_IMPORTED_MODULE_1__.getInterpreter)().getGlobalScope();
   stateInterpreter.appendCode(latestCode);
 

### 2022-03-03 src/blast_states_interpreter.js

@@ -94,7 +94,6 @@ const startEventChecker = function() {
   
   // Initiate States interpreter.
   stateInterpreter = new Interpreter('');
-  console.log(stateInterpreter);
   stateInterpreter.getStateStack()[0].scope = getInterpreter().getGlobalScope();
   stateInterpreter.appendCode(latestCode);
 

### 2022-03-03 examples/web/dist/app.js
add stdinfo output to stopJs

@@ -36448,6 +36448,7 @@ const resetInterpreter = function() {
 const stopJS = function() {
   resetInterpreter();
   setStatus(statusValues.STOPPED);
+  stdInfo('execution stopped');
 };
 
 /**

### 2022-03-03 src/blast_interpreter.js

@@ -306,6 +306,7 @@ export const resetInterpreter = function() {
 export const stopJS = function() {
   resetInterpreter();
   setStatus(statusValues.STOPPED);
+  stdInfo('execution stopped');
 };
 
 /**

### 2022-03-03 demo-eswc22/paper.tex
add text, references and comments

@@
 % be included in EPS format.
+\usepackage{makecell}
 %
@@
 The programming languages currently in use are primarily text-based and are difficult to access for laypersons without prior knowledge.
-One possible approach to improve accessibility and simplify the creation of computer programs are so-called Visual Programming Languages (VPL).
-VPLs do not require the user to enter any text, they are instead based on graphical elements like blocks, tables or diagrams.
+One possible approach to improve accessibility and simplify the creation of computer programs is so-called Visual Programming (VP).
+% Falls Platz dafür ist, die Definition für VP fand ich besser:
+VP as defined by Myers \cite{myers1990taxonomies} refers to any system that allows the user to specify a program in a two (or more) dimensional fashion.
+Conventional textual languages are not considered two dimensional since the compiler or interpreter processes it as a long, one-dimensional stream.
+For a more in-depth definition of VP, the reader is referred to \cite{burnett1995visual}.
+VP does not require the user to enter any text, it is instead based on graphical elements like blocks, graphs, tables or diagrams.
 Programs are created by arranging the available graphical elements in the correct order.
-The block-based approach of VPLs has become established in recent years, especially as an entry point for novice programmers.
+The block-based approach of VP has become established in recent years, especially as an entry point for novice programmers 
+% Vorschläge für Referenzen
+\cite{moors2018transitioning} \cite{weintrop2017blocks} \cite{chao2016exploring} \cite{HUNDHAUSEN200722} \cite{10.1145/2787622.2787712}.
 
@@
 Blocks can be geometrically aligned with other compatible blocks, like in a jigsaw puzzle, to form complex programs.
-Since blocks can only be arranged in the correct way, no syntax errors can occur \cite{10.11453341221}.
+Since blocks can only be arranged in the correct way, no syntax errors can occur \cite{10.11453341221} \cite{maloney2010scratch} \cite{10.1145/1089733.1089734} \cite{lye2014review}.
 The created block programs can be translated into any predefined programming language, resulting in a normal source code. 
 The block-based approach can be used not only for learning programming concepts, but also for more complex problems.
-For example, it has been shown that block languages can be successfully used in programming industrial robots \cite{8120406} or executing SPARQL queries \cite{7369012}.
+For example, it has been shown that block languages can be successfully used in programming industrial robots \cite{8120406} \cite{ghazal2016framework} \cite{tomlein2017visual} or executing SPARQL queries \cite{7369012}.
 Both areas, which normally require advanced programming skills.
+Furthermore, Ray examined the use of block-based programming languages for IoT devices in \cite{ray2017survey} and concluded that IoT seems to be suitably getting empowered by smooth entanglement and promotion with promising reduction in physical-digital interface.
+%Das ist ein direktes Zitat, muss man das anders schreiben?
 
 \section{BLAST - Block Applications For Things}
-Due to the success of block-based languages in different challenging areas, we have developed our own block language based on Google's Blockly\footnote{https://developers.google.com/blockly} library.
+Due to the success of block-based languages in different challenging areas, we have developed our own block language based on Google's Blockly\footnote{https://developers.google.com/blockly/} library.
+%Momentan zweimal die gleiche Fußnote auf einer Seite.
 Blockly is a pure JavaScript library for creating block-based languages and editors.
@@
 The browser-based BLAST uses web Bluetooth to communicate with IoT devices, custom control and command blocks, and generates JavaScript code that can be used by any JavaScript interpreter.
-To interact with the IoT devices, BLAST requires custom drivers for each device, which represent an extended form of the WoT TD and contain the metadata and interaction affordances as well as the JavaScript code needed for communication.
+To interact with the IoT devices, BLAST requires custom drivers for each device, which represent an extended form of the WoT TD % Beides noch nicht definiert
+ and contain the metadata and interaction affordances as well as the JavaScript code needed for communication.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{BL2.PNG}
+\includegraphics[width=\textwidth]{Blast Screenshot.png}%im Ordner sind noch 2 alternative Screenshots
 \caption{Graphical user interface of the BLAST programming environment.} \label{fig1}
@@
 
+The currently best known tool for programming IoT devices using VP is Node-Red\footnote{https://nodered.org/}.
+Other than BLAST, Node-Red employs a flow-based programming paradigm, and therefore displays applications as graphs.
+The nodes in these graphs are black box processes, created by the developers, that can be connected to each other by the end user.
+The block-based approach utilized by BLAST provides more flexibility as its blocks are a lot more fine grained.
+Also, Node-Red does not implement the WoT standard, which hinders re-usability of code with applications other than Node-Red.
+Another application similiar to BLAST is Punya\cite{patton2021punya} an Android App development Application based on the MIT App Inventor\footnote{https://appinventor.mit.edu/}.
+Like Blast, Punya offers a block-based programming environment able to run SPARQL queries and utilizes services like sending a tweet.
+But Punya focuses on creating applications for Android devices only and solely communicates with the device's internal hardware.
+Other than BLAST, Punya apps are capable of working as a LDP-CoAP client to publish and access data on CoAP servers.
+
 \section{Supported Devices and Services}
 
-To demonstrate how BLAST can interact with WoT devices, we provide a Web of Things abstraction over devices communicating with Bluetooth Low Energy and USB Human Interface Device (HID) Class.
-We also provide access to online APIs related to speech input and output.
+To demonstrate how BLAST can interact with WoT devices, we provide a Web of Things abstraction for devices communicating with Bluetooth Low Energy and USB Human Interface Devices (HID).
+We also provide access to online APIs related to speech input and output and services like playing audio from a URI or invoking SPARQL queries on an online ressource.
 
 \begin{center}
-\begin{tabular}{ |c|c|c| } 
+  \begin{tabular}{|c|c|c|}
   \hline
- cell1 & cell2 & cell3 \\ 
- cell4 & cell5 & cell6 \\ 
- cell7 & cell8 & cell9 \\ 
+  Device & Communication & WoT interactions \\
+  \hline
+  Eddystone Devices & BLE GATT & read/write Eddystone properties \\
+  HuskyLens\footnote{https://wiki.dfrobot.com/HUSKYLENS\_V1.0\_SKU\_SEN0305\_SEN0336} & BLE GATT & read sensor properties, invoke forget action \\
+  RGB LED Controller\footnote{https://aliexpress.com/item/4000208329326.html} & BLE GATT & write color properties \\
+  RuuviTag\footnote{https://ruuvi.com/ruuvitag/} & BLE GATT & \makecell{read sensor properties, read battery property, \\
+  read/write txPower property, \\
+  read movement counter propert,y \\
+  read measurement sequence counter property} \\
+  StreamDeck\footnote{https://www.streamdeck.com/} & USB HID & \makecell{write display properties, \\ subscribe to button push events} \\
+  Tulogic BlinkStick\footnote{https://www.blinkstick.com/} & USB HID & write color properties \\ 
+  Nintendo JoyCon\footnote{https://www.nintendo.com/switch/tech-specs/\#joycon-section} & USB HID \& BLE GATT & \makecell{read sensor properties,\\ subscribe to button push events} \\
+  Xiaomi Thermometer\footnote{https://xiaomipedia.com/en/p/xiaomi-electronic-thermometer-and-hygrometer/} & BLE GATT & read sensor properties \\
+  \hline
+  \end{tabular}
+
+  \begin{tabular}{|c|c|}
+  \hline
+  Service & WoT interactions \\
+  \hline
+  Camera & invoke capture image action \\
+  Audio & invoke play audio action \\ % TODO
+  WebSpeech API & invoke text to speech action, invoke speech to text action \\
+  HTTP Requests & invoke send HTTP request action \\
+  SPARQL Query & invoke execute SPARQL query action \\
+  SOLID & invoke upload to solid container action \\
   \hline

### 2022-03-04 demo-eswc22/paper.tex
Fix tables

@@
 \usepackage{makecell}
+\renewcommand\theadfont{\bfseries}
 %
@@
   \hline
-  Device & Communication & WoT interactions \\
+  \thead{Device} & \thead{Communication} & \thead{WoT interactions} \\
   \hline
   Eddystone Devices & BLE GATT & read/write Eddystone properties \\
+  \hline
   HuskyLens\footnote{https://wiki.dfrobot.com/HUSKYLENS\_V1.0\_SKU\_SEN0305\_SEN0336} & BLE GATT & read sensor properties, invoke forget action \\
+  \hline
   RGB LED Controller\footnote{https://aliexpress.com/item/4000208329326.html} & BLE GATT & write color properties \\
-  RuuviTag\footnote{https://ruuvi.com/ruuvitag/} & BLE GATT & \makecell{read sensor properties, read battery property, \\
+  \hline
+  RuuviTag\footnote{https://ruuvi.com/ruuvitag/} & BLE GAP & \makecell{read sensor properties, read battery property, \\
   read/write txPower property, \\
@@
   read measurement sequence counter property} \\
+  \hline
   StreamDeck\footnote{https://www.streamdeck.com/} & USB HID & \makecell{write display properties, \\ subscribe to button push events} \\
+  \hline
   Tulogic BlinkStick\footnote{https://www.blinkstick.com/} & USB HID & write color properties \\ 
+  \hline
   Nintendo JoyCon\footnote{https://www.nintendo.com/switch/tech-specs/\#joycon-section} & USB HID \& BLE GATT & \makecell{read sensor properties,\\ subscribe to button push events} \\
-  Xiaomi Thermometer\footnote{https://xiaomipedia.com/en/p/xiaomi-electronic-thermometer-and-hygrometer/} & BLE GATT & read sensor properties \\
+  \hline
+  Xiaomi Thermometer\footnote{https://xiaomipedia.com/en/p/xiaomi-electronic-thermometer-and-hygrometer/} & BLE GAP & read sensor properties \\
   \hline
@@
   \hline
-  Service & WoT interactions \\
+  \thead{Service} & \thead{WoT interactions} \\
   \hline
   Camera & invoke capture image action \\
-  Audio & invoke play audio action \\ % TODO
+  \hline
+  Audio & invoke play audio action \\
+  \hline
   WebSpeech API & invoke text to speech action, invoke speech to text action \\
+  \hline
   HTTP Requests & invoke send HTTP request action \\
+  \hline
   SPARQL Query & invoke execute SPARQL query action \\
+  \hline
   SOLID & invoke upload to solid container action \\

### 2022-03-04 demo-eswc22/paper.tex
change screenshot, add description

@@
 \begin{figure}
-\includegraphics[width=\textwidth]{Blast Screenshot.png}%im Ordner sind noch 2 alternative Screenshots
-\caption{Graphical user interface of the BLAST programming environment.} \label{fig1}
+\includegraphics[width=\textwidth]{screenshot.png}%im Ordner sind noch 2 alternative Screenshots
+\caption{Example BLAST program} \label{fig1}
 \end{figure}
@@
 This makes the BLAST vocabulary both understandable for beginners, but still flexible.
+Take the program in Figure \ref{fig1} as an example.
+One should easily figure out that it is used to toggle a Bluetooth LED light.
+Every time the user pushes the top-left button on their StreamDeck down, the LED light is toggled between red and off.
 

### 2022-03-07 demo-eswc22/paper.tex
started iterating over the paper

@@
 \begin{abstract}
-  An open research challenge in the deployment of digital twins is the interaction with humans.
-  To facilitate this, we have created a digital twin based on Web of Things technology and a block-based visual programming language and execution environment called BLAST.
-  We show that BLAST can be used to create programs that interact with a digital twin and IoT devices to control and monitor a process.
-
+  An open research challenge in the deployment of IoT devices is the interaction with humans.
+  We introduce a block-based visual programming language and execution environment called BLAST.
+  BLAST allows for visually creating programs involving devices with a Web of Things interface.
+  We demonstrate that BLAST can be used to create programs that interact with a variety of devices in different scenarios.
 \keywords{Block-based Programming \and Web of Things.}
@@
 \section{Introduction}
-IoT devices can be used for state monitoring, energy consumption analysis, simulation and intelligent optimization \cite{CIMINO2019103130}.
+IoT devices form the basis for a variety of applications, such as condition monitoring, energy consumption analysis, simulation and optimisation~\cite{CIMINO2019103130}.
 However, there are still some research challenges that need to be overcome.
-According to Semeraro et al. \cite{SEMERARO2021103469}, the main research challenges in implementing a DT are in the areas of architecture, interoperability, and  interaction capabilities.
+Interaction capabilities refer to the fact that devices will not be involved in any important decisions without humans.
+In this paper, we focus on the challenge of humans interacting with devices, a challenge that needs to be resolved to achieve a widespread deployment of IoT devices in industry~\cite{KUEHNER20211227}.
+Thus, humans should find it easy to interact with devices and the devices should be able to interact smoothly with humans.
 
-Architecture refers to the fact that no design standard currently exists, so different DTs use varying technologies, interfaces, and communication protocols.
-A reference architecture could contribute to the flexibility and reusability of DTs.
-Interoperability includes a DT's ability to capture a multi-stage product lifecycle, which requires collecting data from external sources and from other companies.
-However, to achieve this, data exchange between multiple DTs must be enabled.
-The area of interaction capabilities refers to the fact that Digital Twins will not be involved in any important decisions without humans. Therefore, humans should find it easy to interact with DTs. 
-Some other authors have also suggested that human-computer interaction is an open research question that needs to be resolved before widespread deployment of DTs in industry \cite{KUEHNER20211227}.
+We assume that the interoperability challenge, that is, a devices' ability to capture a multi-stage product lifecycle, which requires collecting and integrating data from multiple devices and sources~\cite{SEMERARO2021103469}, has been addressed by the use of the Web of Things abstraction.
 
-In this paper, we want to address the problem of human-digital twin interaction.
-Semeraro et al. \cite{SEMERARO2021103469} propose in this context to focus on the development of the Digital Twin so that it is able to interact smoothly with humans.
-Our proposed solution follows this approach.
-We have described a digital twin using RDF and ontologies in human and machine-readable form.
-However, our solution includes another perspective to improve human-DT interaction.
-We developed an easy-to-use interaction interface for humans with digital twins based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}}.
-To show the feasibility of this approach, we developed and implemented a demonstrator for a commissioning process as a proof of concept.
+We present BLAST (Block Applications for Things), an easy-to-use interaction interface for humans with devices following the Web of Things interface based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}}.
+BLAST is a programming language with a focus on control flow constructs.
+
+We first overview block-based visual programming approaches, next introduce BLAST with a scenario involving multiple devices, list the currently supported devices and services and conclude with a summary and outlook.
 
 \section{Block-based Visual Programming}
+
 The programming languages currently in use are primarily text-based and are difficult to access for laypersons without prior knowledge.
@@
 The block-based approach can be used not only for learning programming concepts, but also for more complex problems.
-For example, it has been shown that block languages can be successfully used in programming industrial robots \cite{8120406} \cite{ghazal2016framework} \cite{tomlein2017visual} or executing SPARQL queries \cite{7369012}.
-Both areas, which normally require advanced programming skills.
+For example, block languages have been successfully used in programming industrial robots \cite{8120406} \cite{ghazal2016framework} \cite{tomlein2017visual} or executing SPARQL queries \cite{7369012}, both areas which normally require advanced programming skills.
+
 Furthermore, Ray examined the use of block-based programming languages for IoT devices in \cite{ray2017survey} and concluded that IoT seems to be suitably getting empowered by smooth entanglement and promotion with promising reduction in physical-digital interface.
@@
 
+The currently best known tool for programming IoT devices using visual programming is Node-RED\footnote{\url{https://nodered.org/}}.
+Other than BLAST, Node-RED employs a flow-based programming paradigm, and therefore displays applications as graphs.
+The nodes in these graphs are black box processes, created by the developers, that can be connected to each other by the end user.
+The block-based approach utilized by BLAST provides more flexibility as its blocks are a lot more fine grained.
+
+Another application similiar to BLAST is Punya\cite{patton2021punya}, an Android App development Application based on the MIT App Inventor\footnote{\url{https://appinventor.mit.edu/}}.
+Like BLAST, Punya offers a block-based programming environment able to run SPARQL queries and utilizes services like sending a tweet.
+But Punya focuses on creating applications for Android devices only and solely communicates with the device's internal hardware.
+Other than BLAST, which supports devices with a Web of Things interface, Punya apps are capable of working as a LDP-CoAP client to publish and access data on CoAP servers.
+
 \section{BLAST - Block Applications For Things}
-Due to the success of block-based languages in different challenging areas, we have developed our own block language based on Google's Blockly\footnote{https://developers.google.com/blockly/} library.
+Due to the success of block-based languages in different challenging areas, we have developed our own block language based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}} library.
 %Momentan zweimal die gleiche Fußnote auf einer Seite.
@@
 This block makes almost everything that is possible in JavaScript also possible in BLAST.
-
-The currently best known tool for programming IoT devices using VP is Node-Red\footnote{https://nodered.org/}.
-Other than BLAST, Node-Red employs a flow-based programming paradigm, and therefore displays applications as graphs.
-The nodes in these graphs are black box processes, created by the developers, that can be connected to each other by the end user.
-The block-based approach utilized by BLAST provides more flexibility as its blocks are a lot more fine grained.
-Also, Node-Red does not implement the WoT standard, which hinders re-usability of code with applications other than Node-Red.
-Another application similiar to BLAST is Punya\cite{patton2021punya} an Android App development Application based on the MIT App Inventor\footnote{https://appinventor.mit.edu/}.
-Like Blast, Punya offers a block-based programming environment able to run SPARQL queries and utilizes services like sending a tweet.
-But Punya focuses on creating applications for Android devices only and solely communicates with the device's internal hardware.
-Other than BLAST, Punya apps are capable of working as a LDP-CoAP client to publish and access data on CoAP servers.
 

### 2022-03-07 demo-eswc22/paper.tex
update

@@
   BLAST allows for visually creating programs involving devices with a Web of Things interface.
-  We demonstrate that BLAST can be used to create programs that interact with a variety of devices in different scenarios.
+  We demonstrate that BLAST can be used to create programs that interact with a variety of devices in a geofencing scenario.
 \keywords{Block-based Programming \and Web of Things.}
@@
 BLAST is a programming language with a focus on control flow constructs.
+BLAST implements the Web of Things abstraction to devices with Bluetooth Low Energy (BLE) and USB Human Interface Devices (HID) interface and to various browser APIs that allow for accessing HTTP APIs.
+These devices and APIs are supported by modern web browsers.
 
@@
 \section{BLAST - Block Applications For Things}
+
 Due to the success of block-based languages in different challenging areas, we have developed our own block language based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}} library.

### 2022-03-07 demo-eswc22/paper.tex
paper is feature complete

@@
 We present BLAST (Block Applications for Things), an easy-to-use interaction interface for humans with devices following the Web of Things interface based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}}.
-BLAST is a programming language with a focus on control flow constructs.
+Blockly is a pure JavaScript library for creating block-based languages and editors.
 BLAST implements the Web of Things abstraction to devices with Bluetooth Low Energy (BLE) and USB Human Interface Devices (HID) interface and to various browser APIs that allow for accessing HTTP APIs.
 These devices and APIs are supported by modern web browsers.
+The Web of Thing abstraction involves Things and their Properties that can be read and written, their Actions that can be invoked and their Events that can be observed.
+
+The currently best known tool for programming IoT devices using visual programming is Node-RED\footnote{\url{https://nodered.org/}}.
+In contrast to BLAST, which focuses on control flow constructs, Node-RED's programming paradigm is based on dataflows.
+The use cases we envision for BLAST involve mostly control flow, and in such scenarios a dataflow abstraction can lead to programs that are difficult to understand and maintain.
+%The nodes in these graphs are black box processes, created by the developers, that can be connected to each other by the end user.
+%The block-based approach utilized by BLAST provides more flexibility as its blocks are a lot more fine grained.
+%BLAST is a programming language with a
+
+Another system similiar to BLAST is Punya~\cite{patton2021punya}, an Android app development system based on the MIT App Inventor\footnote{\url{https://appinventor.mit.edu/}}.
+Like BLAST, Punya offers a block-based programming environment able to run SPARQL queries and include online services.
+Punya focuses on creating applications for Android devices only and communicates with the device's internal hardware, in addition to working as a LDP-CoAP client to publish and access data on CoAP servers.
+BLAST, on the other hand, runs in modern web browsers and supports devices based on a Web of Things abstraction.
 
@@
 
-The programming languages currently in use are primarily text-based and are difficult to access for laypersons without prior knowledge.
-One possible approach to improve accessibility and simplify the creation of computer programs is so-called Visual Programming (VP).
+%The programming languages currently in use for accessing devices are primarily text-based and are difficult to access for casual users.
+%One possible approach to improve accessibility and simplify the creation of computer programs is so-called Visual Programming (VP).
 % Falls Platz dafür ist, die Definition für VP fand ich besser:
-VP as defined by Myers \cite{myers1990taxonomies} refers to any system that allows the user to specify a program in a two (or more) dimensional fashion.
+Visual programming refers to any system that allows the user to specify a program in a two (or more) dimensional fashion~\cite{myers1990taxonomies}.
 Conventional textual languages are not considered two dimensional since the compiler or interpreter processes it as a long, one-dimensional stream.
-For a more in-depth definition of VP, the reader is referred to \cite{burnett1995visual}.
-VP does not require the user to enter any text, it is instead based on graphical elements like blocks, graphs, tables or diagrams.
-Programs are created by arranging the available graphical elements in the correct order.
-The block-based approach of VP has become established in recent years, especially as an entry point for novice programmers 
+%For a more in-depth definition of VP, the reader is referred to \cite{burnett1995visual}. 
+Visual programming does not require the user to enter any text; instead, programs are based on graphical elements like blocks, graphs, tables or diagrams.
+Programs are created by arranging predefined blocks with images or text are arranged into programs via a drag-and-drop interface.
+Blocks can be geometrically aligned with other compatible blocks, like in a jigsaw puzzle, to form complex programs.
+Since blocks can only be arranged in the correct way, no syntax errors can occur~\cite{10.11453341221}~\cite{maloney2010scratch}~\cite{10.1145/1089733.1089734}~\cite{lye2014review}.
+
 % Vorschläge für Referenzen
-\cite{moors2018transitioning} \cite{weintrop2017blocks} \cite{chao2016exploring} \cite{HUNDHAUSEN200722} \cite{10.1145/2787622.2787712}.
+%\cite{moors2018transitioning} \cite{weintrop2017blocks} \cite{chao2016exploring} \cite{HUNDHAUSEN200722} \cite{10.1145/2787622.2787712}.
 
-Bau et al.
+%Bau et al.
 \cite{1011453015455} pointed out that block-based programming languages teach programming concepts in a simple way due to an intuitive and friendly user interface and that after using block-based languages it is much easier for users to switch to traditional text-based languages.
 
-The basic idea of the block-based approach is that predefined blocks with images or text are arranged into programs by using the drag-and-drop principle.
-Blocks can be geometrically aligned with other compatible blocks, like in a jigsaw puzzle, to form complex programs.
-Since blocks can only be arranged in the correct way, no syntax errors can occur \cite{10.11453341221} \cite{maloney2010scratch} \cite{10.1145/1089733.1089734} \cite{lye2014review}.
 The created block programs can be translated into any predefined programming language, resulting in a normal source code. 
 The block-based approach can be used not only for learning programming concepts, but also for more complex problems.
-For example, block languages have been successfully used in programming industrial robots \cite{8120406} \cite{ghazal2016framework} \cite{tomlein2017visual} or executing SPARQL queries \cite{7369012}, both areas which normally require advanced programming skills.
+For example, block languages have been successfully used in programming industrial robots~\cite{8120406}~\cite{ghazal2016framework}~\cite{tomlein2017visual} or executing SPARQL queries~\cite{7369012}, both areas which normally require advanced programming skills.
 
-Furthermore, Ray examined the use of block-based programming languages for IoT devices in \cite{ray2017survey} and concluded that IoT seems to be suitably getting empowered by smooth entanglement and promotion with promising reduction in physical-digital interface.
+%Furthermore, Ray examined the use of block-based programming languages for IoT devices in \cite{ray2017survey} and concluded that IoT seems to be suitably getting empowered by smooth entanglement and promotion with promising reduction in physical-digital interface.
 %Das ist ein direktes Zitat, muss man das anders schreiben?
 
-The currently best known tool for programming IoT devices using visual programming is Node-RED\footnote{\url{https://nodered.org/}}.
-Other than BLAST, Node-RED employs a flow-based programming paradigm, and therefore displays applications as graphs.
-The nodes in these graphs are black box processes, created by the developers, that can be connected to each other by the end user.
-The block-based approach utilized by BLAST provides more flexibility as its blocks are a lot more fine grained.
+\section{BLAST Language and Editor}
 
-Another application similiar to BLAST is Punya\cite{patton2021punya}, an Android App development Application based on the MIT App Inventor\footnote{\url{https://appinventor.mit.edu/}}.
-Like BLAST, Punya offers a block-based programming environment able to run SPARQL queries and utilizes services like sending a tweet.
-But Punya focuses on creating applications for Android devices only and solely communicates with the device's internal hardware.
-Other than BLAST, which supports devices with a Web of Things interface, Punya apps are capable of working as a LDP-CoAP client to publish and access data on CoAP servers.
-
-\section{BLAST - Block Applications For Things}
-
-Due to the success of block-based languages in different challenging areas, we have developed our own block language based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}} library.
-%Momentan zweimal die gleiche Fußnote auf einer Seite.
-Blockly is a pure JavaScript library for creating block-based languages and editors.
+Due to the success of block-based languages in different challenging areas, we have developed our own block language.
 Our block-based language simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols such as Bluetooth or HTTP.
-We have named our block language ''Block Applications For Things'', or BLAST for short (See figure \ref{fig1}).
-The browser-based BLAST uses web Bluetooth to communicate with IoT devices, custom control and command blocks, and generates JavaScript code that can be used by any JavaScript interpreter.
+The browser-based BLAST uses Web Bluetooth to communicate with IoT devices, custom control and command blocks, and generates JavaScript code that can be used by any JavaScript interpreter.
 To interact with the IoT devices, BLAST requires custom drivers for each device, which represent an extended form of the WoT TD % Beides noch nicht definiert
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{screenshot.png}%im Ordner sind noch 2 alternative Screenshots
-\caption{Example BLAST program} \label{fig1}
-\end{figure}
-
 When choosing the vocabulary for our block-based language BLAST, we resorted to a mixture of natural language and computer language \cite{8120404}.
 This means that in BLAST, the blocks are arranged into readable sentences, as in a natural language, but the blocks also contain a few technical programming terms, such as ''repeat while true'' instead of ''forever''.
-This makes the BLAST vocabulary both understandable for beginners, but still flexible.
-Take the program in Figure \ref{fig1} as an example.
-One should easily figure out that it is used to toggle a Bluetooth LED light.
-Every time the user pushes the top-left button on their StreamDeck down, the LED light is toggled between red and off.
+For an example for a BLAST program see figure \ref{fig1}.
+We have also implemented a more complex logistics scenario involving an automated picking line to prepare orders.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{screenshot 3.png}%im Ordner sind noch 2 alternative Screenshots
+\caption{Example BLAST program that implements a geofencing scenario: when the BLE beacon gets close, the LED light is turned off; when the BLE beacon leaves the close range, the LED light is turned red.} \label{fig1}
+\end{figure}
 
@@
 If an event occurs, the condition is checked and if necessary the corresponding action is executed.
-Furthermore, it is possible to send HTTP requests with arbitrary header and body or load knowledge graphs from a URI and execute SPARQL queries on the records, which allows interaction with read-write linked data APIs or other REST APIs.
+Furthermore, it is possible to send HTTP requests with arbitrary header and body or load knowledge graphs from a URI and execute SPARQL queries on the records, which allows interaction with Read-Write Linked Data APIs or other REST APIs.
 If the available blocks are not sufficient to implement a desired functionality, there is a block in which native JavaScript code can be entered.
@@
 
-\section{Supported Devices and Services}
+\section{BLAST Execution Environment}
+
+Supported Devices and Services
 
@@
 \section{Conclusion}
+
 As IoT devices become more and more relevant in the industrial environment, it is essential to investigate how the interaction between humans and the IoT devices can be seamlessly implemented.
-So far, papers have tended to take the approach of simplifying the programming of devices.
-
-In contrast, the solution proposed in this paper incorporates another perspective, the user perspective.
-In addition to creating a digital twin in human- and machine-readable form based on Semantic Web technologies, we explored the use of an easy-to-use block-based programming environment to interact with devices.
-For this purpose, we built a demonstrator based on Lego. Using the picking process depicted by the demonstrator, we were able to use BLAST control and simultaneously monitor the running process.
-With the help of the experimental setup, we were able to demonstrate that block-based languages are fundamentally suitable for interacting with DTs and IoT devices.
-In testing the performance of BLAST, we also found that the execution speed is slower, but only by 51,04 percent.
-Based on the accessibility and usability benefits, the approach of using block languages to interact with DTs should be pursued.
-
+We have explored the use of an easy-to-use block-based programming environment to interact with devices.
 We are currently working on a way to execute the created BLAST program independently of browsers.
 To this end, we are developing an execution environment that can load BLAST programs, convert them to JavaScript, and execute them as a server.
-In the future, it would enrich BLAST if there was a way to consume WoT TDs and derive interaction possibilities, which would allow BLAST to interact with any WoT device.
-
-@@@Web Bluetooth has certain restrictions (security, reading RSSI), server should not have these restrictions.
+%In the future, it would enrich BLAST if there was a way to consume WoT TDs and derive interaction possibilities, which would allow BLAST to interact with any WoT device.
+%@@@Web Bluetooth has certain restrictions (security, reading RSSI), server should not have these restrictions.
 

### 2022-03-07 dist/things/eddystone/EddystoneDevice.js
clean-up: remove redundant checks

@@ -70,18 +70,17 @@ export class EddystoneDevice {
         });
     }
     addPropertyHandlers() {
+        var _a, _b;
         const properties = this.thingModel.properties;
         const propertyKeys = Object.keys(properties);
-        if (this.thing) {
-            for (const p of propertyKeys) {
-                this.thing.setPropertyReadHandler(p, () => {
-                    return readEddystoneProperty(this.webBluetoothId, p);
+        for (const p of propertyKeys) {
+            (_a = this.thing) === null || _a === void 0 ? void 0 : _a.setPropertyReadHandler(p, () => {
+                return readEddystoneProperty(this.webBluetoothId, p);
+            });
+            if (!properties[p].readOnly) {
+                (_b = this.thing) === null || _b === void 0 ? void 0 : _b.setPropertyWriteHandler(p, value => {
+                    return writeEddystoneProperty(this.webBluetoothId, p, value);
                 });
-                if (!properties[p].readOnly) {
-                    this.thing.setPropertyWriteHandler(p, value => {
-                        return writeEddystoneProperty(this.webBluetoothId, p, value);
-                    });
-                }
             }
         }
     }

### 2022-03-07 src/things/eddystone/EddystoneDevice.ts

@@ -1,4 +1,3 @@
-// eslint-disable-next-line node/no-unpublished-import
 import * as WoT from 'wot-typescript-definitions';
 import {
   getActiveSlot,
@@ -85,21 +84,19 @@ export class EddystoneDevice {
   private addPropertyHandlers(): void {
     const properties = this.thingModel.properties;
     const propertyKeys = Object.keys(properties);
-    if (this.thing) {
-      for (const p of propertyKeys) {
-        this.thing.setPropertyReadHandler(p, () => {
-          return readEddystoneProperty(this.webBluetoothId, p);
-        });
+    for (const p of propertyKeys) {
+      this.thing?.setPropertyReadHandler(p, () => {
+        return readEddystoneProperty(this.webBluetoothId, p);
+      });
 
-        if (!properties[p].readOnly) {
-          this.thing.setPropertyWriteHandler(p, value => {
-            return writeEddystoneProperty(
-              this.webBluetoothId,
-              p,
-              value as unknown as string
-            );
-          });
-        }
+      if (!properties[p].readOnly) {
+        this.thing?.setPropertyWriteHandler(p, value => {
+          return writeEddystoneProperty(
+            this.webBluetoothId,
+            p,
+            value as unknown as string
+          );
+        });
       }
     }
   }

### 2022-03-07 dist/thingBlocks/streamdeck/generators.js
add streamDeck WoT implementation

@@ -8,7 +8,6 @@
 'use strict';
 
 import {JavaScript} from 'blockly';
-import StreamDeck from '@elgato-stream-deck/webhid';
 import {addCleanUpFunction} from './../../blast_interpreter.js';
 import {getThingsLog} from './../../blast_things.js';
 import {apiFunctions} from './../../blast_interpreter.js';
@@ -16,7 +15,7 @@ import {asyncApiFunctions} from './../../blast_interpreter.js';
 import {getInterpreter} from './../../blast_interpreter.js';
 import {setInterrupted} from './../../blast_interpreter.js';
 // eslint-disable-next-line node/no-missing-import
-import {Streamdeck} from './../../things/streamdeck/Streamdeck.js';
+import {StreamDeck} from './../../things/streamdeck/StreamDeck.js';
 import {throwError} from './../../blast_interpreter.js';
 
 const thingsLog = getThingsLog();

### 2022-03-07 dist/things/streamdeck/StreamDeck.d.ts

@@ -1,10 +1,11 @@
 import * as WoT from 'wot-typescript-definitions';
-export declare class Streamdeck {
+export declare class StreamDeck {
     private thing;
     private exposedThing;
-    td: WoT.ThingDescription;
     private streamdeck;
     private webHidId;
+    private opened;
+    td: WoT.ThingDescription;
     thingModel: WoT.ThingDescription;
     constructor(webHidId: string);
     /**

### 2022-03-07 dist/things/streamdeck/StreamDeck.js

@@ -3,11 +3,12 @@ import { throwError } from '../../blast_interpreter.js';
 import { openDevice } from '@elgato-stream-deck/webhid';
 import { getThing, removeThing } from '../index.js';
 const thingsLog = getThingsLog();
-export class Streamdeck {
+export class StreamDeck {
     constructor(webHidId) {
         this.thing = null;
         this.exposedThing = null;
         this.streamdeck = null;
+        this.opened = false;
         this.thingModel = {
             '@context': ['https://www.w3.org/2019/wot/td/v1'],
             '@type': ['Thing'],
@@ -85,6 +86,7 @@ export class Streamdeck {
         let sd;
         try {
             sd = await openDevice(device);
+            this.opened = true;
             return sd;
         }
         catch (e) {
@@ -104,7 +106,8 @@ export class Streamdeck {
      * Sets the colors of the streamdeck buttons.
      */
     async setButtonColors(buttonColors) {
-        while (!this.streamdeck) {
+        var _a, _b, _c;
+        while (!this.opened) {
             // Wait for the thing to be initialized
             await new Promise(resolve => setTimeout(resolve, 100));
         }
@@ -122,16 +125,17 @@ export class Streamdeck {
                 red,
                 green,
                 blue,
-            ].toString()}</code>`, 'hid', this.streamdeck.PRODUCT_NAME);
-            await this.streamdeck.fillKeyColor(id, red, green, blue);
-            thingsLog('Finished <code>fillKeyColor</code>', 'hid', this.streamdeck.PRODUCT_NAME);
+            ].toString()}</code>`, 'hid', (_a = this.streamdeck) === null || _a === void 0 ? void 0 : _a.PRODUCT_NAME);
+            await ((_b = this.streamdeck) === null || _b === void 0 ? void 0 : _b.fillKeyColor(id, red, green, blue));
+            thingsLog('Finished <code>fillKeyColor</code>', 'hid', (_c = this.streamdeck) === null || _c === void 0 ? void 0 : _c.PRODUCT_NAME);
         }
     }
     /**
      * Sets the text of the streamdeck buttons.
      */
     async setButtonText(buttonText) {
-        while (!this.streamdeck) {
+        var _a, _b, _c, _d, _e;
+        while (!this.opened) {
             // Wait for the thing to be initialized
             await new Promise(resolve => setTimeout(resolve, 100));
         }
@@ -142,8 +146,8 @@ export class Streamdeck {
[…]

### 2022-03-07 src/things/streamdeck/StreamDeck.ts

@@ -1,4 +1,3 @@
-// eslint-disable-next-line node/no-unpublished-import
 import * as WoT from 'wot-typescript-definitions';
 import {getThingsLog, getWebHidDevice} from '../../blast_things.js';
 import {throwError} from '../../blast_interpreter.js';
@@ -9,12 +8,13 @@ import {ExposedThing} from '@node-wot/core';
 
 const thingsLog = getThingsLog();
 
-export class Streamdeck {
+export class StreamDeck {
   private thing: WoT.ExposedThing | null = null;
   private exposedThing: ExposedThing | null = null;
-  public td: WoT.ThingDescription;
   private streamdeck: StreamDeckWeb | null = null;
   private webHidId: string;
+  private opened = false;
+  public td: WoT.ThingDescription;
 
   public thingModel: WoT.ThingDescription = {
     '@context': ['https://www.w3.org/2019/wot/td/v1'],
@@ -96,6 +96,7 @@ export class Streamdeck {
     let sd;
     try {
       sd = await openDevice(device);
+      this.opened = true;
       return sd;
     } catch (e: any) {
       // if InvalidStateError error, device is probably already opened
@@ -116,7 +117,7 @@ export class Streamdeck {
   private async setButtonColors(
     buttonColors: Array<{id: number; color: string}>
   ): Promise<void> {
-    while (!this.streamdeck) {
+    while (!this.opened) {
       // Wait for the thing to be initialized
       await new Promise(resolve => setTimeout(resolve, 100));
     }
@@ -138,13 +139,13 @@ export class Streamdeck {
           blue,
         ].toString()}</code>`,
         'hid',
-        this.streamdeck.PRODUCT_NAME
+        this.streamdeck?.PRODUCT_NAME
       );
-      await this.streamdeck.fillKeyColor(id, red, green, blue);
+      await this.streamdeck?.fillKeyColor(id, red, green, blue);
       thingsLog(
         'Finished <code>fillKeyColor</code>',
         'hid',
-        this.streamdeck.PRODUCT_NAME
+        this.streamdeck?.PRODUCT_NAME
       );
     }
   }
@@ -153,7 +154,7 @@ export class Streamdeck {
    * Sets the text of the streamdeck buttons.
    */
   private async setButtonText(buttonText: Array<{id: number; text: string}>) {
-    while (!this.streamdeck) {
+    while (!this.opened) {
       // Wait for the thing to be initialized
[…]

### 2022-03-07 src/thingBlocks/streamdeck/generators.js
fix StreamDeck generator

@@ -8,7 +8,6 @@
 'use strict';
 
 import {JavaScript} from 'blockly';
-import StreamDeck from '@elgato-stream-deck/webhid';
 import {addCleanUpFunction} from './../../blast_interpreter.js';
 import {getThingsLog} from './../../blast_things.js';
 import {apiFunctions} from './../../blast_interpreter.js';
@@ -16,7 +15,7 @@ import {asyncApiFunctions} from './../../blast_interpreter.js';
 import {getInterpreter} from './../../blast_interpreter.js';
 import {setInterrupted} from './../../blast_interpreter.js';
 // eslint-disable-next-line node/no-missing-import
-import {Streamdeck} from './../../things/streamdeck/Streamdeck.js';
+import {StreamDeck} from './../../things/streamdeck/StreamDeck.js';
 import {throwError} from './../../blast_interpreter.js';
 
 const thingsLog = getThingsLog();
@@ -135,7 +134,7 @@ const registerStreamdeckHandler = function (id, buttons, upDown, statements) {
     }
   };
 
-  const thing = new Streamdeck(id);
+  const thing = new StreamDeck(id);
   thing.subscribeEvent('button' + upDown, handler);
 
   addCleanUpFunction(() => {
@@ -174,7 +173,7 @@ const streamdeckColorButtons = async function (id, buttons, color, callback) {
     }
   }
 
-  const thing = new Streamdeck(id);
+  const thing = new StreamDeck(id);
   await thing.writeProperty('buttonColors', buttonsToColor);
 
   callback();
@@ -231,7 +230,7 @@ const streamdeckWriteOnButtons = async function (id, buttons, value, callback) {
     }
   }
 
-  const thing = new Streamdeck(id);
+  const thing = new StreamDeck(id);
   await thing.writeProperty('buttonText', buttonsToWrite);
 
   callback();

### 2022-03-07 dist/thingBlocks/joycon/generators.js
add joy-con sensor WoT implementation

@@ -8,6 +8,8 @@
 
 import {JavaScript} from 'blockly';
 import {JoyConLeft, JoyConRight} from './joycon-webhid/joycon.js';
+// eslint-disable-next-line node/no-missing-import
+import {JoyCon} from './../../things/joycon/JoyCon.js';
 import {apiFunctions} from './../../blast_interpreter.js';
 import {asyncApiFunctions} from './../../blast_interpreter.js';
 import {deviceEventHandlers} from './../../blast_interpreter.js';
@@ -59,94 +61,18 @@ const readJoyConProperty = async function (
     return;
   }
 
-  const device = getWebHidDevice(id);
-
-  if (!device) {
-    throwError(
-      'Connected device is not a HID device.\nMake sure you are connecting the JoyCon via webHID'
-    );
-    callback();
-    return;
-  }
-
-  if (!device.opened) {
-    try {
-      await device.open();
-    } catch (error) {
-      throwError(
-        "Failed to open device, your browser or OS probably doesn't support webHID."
-      );
-    }
-  }
-
-  // Check if device is a Joy-Con.
-  if (
-    device.vendorId !== 1406 ||
-    (device.productId !== 0x2006 && device.productId !== 0x2007)
-  ) {
-    throwError('The connected device is not a Joy-Con.');
-    callback();
-    return;
-  }
-
-  let joyCon;
-  if (device.productId === 0x2006) {
-    joyCon = new JoyConLeft(device);
-  } else if (device.productId === 0x2007) {
-    joyCon = new JoyConRight(device);
-  }
-  await joyCon.open();
-  await joyCon.enableStandardFullMode();
-  await joyCon.enableIMUMode();
-
-  const thingsLog = getThingsLog();
-
-  const hidInputHandler = async function (event) {
-    const packet = event.detail;
-    if (!packet || !packet.actualOrientation) {
-      return;
-    }
-
-    thingsLog(
-      `Received <code>hidinput</code> event from Joy-Con: <code>${JSON.stringify(
-        packet
-      )}</code>`,
-      'hid',
-      device.productname
-    );
-
-    thingsLog(
-      'Removing <code>hidinput</code> event listener',
-      'hid',
-      device.productname
-    );
-    joyCon.removeEventListener('hidinput', hidInputHandler);
-    if (subValue2 !== '') {
-      if (property === 'accelerometers') {
-        callback(packet[property][subValue][subValue2].acc);
-      } else if (property === 'gyroscopes') {
[…]

### 2022-03-07 dist/thingBlocks/streamdeck/generators.js

@@ -134,7 +134,7 @@ const registerStreamdeckHandler = function (id, buttons, upDown, statements) {
     }
   };
 
-  const thing = new Streamdeck(id);
+  const thing = new StreamDeck(id);
   thing.subscribeEvent('button' + upDown, handler);
 
   addCleanUpFunction(() => {
@@ -173,7 +173,7 @@ const streamdeckColorButtons = async function (id, buttons, color, callback) {
     }
   }
 
-  const thing = new Streamdeck(id);
+  const thing = new StreamDeck(id);
   await thing.writeProperty('buttonColors', buttonsToColor);
 
   callback();
@@ -230,7 +230,7 @@ const streamdeckWriteOnButtons = async function (id, buttons, value, callback) {
     }
   }
 
-  const thing = new Streamdeck(id);
+  const thing = new StreamDeck(id);
   await thing.writeProperty('buttonText', buttonsToWrite);
 
   callback();

### 2022-03-07 dist/things/joycon/JoyCon.d.ts

@@ -1,0 +1,15 @@
+import * as WoT from 'wot-typescript-definitions';
+export declare class JoyCon {
+    private thing;
+    private device;
+    private joyCon;
+    private log;
+    private opened;
+    private eventListenerAttached;
+    td: WoT.ThingDescription;
+    private webHidId;
+    thingModel: WoT.ThingDescription;
+    constructor(webHidId: string);
+    private open;
+    readProperty(property: string): Promise<any>;
+}

### 2022-03-07 dist/things/joycon/JoyCon.js

@@ -1,0 +1,455 @@
+import { getThing } from '../index.js';
+import { JoyConLeft, JoyConRight } from 'joy-con-webhid';
+import { getThingsLog, getWebHidDevice } from '../../blast_things.js';
+import { throwError } from '../../blast_interpreter.js';
+export class JoyCon {
+    constructor(webHidId) {
+        this.thing = null;
+        this.device = null;
+        this.joyCon = null;
+        this.opened = false;
+        this.eventListenerAttached = false;
+        this.thingModel = {
+            '@context': ['https://www.w3.org/2019/wot/td/v1'],
+            '@type': ['Thing'],
+            id: 'blast:webhid:joycon',
+            title: 'Joy-Con',
+            description: 'Nintendo Joy-Con',
+            securityDefinitions: {
+                nosec_sc: {
+                    scheme: 'nosec',
+                },
+            },
+            security: 'nosec_sc',
+            properties: {
+                accelerometer: {
+                    title: 'Accelerometer',
+                    description: 'The accelerometer of the joy-con',
+                    type: 'object',
+                    properties: {
+                        x: {
+                            title: 'X',
+                            description: 'The X-axis of the accelerometer',
+                            type: 'number',
+                            readOnly: true,
+                        },
+                        y: {
+                            title: 'Y',
+                            description: 'The Y-axis of the accelerometer',
+                            type: 'number',
+                            readOnly: true,
+                        },
+                        z: {
+                            title: 'Z',
+                            description: 'The Z-axis of the accelerometer',
+                            type: 'number',
+                            readOnly: true,
+                        },
+                    },
+                },
+                actualAccelerometer: {
+                    title: 'Actual accelerometer',
+                    description: 'The actual accelerometer of the joy-con',
+                    type: 'object',
+                    properties: {
+                        x: {
+                            title: 'X',
+                            description: 'The X-axis of the accelerometer',
+                            type: 'number',
+                            readOnly: true,
+                        },
+                        y: {
+                            title: 'Y',
+                            description: 'The Y-axis of the accelerometer',
+                            type: 'number',
+                            readOnly: true,
+                        },
+                        z: {
+                            title: 'Z',
+                            description: 'The Z-axis of the accelerometer',
+                            type: 'number',
+                            readOnly: true,
+                        },
+                    },
+                },
+                actualGyroscope: {
+                    title: 'Actual gyroscope',
+                    description: 'The angular velocity (rps and dps) based on all 3 gyroscopes, on 3 axis',
+                    type: 'object',
[…]

### 2022-03-07 src/things/joycon/JoyCon.ts

@@ -1,0 +1,499 @@
+import * as WoT from 'wot-typescript-definitions';
+import {getThing} from '../index.js';
+import {JoyConLeft, JoyConRight} from 'joy-con-webhid';
+import {getThingsLog, getWebHidDevice} from '../../blast_things.js';
+import {throwError} from '../../blast_interpreter.js';
+
+export class JoyCon {
+  private thing: WoT.ExposedThing | null = null;
+  private device: HIDDevice | null = null;
+  private joyCon: JoyConLeft | JoyConRight | null = null;
+  private log: Function;
+  private opened = false;
+  private eventListenerAttached = false;
+  public td: WoT.ThingDescription;
+  private webHidId: string;
+
+  public thingModel: WoT.ThingDescription = {
+    '@context': ['https://www.w3.org/2019/wot/td/v1'],
+    '@type': ['Thing'],
+    id: 'blast:webhid:joycon', // this should normally be an URI, need to figure out a how to properly identify tds
+    title: 'Joy-Con',
+    description: 'Nintendo Joy-Con',
+    securityDefinitions: {
+      nosec_sc: {
+        scheme: 'nosec',
+      },
+    },
+    security: 'nosec_sc',
+    properties: {
+      accelerometer: {
+        title: 'Accelerometer',
+        description: 'The accelerometer of the joy-con',
+        type: 'object',
+        properties: {
+          x: {
+            title: 'X',
+            description: 'The X-axis of the accelerometer',
+            type: 'number',
+            readOnly: true,
+          },
+          y: {
+            title: 'Y',
+            description: 'The Y-axis of the accelerometer',
+            type: 'number',
+            readOnly: true,
+          },
+          z: {
+            title: 'Z',
+            description: 'The Z-axis of the accelerometer',
+            type: 'number',
+            readOnly: true,
+          },
+        },
+      },
+      actualAccelerometer: {
+        title: 'Actual accelerometer',
+        description: 'The actual accelerometer of the joy-con',
+        type: 'object',
+        properties: {
+          x: {
+            title: 'X',
+            description: 'The X-axis of the accelerometer',
+            type: 'number',
+            readOnly: true,
+          },
+          y: {
+            title: 'Y',
+            description: 'The Y-axis of the accelerometer',
+            type: 'number',
+            readOnly: true,
+          },
+          z: {
+            title: 'Z',
+            description: 'The Z-axis of the accelerometer',
+            type: 'number',
+            readOnly: true,
+          },
+        },
+      },
[…]

### 2022-03-07 demo-eswc22/paper.tex
sections 1 and 2 are almost final

@@
 % to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
+%\renewcommand\UrlFont{\color{blue}\rmfamily}
 
@@
 \begin{abstract}
-  An open research challenge in the deployment of IoT devices is the interaction with humans.
-  We introduce a block-based visual programming language and execution environment called BLAST.
-  BLAST allows for visually creating programs involving devices with a Web of Things interface.
-  We demonstrate that BLAST can be used to create programs that interact with a variety of devices in a geofencing scenario.
+  We introduce a block-based visual programming language called BLAST to write programs involving connected devices with a Web of Things abstraction.
+  We developed an editor and an execution environment for BLAST programs that runs in a web browser.
+  We demonstrate that BLAST can be used to create programs that interact with a variety of devices.
+  In particular we show the use of connected devices in a geofencing scenario.
 \keywords{Block-based Programming \and Web of Things.}
@@
 \section{Introduction}
-IoT devices form the basis for a variety of applications, such as condition monitoring, energy consumption analysis, simulation and optimisation~\cite{CIMINO2019103130}.
-However, there are still some research challenges that need to be overcome.
-Interaction capabilities refer to the fact that devices will not be involved in any important decisions without humans.
-In this paper, we focus on the challenge of humans interacting with devices, a challenge that needs to be resolved to achieve a widespread deployment of IoT devices in industry~\cite{KUEHNER20211227}.
-Thus, humans should find it easy to interact with devices and the devices should be able to interact smoothly with humans.
+Connected devices form the basis for a wide variety of applications in industry settings, such as condition monitoring, energy consumption analysis, simulation and optimisation~\cite{CIMINO2019103130}.
+%Given the multitude of protocols for interacting with such devices, application development is difficult.
+The Web of Things (WoT)\footnote{\url{https://www.w3.org/WoT/}} aims at providing a set of standardised technologies to help simplify the creating of applications involving connected devices.
+At the same time, casual users should be able to quickly program applications involving connected devices.
+The programming languages currently in use for accessing devices are primarily text-based and are difficult to access for casual users.
+One possible approach to improve accessibility and simplify the creation of computer programs is the visual programming paradigm.
 
-We assume that the interoperability challenge, that is, a devices' ability to capture a multi-stage product lifecycle, which requires collecting and integrating data from multiple devices and sources~\cite{SEMERARO2021103469}, has been addressed by the use of the Web of Things abstraction.
+Visual programming does not require the user to enter any text; instead, programs are based on graphical elements like blocks, graphs, tables or diagrams.
+Programs are created by arranging predefined blocks with images or text are arranged into programs via a drag-and-drop interface.
+Blocks can be geometrically aligned with other compatible blocks, like in a jigsaw puzzle, to form complex programs.
+Since blocks can only be arranged in the correct way, no syntax errors can occur~\cite{10.11453341221}~\cite{maloney2010scratch}~\cite{10.1145/1089733.1089734}.
 
-We present BLAST (Block Applications for Things), an easy-to-use interaction interface for humans with devices following the Web of Things interface based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}}.
-Blockly is a pure JavaScript library for creating block-based languages and editors.
-BLAST implements the Web of Things abstraction to devices with Bluetooth Low Energy (BLE) and USB Human Interface Devices (HID) interface and to various browser APIs that allow for accessing HTTP APIs.
-These devices and APIs are supported by modern web browsers.
-The Web of Thing abstraction involves Things and their Properties that can be read and written, their Actions that can be invoked and their Events that can be observed.
+The created block programs can be translated into any predefined programming language, resulting in a normal source code. 
+The block-based approach can be used not only for learning programming concepts, but also for more complex problems.
+For example, block languages have been successfully used in programming industrial robots~\cite{8120406}~\cite{ghazal2016framework}~\cite{tomlein2017visual} or executing SPARQL queries~\cite{7369012}, both areas which normally require advanced programming skills.
+
+We present BLAST, a visual programming environment that works with devices following the Web of Things interface.
+BLAST programs can be created in a web browser, based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}}, a JavaScript library for creating block-based languages and editors.
+BLAST programs can be translated to JavaScript and executed in the web browser.
+BLAST implements the Web of Things abstraction to devices with Bluetooth Low Energy (BLE) and USB Human Interface Devices (HID) interface via APIs of modern web browsers.
 
@@
 In contrast to BLAST, which focuses on control flow constructs, Node-RED's programming paradigm is based on dataflows.
-The use cases we envision for BLAST involve mostly control flow, and in such scenarios a dataflow abstraction can lead to programs that are difficult to understand and maintain.
+The use cases in industrial settings we envision for BLAST involve mostly control flow, and in such scenarios a dataflow abstraction can lead to programs that are difficult to understand and maintain.
 %The nodes in these graphs are black box processes, created by the developers, that can be connected to each other by the end user.
@@
 Like BLAST, Punya offers a block-based programming environment able to run SPARQL queries and include online services.
-Punya focuses on creating applications for Android devices only and communicates with the device's internal hardware, in addition to working as a LDP-CoAP client to publish and access data on CoAP servers.
-BLAST, on the other hand, runs in modern web browsers and supports devices based on a Web of Things abstraction.
+Punya focuses on creating applications for Android devices and communicates with the mobile phones's internal hardware, in addition to working as a LDP-CoAP client to publish and access data on CoAP servers.
+BLAST programs, on the other hand, run in modern web browsers and support devices based on a Web of Things abstraction.
 
-We first overview block-based visual programming approaches, next introduce BLAST with a scenario involving multiple devices, list the currently supported devices and services and conclude with a summary and outlook.
+In the following we first introduce the BLAST language using a geofencing scenario, next describe the browser-based editor and execution environment for BLAST programs and then conclude.
 
-\section{Block-based Visual Programming}
+\section{BLAST Language}
 
-%The programming languages currently in use for accessing devices are primarily text-based and are difficult to access for casual users.
-%One possible approach to improve accessibility and simplify the creation of computer programs is so-called Visual Programming (VP).
-% Falls Platz dafür ist, die Definition für VP fand ich besser:
-Visual programming refers to any system that allows the user to specify a program in a two (or more) dimensional fashion~\cite{myers1990taxonomies}.
-Conventional textual languages are not considered two dimensional since the compiler or interpreter processes it as a long, one-dimensional stream.
-%For a more in-depth definition of VP, the reader is referred to \cite{burnett1995visual}. 
-Visual programming does not require the user to enter any text; instead, programs are based on graphical elements like blocks, graphs, tables or diagrams.
-Programs are created by arranging predefined blocks with images or text are arranged into programs via a drag-and-drop interface.
-Blocks can be geometrically aligned with other compatible blocks, like in a jigsaw puzzle, to form complex programs.
-Since blocks can only be arranged in the correct way, no syntax errors can occur~\cite{10.11453341221}~\cite{maloney2010scratch}~\cite{10.1145/1089733.1089734}~\cite{lye2014review}.
+When choosing the vocabulary for our block-based language BLAST, we decided on a mixture of natural language and computer language~\cite{8120404}.
+In BLAST, the blocks are arranged into readable sentences, as in a natural language, but the blocks also contain a few technical programming terms, such as ''repeat while true'' instead of ''forever''.
 
-% Vorschläge für Referenzen
-%\cite{moors2018transitioning} \cite{weintrop2017blocks} \cite{chao2016exploring} \cite{HUNDHAUSEN200722} \cite{10.1145/2787622.2787712}.
+The BLAST language includes standard elements from other programming languages such as loops, functions, and variables.
+In addition, the BLAST language provides blocks related to interacting with WoT devices.
+These WoT-related blocks can be grouped under the three interaction affordances Properties (that can be read and written), Actions (that can be invoked), and Events (that can be observed).
+Further, the BLAST language includes blocks to send HTTP requests with arbitrary headers, request method and request body.
+Using HTTP requests, one can load RDF graphs from a URI and execute SPARQL queries, which allows for the interaction with Read-Write Linked Data APIs or other REST APIs.
+Finally, if the available blocks are not sufficient to implement a desired functionality, there is a block in which native JavaScript code can be entered, and thus almost everything that is possible in JavaScript is also possible in BLAST.
 
-%Bau et al.
-\cite{1011453015455} pointed out that block-based programming languages teach programming concepts in a simple way due to an intuitive and friendly user interface and that after using block-based languages it is much easier for users to switch to traditional text-based languages.
-
-The created block programs can be translated into any predefined programming language, resulting in a normal source code. 
-The block-based approach can be used not only for learning programming concepts, but also for more complex problems.
-For example, block languages have been successfully used in programming industrial robots~\cite{8120406}~\cite{ghazal2016framework}~\cite{tomlein2017visual} or executing SPARQL queries~\cite{7369012}, both areas which normally require advanced programming skills.
-
-%Furthermore, Ray examined the use of block-based programming languages for IoT devices in \cite{ray2017survey} and concluded that IoT seems to be suitably getting empowered by smooth entanglement and promotion with promising reduction in physical-digital interface.
-%Das ist ein direktes Zitat, muss man das anders schreiben?
-
-\section{BLAST Language and Editor}
-
-Due to the success of block-based languages in different challenging areas, we have developed our own block language.
-Our block-based language simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols such as Bluetooth or HTTP.
-The browser-based BLAST uses Web Bluetooth to communicate with IoT devices, custom control and command blocks, and generates JavaScript code that can be used by any JavaScript interpreter.
-To interact with the IoT devices, BLAST requires custom drivers for each device, which represent an extended form of the WoT TD % Beides noch nicht definiert
-and contain the metadata and interaction affordances as well as the JavaScript code needed for communication.
-
-When choosing the vocabulary for our block-based language BLAST, we resorted to a mixture of natural language and computer language \cite{8120404}.
-This means that in BLAST, the blocks are arranged into readable sentences, as in a natural language, but the blocks also contain a few technical programming terms, such as ''repeat while true'' instead of ''forever''.
 For an example for a BLAST program see figure \ref{fig1}.
-We have also implemented a more complex logistics scenario involving an automated picking line to prepare orders.
+The program involves a LED light with a BLE interface and a small battery-powered BLE beacon.
+The BLE controller (the ``BLE central'') is implicitly used when reading the signal-strength property.
+The functionality of these devices (``Things'') can be accessed via reading and writing properties.
+The LED light, for example, has a property ``colour'' that can be written.
+To enable an event abstraction, the program includes a block that defines a state with a condition on the signal strength of the BLE beacon.
+On entering or exiting the defined state, the event blocks, which can contain arbitrary blocks, are triggered.
 
@@
 \includegraphics[width=\textwidth]{screenshot 3.png}%im Ordner sind noch 2 alternative Screenshots
-\caption{Example BLAST program that implements a geofencing scenario: when the BLE beacon gets close, the LED light is turned off; when the BLE beacon leaves the close range, the LED light is turned red.} \label{fig1}
+\caption{Example BLAST program that implements a geofencing scenario: when the beacon gets close, the light is turned off; when the beacon leaves the close range, the light is turned red.} \label{fig1}
 \end{figure}
 
-BLAST includes standards from other programming languages such as loops, functions, and variables, but also WoT and IoT related blocks that can be grouped under the three interaction affordances Properties, Actions, and Events.
-Properties of connected IoT devices can be read and written, actions refer to long-running processes that can be initiated and events are asynchronous and based on the ''Event Conditon Action'' (ECA) rule.
-If an event occurs, the condition is checked and if necessary the corresponding action is executed.
-Furthermore, it is possible to send HTTP requests with arbitrary header and body or load knowledge graphs from a URI and execute SPARQL queries on the records, which allows interaction with Read-Write Linked Data APIs or other REST APIs.
-If the available blocks are not sufficient to implement a desired functionality, there is a block in which native JavaScript code can be entered.
-This block makes almost everything that is possible in JavaScript also possible in BLAST.
+\section{BLAST Editor and Execution Environment}
 
-\section{BLAST Execution Environment}
+We have implemented an editor and an execution environment for BLAST programs that runs in a modern web browser.
+
+uses Web Bluetooth to communicate with IoT devices, custom control and command blocks, and generates JavaScript code that can be used by any JavaScript interpreter.
+To interact with the IoT devices, BLAST requires custom drivers for each device, which represent an extended form of the WoT TD % Beides noch nicht definiert
+and contain the metadata and interaction affordances as well as the JavaScript code needed for communication.
 
@@
 
-As IoT devices become more and more relevant in the industrial environment, it is essential to investigate how the interaction between humans and the IoT devices can be seamlessly implemented.
-We have explored the use of an easy-to-use block-based programming environment to interact with devices.
+Our block-based language simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols such as Bluetooth or HTTP.
+As IoT devices become increasingly relevant in the industrial environment, investigating how the interaction between humans and the IoT devices can be seamlessly implemented.
+We have explored the use of block-based programming environment to interact with devices.
+We have also implemented a more complex logistics scenario involving an automated picking line to prepare orders.
+
 We are currently working on a way to execute the created BLAST program independently of browsers.

### 2022-03-07 demo-eswc22/paper.tex
4 pages

@@
 \begin{abstract}
-  We introduce a block-based visual programming language called BLAST to write programs involving connected devices with a Web of Things abstraction.
+  We introduce a block-based visual programming language called BLAST for programs involving connected devices with a Web of Things abstraction.
   We developed an editor and an execution environment for BLAST programs that runs in a web browser.
@@
 The block-based approach can be used not only for learning programming concepts, but also for more complex problems.
-For example, block languages have been successfully used in programming industrial robots~\cite{8120406}~\cite{ghazal2016framework}~\cite{tomlein2017visual} or executing SPARQL queries~\cite{7369012}, both areas which normally require advanced programming skills.
+For example, block languages have been successfully used in constructing SPARQL queries~\cite{7369012} or programming industrial robots~\cite{8120406}~\cite{tomlein2017visual}, both areas which normally require advanced programming skills.
 
@@
 The currently best known tool for programming IoT devices using visual programming is Node-RED\footnote{\url{https://nodered.org/}}.
-In contrast to BLAST, which focuses on control flow constructs, Node-RED's programming paradigm is based on dataflows.
+Node-RED's programming paradigm is based on dataflows; in contrast, BLAST focuses on control flow constructs,
 The use cases in industrial settings we envision for BLAST involve mostly control flow, and in such scenarios a dataflow abstraction can lead to programs that are difficult to understand and maintain.
 %The nodes in these graphs are black box processes, created by the developers, that can be connected to each other by the end user.
-%The block-based approach utilized by BLAST provides more flexibility as its blocks are a lot more fine grained.
+%The block-based approach utilised by BLAST provides more flexibility as its blocks are a lot more fine grained.
 %BLAST is a programming language with a
 
-Another system similiar to BLAST is Punya~\cite{patton2021punya}, an Android app development system based on the MIT App Inventor\footnote{\url{https://appinventor.mit.edu/}}.
-Like BLAST, Punya offers a block-based programming environment able to run SPARQL queries and include online services.
-Punya focuses on creating applications for Android devices and communicates with the mobile phones's internal hardware, in addition to working as a LDP-CoAP client to publish and access data on CoAP servers.
-BLAST programs, on the other hand, run in modern web browsers and support devices based on a Web of Things abstraction.
+Another system similar to BLAST is Punya~\cite{patton2021punya}, an Android app development system based on the MIT App Inventor\footnote{\url{https://appinventor.mit.edu/}}.
+Like BLAST, Punya offers a block-based programming environment for writing programs that can include SPARQL queries and access online services.
+Punya focuses on creating applications for Android devices that can access the mobile phone's internal hardware.
+Punya also acts as a client to publish and access data on servers supporting the Constrained Application Protocol (CoAP).
+BLAST programs, on the other hand, run in modern web browsers and support devices based on a WoT abstraction.
 
@@
 Further, the BLAST language includes blocks to send HTTP requests with arbitrary headers, request method and request body.
-Using HTTP requests, one can load RDF graphs from a URI and execute SPARQL queries, which allows for the interaction with Read-Write Linked Data APIs or other REST APIs.
+The BLAST language also includes blocks to load RDF graphs from a URI and execute SPARQL queries, which allows for the interaction with Read-Write Linked Data APIs or other REST APIs.
 Finally, if the available blocks are not sufficient to implement a desired functionality, there is a block in which native JavaScript code can be entered, and thus almost everything that is possible in JavaScript is also possible in BLAST.
@@
 \includegraphics[width=\textwidth]{screenshot 3.png}%im Ordner sind noch 2 alternative Screenshots
-\caption{Example BLAST program that implements a geofencing scenario: when the beacon gets close, the light is turned off; when the beacon leaves the close range, the light is turned red.} \label{fig1}
+\caption{Example BLAST program that implements a geofencing scenario: when the beacon gets close, the light is turned off; when the beacon leaves the close range, a sound is played and the light is turned red.} \label{fig1}
 \end{figure}
@@
 
-We have implemented an editor and an execution environment for BLAST programs that runs in a modern web browser.
+We have implemented an editor and an execution environment for BLAST programs that runs in modern web browsers.
 
-uses Web Bluetooth to communicate with IoT devices, custom control and command blocks, and generates JavaScript code that can be used by any JavaScript interpreter.
-To interact with the IoT devices, BLAST requires custom drivers for each device, which represent an extended form of the WoT TD % Beides noch nicht definiert
-and contain the metadata and interaction affordances as well as the JavaScript code needed for communication.
-
-Supported Devices and Services
-
-To demonstrate how BLAST can interact with WoT devices, we provide a Web of Things abstraction for devices communicating with Bluetooth Low Energy and USB Human Interface Devices (HID).
-We also provide access to online APIs related to speech input and output and services like playing audio from a URI or invoking SPARQL queries on an online ressource.
-
-\begin{center}
-  \begin{tabular}{|c|c|c|}
-  \hline
-  \thead{Device} & \thead{Communication} & \thead{WoT interactions} \\
-  \hline
-  Eddystone Devices & BLE GATT & read/write Eddystone properties \\
-  \hline
-  HuskyLens\footnote{https://wiki.dfrobot.com/HUSKYLENS\_V1.0\_SKU\_SEN0305\_SEN0336} & BLE GATT & read sensor properties, invoke forget action \\
-  \hline
-  RGB LED Controller\footnote{https://aliexpress.com/item/4000208329326.html} & BLE GATT & write color properties \\
-  \hline
-  RuuviTag\footnote{https://ruuvi.com/ruuvitag/} & BLE GAP & \makecell{read sensor properties, read battery property, \\
-  read/write txPower property, \\
-  read movement counter propert,y \\
-  read measurement sequence counter property} \\
-  \hline
-  StreamDeck\footnote{https://www.streamdeck.com/} & USB HID & \makecell{write display properties, \\ subscribe to button push events} \\
-  \hline
-  Tulogic BlinkStick\footnote{https://www.blinkstick.com/} & USB HID & write color properties \\ 
-  \hline
-  Nintendo JoyCon\footnote{https://www.nintendo.com/switch/tech-specs/\#joycon-section} & USB HID \& BLE GATT & \makecell{read sensor properties,\\ subscribe to button push events} \\
-  \hline
-  Xiaomi Thermometer\footnote{https://xiaomipedia.com/en/p/xiaomi-electronic-thermometer-and-hygrometer/} & BLE GAP & read sensor properties \\
-  \hline
-  \end{tabular}
-
-  \begin{tabular}{|c|c|}
-  \hline
-  \thead{Service} & \thead{WoT interactions} \\
-  \hline
-  Camera & invoke capture image action \\
-  \hline
-  Audio & invoke play audio action \\
-  \hline
-  WebSpeech API & invoke text to speech action, invoke speech to text action \\
-  \hline
-  HTTP Requests & invoke send HTTP request action \\
-  \hline
-  SPARQL Query & invoke execute SPARQL query action \\
-  \hline
-  SOLID & invoke upload to solid container action \\
-  \hline
-  \end{tabular}
-\end{center}
+The editor uses the Blockly library and provides custom control and command blocks that make up the BLAST language.
+For execution, the editor generates JavaScript code that can be executed in the browser.
+The system builds on the Web Bluetooth API\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/}} and the WebHID API\footnote{\url{https://wicg.github.io/webhid/}} to interact with devices.
+The system uses the Web of Things abstraction as interface; we have implemented the WoT interface for eight devices the use the BLE GAP and GATT profiles as well as the USB Human Interface Devices (HID) interface.
+The WoT interface contains the metadata and interaction affordances as well as the JavaScript code needed for communication.
+In addition, the system includes access to the camera and sound output via browser APIs using the WoT interface.
+Further, the system includes access to the Web Speech API\footnote{\url{https://wicg.github.io/speech-api/}}.
+The ability to issue HTTP requests is implemented using the @@@ API, Social Linked Data (Solid) authentication is implemented using the @@@ API, and SPARQL query support is implemented using µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
+Next the the presented scenario around geofences, we have also implemented a BLAST program to control and monitor an automated picking line to prepare orders in a more complex logistics scenario.
 
@@
 
-Our block-based language simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols such as Bluetooth or HTTP.
-As IoT devices become increasingly relevant in the industrial environment, investigating how the interaction between humans and the IoT devices can be seamlessly implemented.
-We have explored the use of block-based programming environment to interact with devices.
-We have also implemented a more complex logistics scenario involving an automated picking line to prepare orders.
-
-We are currently working on a way to execute the created BLAST program independently of browsers.
-To this end, we are developing an execution environment that can load BLAST programs, convert them to JavaScript, and execute them as a server.
+We have presented BLAST, a block-based language that simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols.
+We are currently working on an execution environment that runs on Node.js as a way to execute BLAST programs independently of browsers.
+%To this end, we are developing an execution environment that can load BLAST programs, convert them to JavaScript, and execute them as a server.
 %In the future, it would enrich BLAST if there was a way to consume WoT TDs and derive interaction possibilities, which would allow BLAST to interact with any WoT device.

### 2022-03-07 demo-eswc22/paper.tex
minor fixes

@@
 Further, the system includes access to the Web Speech API\footnote{\url{https://wicg.github.io/speech-api/}}.
-The ability to issue HTTP requests is implemented using the @@@ API, Social Linked Data (Solid) authentication is implemented using the @@@ API, and SPARQL query support is implemented using µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
-Next the the presented scenario around geofences, we have also implemented a BLAST program to control and monitor an automated picking line to prepare orders in a more complex logistics scenario.
+The functionality to issue HTTP requests is implemented using the @@@ API/library, Social Linked Data (Solid) authentication is implemented using the @@@ library, and SPARQL query support is implemented using µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
+Next to the presented small scenario around geofences, we have also developed BLAST programs to control and monitor an automated picking line to prepare orders in a more complex logistics scenario.
 

### 2022-03-07 demo-eswc22/paper.tex
add webBluetooth restrictions

@@
 We are currently working on an execution environment that runs on Node.js as a way to execute BLAST programs independently of browsers.
+This will allow BLAST to use the full Bluetooth specification and not only features exposed by the Web Bluetooth API, which restricts the set of accessible GATT attributes in a blocklist~\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/\#the-gatt-blocklist}} to provide security and privacy protection.
 %To this end, we are developing an execution environment that can load BLAST programs, convert them to JavaScript, and execute them as a server.

### 2022-03-07 demo-eswc22/paper.tex
small corrections, add libraries/APIs

@@
 %Given the multitude of protocols for interacting with such devices, application development is difficult.
-The Web of Things (WoT)\footnote{\url{https://www.w3.org/WoT/}} aims at providing a set of standardised technologies to help simplify the creating of applications involving connected devices.
+The Web of Things (WoT)\footnote{\url{https://www.w3.org/WoT/}} aims at providing a set of standardised technologies to help simplify creating applications involving connected devices.
 At the same time, casual users should be able to quickly program applications involving connected devices.
 The programming languages currently in use for accessing devices are primarily text-based and are difficult to access for casual users.
-One possible approach to improve accessibility and simplify the creation of computer programs is the visual programming paradigm.
+One possible approach to improve accessibility and ease the creation of computer programs is the visual programming paradigm.
 
 Visual programming does not require the user to enter any text; instead, programs are based on graphical elements like blocks, graphs, tables or diagrams.
-Programs are created by arranging predefined blocks with images or text are arranged into programs via a drag-and-drop interface.
+Programs are created by arranging predefined blocks with images or text via a drag-and-drop interface.
 Blocks can be geometrically aligned with other compatible blocks, like in a jigsaw puzzle, to form complex programs.
@@
 BLAST programs can be created in a web browser, based on Google's Blockly\footnote{\url{https://developers.google.com/blockly/}}, a JavaScript library for creating block-based languages and editors.
-BLAST programs can be translated to JavaScript and executed in the web browser.
+BLAST programs can be translated into JavaScript and executed in the web browser.
 BLAST implements the Web of Things abstraction to devices with Bluetooth Low Energy (BLE) and USB Human Interface Devices (HID) interface via APIs of modern web browsers.
@@
 The currently best known tool for programming IoT devices using visual programming is Node-RED\footnote{\url{https://nodered.org/}}.
-Node-RED's programming paradigm is based on dataflows; in contrast, BLAST focuses on control flow constructs,
+Node-RED's programming paradigm is based on dataflows; in contrast, BLAST focuses on control flow constructs.
 The use cases in industrial settings we envision for BLAST involve mostly control flow, and in such scenarios a dataflow abstraction can lead to programs that are difficult to understand and maintain.
@@
 
-For an example for a BLAST program see figure \ref{fig1}.
+For an example of a BLAST program see figure \ref{fig1}.
 The program involves a LED light with a BLE interface and a small battery-powered BLE beacon.
@@
 
-We have implemented an editor and an execution environment for BLAST programs that runs in modern web browsers.
+We have implemented an editor and an execution environment for BLAST programs that run in modern web browsers.
 
 The editor uses the Blockly library and provides custom control and command blocks that make up the BLAST language.
-For execution, the editor generates JavaScript code that can be executed in the browser.
+Based on the user's arrangement of these blocks, the editor generates JavaScript code that can then be executed in the browser.
 The system builds on the Web Bluetooth API\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/}} and the WebHID API\footnote{\url{https://wicg.github.io/webhid/}} to interact with devices.
-The system uses the Web of Things abstraction as interface; we have implemented the WoT interface for eight devices the use the BLE GAP and GATT profiles as well as the USB Human Interface Devices (HID) interface.
+The system uses the Web of Things abstraction as interface; we have implemented the WoT interface for eight devices that use the BLE GAP and GATT profiles as well as the USB Human Interface Devices (HID) interface.
 The WoT interface contains the metadata and interaction affordances as well as the JavaScript code needed for communication.
@@
 Further, the system includes access to the Web Speech API\footnote{\url{https://wicg.github.io/speech-api/}}.
-The functionality to issue HTTP requests is implemented using the @@@ API/library, Social Linked Data (Solid) authentication is implemented using the @@@ library, and SPARQL query support is implemented using µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
+The functionality to issue HTTP requests is implemented using the fetch API~\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/API/Fetch\_API/Using\_Fetch}}, Social Linked Data (Solid) authentication is implemented using the inrupt solid library~\footnote{\url{https://docs.inrupt.com/developer-tools/javascript/client-libraries/}}, and SPARQL query support is implemented using µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
 Next to the presented small scenario around geofences, we have also developed BLAST programs to control and monitor an automated picking line to prepare orders in a more complex logistics scenario.

### 2022-03-07 demo-eswc22/paper.tex
shortened to 4 pages

@@
 
+\begin{figure}
+\includegraphics[width=.97\textwidth]{screenshot 3.png}%im Ordner sind noch 2 alternative Screenshots
+\caption{Example BLAST program that implements a geofencing scenario: when the beacon gets close, the light is turned off; when the beacon leaves the close range, a sound is played and the light is turned red.} \label{fig1}
+\end{figure}
+
 For an example of a BLAST program see figure \ref{fig1}.
@@
 To enable an event abstraction, the program includes a block that defines a state with a condition on the signal strength of the BLE beacon.
-On entering or exiting the defined state, the event blocks, which can contain arbitrary blocks, are triggered.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{screenshot 3.png}%im Ordner sind noch 2 alternative Screenshots
-\caption{Example BLAST program that implements a geofencing scenario: when the beacon gets close, the light is turned off; when the beacon leaves the close range, a sound is played and the light is turned red.} \label{fig1}
-\end{figure}
+On entering or exiting the defined state, the event blocks, which itself can contain arbitrary blocks, are triggered.
 
@@
 Further, the system includes access to the Web Speech API\footnote{\url{https://wicg.github.io/speech-api/}}.
-The functionality to issue HTTP requests is implemented using the fetch API~\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/API/Fetch\_API/Using\_Fetch}}, Social Linked Data (Solid) authentication is implemented using the inrupt solid library~\footnote{\url{https://docs.inrupt.com/developer-tools/javascript/client-libraries/}}, and SPARQL query support is implemented using µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
+The functionality to issue HTTP requests is based on the Fetch API\footnote{\url{https://fetch.spec.whatwg.org/}}, Social Linked Data (Solid) authentication is based on the Inrupt client libraries\footnote{\url{https://docs.inrupt.com/developer-tools/javascript/client-libraries/}}, and SPARQL query support is based on µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
 Next to the presented small scenario around geofences, we have also developed BLAST programs to control and monitor an automated picking line to prepare orders in a more complex logistics scenario.
@@
 We have presented BLAST, a block-based language that simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols.
-We are currently working on an execution environment that runs on Node.js as a way to execute BLAST programs independently of browsers.
-This will allow BLAST to use the full Bluetooth specification and not only features exposed by the Web Bluetooth API, which restricts the set of accessible GATT attributes in a blocklist~\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/\#the-gatt-blocklist}} to provide security and privacy protection.
+We are currently working on an execution environment that runs on Node.js as a way to execute BLAST programs independently of browsers, which impose restrictions on accessing devices to provide security and privacy protection.
+%This will allow BLAST to use the full Bluetooth specification and not only features exposed by the Web Bluetooth API, which restricts the set of accessible GATT attributes in a blocklist\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/\#the-gatt-blocklist}} to provide security and privacy protection.
 %To this end, we are developing an execution environment that can load BLAST programs, convert them to JavaScript, and execute them as a server.

### 2022-03-07 demo-eswc22/paper.tex
hid

@@
 The system builds on the Web Bluetooth API\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/}} and the WebHID API\footnote{\url{https://wicg.github.io/webhid/}} to interact with devices.
-The system uses the Web of Things abstraction as interface; we have implemented the WoT interface for eight devices that use the BLE GAP and GATT profiles as well as the USB Human Interface Devices (HID) interface.
+The system uses the Web of Things abstraction as interface; we have implemented the WoT interface for eight devices that use the BLE GAP and GATT profiles as well as the USB and Bluetooth HID interface.
 The WoT interface contains the metadata and interaction affordances as well as the JavaScript code needed for communication.

### 2022-03-07 demo-eswc22/paper.tex
source code
commented out code sentence

@@
 
-The created block programs can be translated into any predefined programming language, resulting in a normal source code. 
+%The created block programs can be translated into source code of any predefined programming language and then executed.
 The block-based approach can be used not only for learning programming concepts, but also for more complex problems.
-For example, block languages have been successfully used in constructing SPARQL queries~\cite{7369012} or programming industrial robots~\cite{8120406}~\cite{tomlein2017visual}, both areas which normally require advanced programming skills.
+Block languages have been successfully used in constructing SPARQL queries~\cite{7369012} or programming industrial robots~\cite{8120406}~\cite{tomlein2017visual}, both areas which normally require advanced programming skills.
 
@@
 \begin{figure}
-\includegraphics[width=.97\textwidth]{screenshot 3.png}%im Ordner sind noch 2 alternative Screenshots
+\includegraphics[width=\textwidth]{screenshot 3.png}%im Ordner sind noch 2 alternative Screenshots
 \caption{Example BLAST program that implements a geofencing scenario: when the beacon gets close, the light is turned off; when the beacon leaves the close range, a sound is played and the light is turned red.} \label{fig1}

### 2022-03-10 examples/web/sw.js
ready for merge

@@ -25,7 +25,7 @@ registerRoute(
     new CacheFirst(),
 );
 
-precacheAndRoute([{"revision":"0aaeb0deb3bd4bd32ec0e34e895c6ffc","url":"src/blocks.js"},{"revision":"72186d9b570faf5cff2aa2dac17888cb","url":"src/generators.js"},{"revision":"01eee06abcd0455d6e28db7d8a5d985b","url":"src/index.js"},{"revision":"3e07a041289aa1782c5f26fe22a87dcc","url":"src/screenshot.js"},{"revision":"4148d0ef95aa57b31aa7d2b09ec3aed9","url":"src/web.js"}]);
+precacheAndRoute([{"revision":"69b321a59218e7df177dd0994eee58b5","url":"src/blocks.js"},{"revision":"b4fd87468b122f33712e70f57cd83c71","url":"src/generators.js"},{"revision":"70388b3c0763d002418d43783f9bf86e","url":"src/index.js"},{"revision":"3ea2e9ae27194749899388040864d32c","url":"src/screenshot.js"},{"revision":"99da5321d19f10e5dcd1823a24b33be5","url":"src/web.js"}]);
 
 // Cache CSS, JS, and Web Worker requests with a Stale While Revalidate strategy
 registerRoute(

### 2022-03-10 dist/thingBlocks/joycon/generators.js
add joy-con button events

@@ -7,12 +7,11 @@
 'use strict';
 
 import {JavaScript} from 'blockly';
-import {JoyConLeft, JoyConRight} from './joycon-webhid/joycon.js';
 // eslint-disable-next-line node/no-missing-import
+import {addCleanUpFunction} from './../../blast_interpreter.js';
 import {JoyCon} from './../../things/joycon/JoyCon.js';
 import {apiFunctions} from './../../blast_interpreter.js';
 import {asyncApiFunctions} from './../../blast_interpreter.js';
-import {deviceEventHandlers} from './../../blast_interpreter.js';
 import {getInterpreter} from './../../blast_interpreter.js';
 import {getThingsLog} from './../../blast_things.js';
 import {getWebHidDevice} from './../../blast_things.js';
@@ -65,7 +64,7 @@ const readJoyConProperty = async function (
   const packet = await thing.readProperty(property);
   if (subValue2 !== '') {
     if (property === 'accelerometers') {
-      callback(packet[subValue][subValue2]);
+      callback(packet[subValue][subValue2]['acc']);
     } else if (property === 'gyroscopes') {
       callback(packet[subValue][subValue2][subValue3]);
     } else {
@@ -114,115 +113,50 @@ const handleJoyConButtons = async function (id, button, statements, callback) {
     return;
   }
 
-  const device = getWebHidDevice(id);
-
-  if (!device) {
-    throwError(
-      'Connected device is not a HID device.\nMake sure you are connecting the JoyCon via webHID'
-    );
-    callback();
-    return;
-  }
-
-  if (!device.opened) {
-    try {
-      await device.open();
-    } catch (error) {
-      throwError(
-        "Failed to open device, your browser or OS probably doesn't support webHID."
-      );
-    }
-  }
-
-  // Check if device is a Joy-Con.
-  if (
-    device.vendorId !== 1406 ||
-    (device.productId !== 0x2006 && device.productId !== 0x2007)
-  ) {
-    throwError('The connected device is not a Joy-Con.');
-    callback();
-    return;
-  }
-
-  let joyCon;
-  if (device.productId === 0x2006) {
-    joyCon = new JoyConLeft(device);
-  } else if (device.productId === 0x2007) {
-    joyCon = new JoyConRight(device);
-  }
-  await joyCon.open();
-  await joyCon.enableStandardFullMode();
-  await joyCon.enableIMUMode();
-
-  let pushedInLastPacket = false;
   const thingsLog = getThingsLog();
 
-  const hidInputHandler = async function (event) {
[…]

### 2022-03-10 dist/things/joycon/JoyCon.d.ts

@@ -1,15 +1,27 @@
 import * as WoT from 'wot-typescript-definitions';
+import type { Packet } from './types';
 export declare class JoyCon {
     private thing;
-    private device;
+    private exposedThing;
     private joyCon;
-    private log;
     private opened;
     private eventListenerAttached;
     td: WoT.ThingDescription;
     private webHidId;
+    private packet;
+    private inputHandler;
     thingModel: WoT.ThingDescription;
     constructor(webHidId: string);
     private open;
-    readProperty(property: string): Promise<any>;
+    readProperty(property: keyof Packet): Promise<any>;
+    private registerButtonEventEmitter;
+    /**
+     * Wrapper method for subscribing to JoyCon events.
+     */
+    subscribeEvent(eventName: string, fn: (...args: any[]) => void): Promise<void>;
+    /**
+     * Wrapper method for unsubscribing from all JoyCon events.
+     */
+    unsubscribeAll(): Promise<void>;
+    private destroy;
 }

### 2022-03-10 dist/things/joycon/JoyCon.js

@@ -1,14 +1,15 @@
-import { getThing } from '../index.js';
+import { getThing, removeThing } from '../index.js';
 import { JoyConLeft, JoyConRight } from 'joy-con-webhid';
-import { getThingsLog, getWebHidDevice } from '../../blast_things.js';
+import { getWebHidDevice } from '../../blast_things.js';
 import { throwError } from '../../blast_interpreter.js';
 export class JoyCon {
     constructor(webHidId) {
         this.thing = null;
-        this.device = null;
+        this.exposedThing = null;
         this.joyCon = null;
         this.opened = false;
         this.eventListenerAttached = false;
+        this.packet = null;
         this.thingModel = {
             '@context': ['https://www.w3.org/2019/wot/td/v1'],
             '@type': ['Thing'],
@@ -27,23 +28,65 @@ export class JoyCon {
                     description: 'The accelerometer of the joy-con',
                     type: 'object',
                     properties: {
-                        x: {
-                            title: 'X',
-                            description: 'The X-axis of the accelerometer',
-                            type: 'number',
-                            readOnly: true,
+                        1: {
+                            x: {
+                                title: 'X',
+                                description: 'The X-axis of the accelerometer',
+                                type: 'number',
+                                readOnly: true,
+                            },
+                            y: {
+                                title: 'Y',
+                                description: 'The Y-axis of the accelerometer',
+                                type: 'number',
+                                readOnly: true,
+                            },
+                            z: {
+                                title: 'Z',
+                                description: 'The Z-axis of the accelerometer',
+                                type: 'number',
+                                readOnly: true,
+                            },
                         },
-                        y: {
-                            title: 'Y',
-                            description: 'The Y-axis of the accelerometer',
-                            type: 'number',
-                            readOnly: true,
+                        2: {
+                            x: {
+                                title: 'X',
+                                description: 'The X-axis of the accelerometer',
+                                type: 'number',
+                                readOnly: true,
+                            },
+                            y: {
+                                title: 'Y',
+                                description: 'The Y-axis of the accelerometer',
+                                type: 'number',
+                                readOnly: true,
+                            },
+                            z: {
[…]

### 2022-03-10 dist/things/joycon/types.d.ts

@@ -1,0 +1,96 @@
+export interface Axis {
+    x: number;
+    y: number;
+    z: number;
+}
+export interface Quaternion extends Axis {
+    w: number;
+}
+export interface StatusWithHex {
+    _raw?: Uint8Array;
+    _hex?: Uint8Array;
+}
+interface Version {
+    major: number;
+    minor: number;
+}
+export interface DeviceInfo extends StatusWithHex {
+    firmwareVersion: Version;
+    type: string | undefined;
+    macAddress: string;
+    spiColorInUse: boolean;
+}
+export interface BatteryLevel extends StatusWithHex {
+    level: string;
+}
+export interface AnalogStick extends StatusWithHex {
+    horizontal: string;
+    vertical: string;
+}
+interface Acceleration extends StatusWithHex {
+    acc: number;
+}
+export interface Accelerometer {
+    x: Acceleration;
+    y: Acceleration;
+    z: Acceleration;
+}
+export interface Gyroscope extends StatusWithHex {
+    dps: number;
+    rps: number;
+}
+export interface EulerAngles {
+    alpha: string;
+    beta: string;
+    gamma: string;
+}
+export interface ButtonStatus extends StatusWithHex {
+    y: boolean;
+    x: boolean;
+    b: boolean;
+    a: boolean;
+    r: boolean;
+    zr: boolean;
+    down: boolean;
+    up: boolean;
+    right: boolean;
+    left: boolean;
+    l: boolean;
+    zl: boolean;
+    sr: boolean;
+    sl: boolean;
+    minus: boolean;
+    plus: boolean;
+    rightStick: boolean;
+    leftStick: boolean;
+    home: boolean;
+    capture: boolean;
+    chargingGrip: boolean;
+}
+export interface Packet {
+    inputReportID?: StatusWithHex;
+    buttonStatus?: Partial<ButtonStatus>;
+    analogStick?: StatusWithHex;
+    filter?: StatusWithHex;
+    timer?: StatusWithHex;
+    batteryLevel?: BatteryLevel;
+    connectionInfo?: StatusWithHex;
+    analogStickLeft?: AnalogStick;
+    analogStickRight?: AnalogStick;
+    vibrator?: StatusWithHex;
+    ack?: StatusWithHex;
+    subcommandID?: StatusWithHex;
+    subcommandReplyData?: StatusWithHex;
+    deviceInfo?: DeviceInfo;
[…]

### 2022-03-10 dist/things/streamdeck/StreamDeck.d.ts

@@ -36,7 +36,7 @@ export declare class StreamDeck {
     /**
      * Registers buttonUp and buttonDown event emitters.
      */
-    private registerButtonUpDownEvenEmitters;
+    private registerButtonUpDownEventEmitters;
     /**
      * Wrapper method for emitting streamdeck events.
      */

### 2022-03-10 dist/things/streamdeck/StreamDeck.js

@@ -72,7 +72,7 @@ export class StreamDeck {
             this.td = thing.getThingDescription();
             this.open().then(sd => {
                 this.streamdeck = sd;
-                this.registerButtonUpDownEvenEmitters();
+                this.registerButtonUpDownEventEmitters();
             });
             this.thing.expose();
         });
@@ -213,7 +213,7 @@ export class StreamDeck {
     /**
      * Registers buttonUp and buttonDown event emitters.
      */
-    async registerButtonUpDownEvenEmitters() {
+    async registerButtonUpDownEventEmitters() {
         var _a, _b;
         while (!this.opened) {
             // Wait for the thing to be initialized

### 2022-03-10 src/things/joycon/JoyCon.ts

@@ -1,18 +1,21 @@
 import * as WoT from 'wot-typescript-definitions';
-import {getThing} from '../index.js';
+import {getThing, removeThing} from '../index.js';
 import {JoyConLeft, JoyConRight} from 'joy-con-webhid';
-import {getThingsLog, getWebHidDevice} from '../../blast_things.js';
+import {getWebHidDevice, thingsFlyoutCategory} from '../../blast_things.js';
 import {throwError} from '../../blast_interpreter.js';
+import type {Packet} from './types';
+import { ExposedThing } from '@node-wot/core';
 
 export class JoyCon {
   private thing: WoT.ExposedThing | null = null;
-  private device: HIDDevice | null = null;
+  private exposedThing: ExposedThing | null = null;
   private joyCon: JoyConLeft | JoyConRight | null = null;
-  private log: Function;
   private opened = false;
   private eventListenerAttached = false;
   public td: WoT.ThingDescription;
   private webHidId: string;
+  private packet: Packet | null = null;
+  private inputHandler: Function | undefined;
 
   public thingModel: WoT.ThingDescription = {
     '@context': ['https://www.w3.org/2019/wot/td/v1'],
@@ -32,23 +35,65 @@ export class JoyCon {
         description: 'The accelerometer of the joy-con',
         type: 'object',
         properties: {
-          x: {
-            title: 'X',
-            description: 'The X-axis of the accelerometer',
-            type: 'number',
-            readOnly: true,
+          1: {
+            x: {
+              title: 'X',
+              description: 'The X-axis of the accelerometer',
+              type: 'number',
+              readOnly: true,
+            },
+            y: {
+              title: 'Y',
+              description: 'The Y-axis of the accelerometer',
+              type: 'number',
+              readOnly: true,
+            },
+            z: {
+              title: 'Z',
+              description: 'The Z-axis of the accelerometer',
+              type: 'number',
+              readOnly: true,
+            },
           },
-          y: {
-            title: 'Y',
-            description: 'The Y-axis of the accelerometer',
-            type: 'number',
-            readOnly: true,
+          2: {
+            x: {
+              title: 'X',
+              description: 'The X-axis of the accelerometer',
+              type: 'number',
+              readOnly: true,
+            },
+            y: {
+              title: 'Y',
+              description: 'The Y-axis of the accelerometer',
+              type: 'number',
+              readOnly: true,
+            },
+            z: {
[…]

### 2022-03-10 src/things/streamdeck/StreamDeck.ts

@@ -81,7 +81,7 @@ export class StreamDeck {
       this.td = thing.getThingDescription();
       this.open().then(sd => {
         this.streamdeck = sd;
-        this.registerButtonUpDownEvenEmitters();
+        this.registerButtonUpDownEventEmitters();
       });
       this.thing.expose();
     });
@@ -256,7 +256,7 @@ export class StreamDeck {
   /**
    * Registers buttonUp and buttonDown event emitters.
    */
-  private async registerButtonUpDownEvenEmitters() {
+  private async registerButtonUpDownEventEmitters() {
     while (!this.opened) {
       // Wait for the thing to be initialized
       await new Promise(resolve => setTimeout(resolve, 100));

### 2022-03-10 src/thingBlocks/joycon/generators.js
statisfy linter

@@ -9,12 +9,12 @@
 import {JavaScript} from 'blockly';
 // eslint-disable-next-line node/no-missing-import
 import {addCleanUpFunction} from './../../blast_interpreter.js';
+// eslint-disable-next-line node/no-missing-import
 import {JoyCon} from './../../things/joycon/JoyCon.js';
 import {apiFunctions} from './../../blast_interpreter.js';
 import {asyncApiFunctions} from './../../blast_interpreter.js';
 import {getInterpreter} from './../../blast_interpreter.js';
 import {getThingsLog} from './../../blast_things.js';
-import {getWebHidDevice} from './../../blast_things.js';
 import {setInterrupted} from './../../blast_interpreter.js';
 import {throwError} from './../../blast_interpreter.js';
 

### 2022-04-06 demo-eswc22/paper.tex
style guide says FAU in german
final version of ESWC 22 paper
improve paper according to reviewers’ comments

@@
 \and
-Friedrich–Alexander University Erlangen-Nürnberg, Nürnberg, Germany}
+Friedrich-Alexander-Universität Erlangen-Nürnberg, Nürnberg, Germany}
 %
@@
   In particular we show the use of connected devices in a geofencing scenario.
-\keywords{Block-based Programming \and Web of Things.}
+\keywords{Block-based Programming \and Web of Things \and Graphical Programming.}
 \end{abstract}
@@
 Blocks can be geometrically aligned with other compatible blocks, like in a jigsaw puzzle, to form complex programs.
-Since blocks can only be arranged in the correct way, no syntax errors can occur~\cite{10.11453341221}~\cite{maloney2010scratch}~\cite{10.1145/1089733.1089734}.
+Since blocks can only be arranged in the correct way, no syntax errors can occur~\cite{10.1145/1089733.1089734}~\cite{maloney2010scratch}~\cite{10.11453341221}.
 
@@
 The block-based approach can be used not only for learning programming concepts, but also for more complex problems.
-Block languages have been successfully used in constructing SPARQL queries~\cite{7369012} or programming industrial robots~\cite{8120406}~\cite{tomlein2017visual}, both areas which normally require advanced programming skills.
+Block languages have been successfully used in constructing SPARQL queries~\cite{7369012} or programming industrial robots~\cite{tomlein2017visual}~\cite{8120406}, both areas which normally require advanced programming skills.
 
@@
 The editor uses the Blockly library and provides custom control and command blocks that make up the BLAST language.
+The custom blocks and the BLAST environment in general follow all the important design principles introduced by Fraser \cite{fraser}, such as a clear border style or the avoidance of transitive connections.
 Based on the user's arrangement of these blocks, the editor generates JavaScript code that can then be executed in the browser.
 The system builds on the Web Bluetooth API\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/}} and the WebHID API\footnote{\url{https://wicg.github.io/webhid/}} to interact with devices.
-The system uses the Web of Things abstraction as interface; we have implemented the WoT interface for eight devices that use the BLE GAP and GATT profiles as well as the USB and Bluetooth HID interface.
+BLAST uses the Web of Things abstraction as interface; we have implemented the WoT interface for eight devices that use the BLE GAP and GATT profiles as well as the USB and Bluetooth HID interface.
 The WoT interface contains the metadata and interaction affordances as well as the JavaScript code needed for communication.
@@
 The functionality to issue HTTP requests is based on the Fetch API\footnote{\url{https://fetch.spec.whatwg.org/}}, Social Linked Data (Solid) authentication is based on the Inrupt client libraries\footnote{\url{https://docs.inrupt.com/developer-tools/javascript/client-libraries/}}, and SPARQL query support is based on µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
-Next to the presented small scenario around geofences, we have also developed BLAST programs to control and monitor an automated picking line to prepare orders in a more complex logistics scenario.
+Next to the presented small scenario around geofences, we have also developed BLAST programs to accomplish five use cases\footnote{TODO: URI to videos} with varying complexity.
+Each use case introduces a different challenge that requiers the use of programming pattern in combination with the built-in blocks for properties, actions, events, requests and queries.
+
+\section{Usability Evaluation }
+There is a large number of standardized questionnaires in scientific literature that allow test users to evaluate the usability of a software product.
+We use the System Usability Scale (SUS) questionnaire to evaluate the user friendliness of BLAST.
+According to Assila et.
+al.
+\cite{assila2016standardized}, SUS provides reliable results over different sample sizes and converges fast to the correct conclusion.
+
+We conducted an evaluation with nine participants.
+None of the participants had background knowledge regarding the Web of Things, RDF, or SPARQL.
+Participants were first asked to solve four tasks using BLAST, these included a simple "Hello World!" program, a periodic polling of RSSI data by using a loop, reading data from a connected IoT device, and as a final task, reading data and processing it using logical operators.
+After the successful completion of these tasks, the participants filled out the SUS questionnaires.
+The achieved SUS score across all questionnaires is 81.4 out of 100 possible points, which corresponds to good usability.
+
+It should be noted that the survey was conducted with an older version of BLAST. However, the user interface has changed only minimally since then, which is why the results are still relevant.
 
@@
 
-We have presented BLAST, a block-based language that simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols.
+We have introduced BLAST, a block-based language that simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols.
 We are currently working on an execution environment that runs on Node.js as a way to execute BLAST programs independently of browsers, which impose restrictions on accessing devices to provide security and privacy protection.

### 2022-04-06 demo-eswc22/paper.tex
fixed spelling errors

@@
 The editor uses the Blockly library and provides custom control and command blocks that make up the BLAST language.
-The custom blocks and the BLAST environment in general follow all the important design principles introduced by Fraser \cite{fraser}, such as a clear border style or the avoidance of transitive connections.
+The custom blocks and the BLAST environment follow all the important design principles introduced by Fraser \cite{fraser}, such as a clear border style or the avoidance of transitive connections.
 Based on the user's arrangement of these blocks, the editor generates JavaScript code that can then be executed in the browser.
@@
 Next to the presented small scenario around geofences, we have also developed BLAST programs to accomplish five use cases\footnote{TODO: URI to videos} with varying complexity.
-Each use case introduces a different challenge that requiers the use of programming pattern in combination with the built-in blocks for properties, actions, events, requests and queries.
+Each use case introduces a different challenge that requires the use of programming patterns in combination with the built-in blocks for properties, actions, events, requests, and queries.
 
 \section{Usability Evaluation }
-There is a large number of standardized questionnaires in scientific literature that allow test users to evaluate the usability of a software product.
-We use the System Usability Scale (SUS) questionnaire to evaluate the user friendliness of BLAST.
-According to Assila et.
-al.
+There is a large number of standardized questionnaires in the scientific literature that allow test users to evaluate the usability of a software product.
+We use the System Usability Scale (SUS) questionnaire to evaluate the user-friendliness of BLAST.
+According to Assila et al.
 \cite{assila2016standardized}, SUS provides reliable results over different sample sizes and converges fast to the correct conclusion.
@@
 None of the participants had background knowledge regarding the Web of Things, RDF, or SPARQL.
-Participants were first asked to solve four tasks using BLAST, these included a simple "Hello World!" program, a periodic polling of RSSI data by using a loop, reading data from a connected IoT device, and as a final task, reading data and processing it using logical operators.
+Participants were first asked to solve four tasks using BLAST, these included a simple "Hello World!" program, periodic polling of RSSI data by using a loop, reading data from a connected IoT device, and as a final task, reading data and processing it using logical operators.
 After the successful completion of these tasks, the participants filled out the SUS questionnaires.

### 2022-04-07 dist/blast_eddystone.js
Update Eddystone WoT implementation

@@ -34,6 +34,22 @@ const UUIDS = {
   REMAIN_CONNECTABLE_CHARACTERISTIC: 'a3c8750c-8ed3-4bdf-8a39-a01bebede295',
 };
 
+export const eddystoneProperties = new Map();
+eddystoneProperties.set(UUIDS.ACTIVE_SLOT_CHARACTERISTIC, 'activeSlot');
+eddystoneProperties.set(
+  UUIDS.ADVERTISED_TX_POWER_CHARACTERISTIC,
+  'advertisedTxPower'
+);
+eddystoneProperties.set(UUIDS.ADV_SLOT_DATA_CHARACTERISTIC, 'advertisedData');
+eddystoneProperties.set(
+  UUIDS.ADVERTISING_INTERVAL_CHARACTERISTIC,
+  'advertisingInterval'
+);
+eddystoneProperties.set(UUIDS.CAPABILITIES_CHARACTERISTIC, 'capabilities');
+eddystoneProperties.set(UUIDS.LOCK_STATE_CHARACTERISTIC, 'lockState');
+eddystoneProperties.set(UUIDS.PUBLIC_ECDH_KEY_CHARACTERISTIC, 'publicEcdhKey');
+eddystoneProperties.set(UUIDS.RADIO_TX_POWER_CHARACTERISTIC, 'radioTxPower');
+
 // Add Eddystone config service to optionalServices to make it accessible.
 optionalServices.push(UUIDS.CONFIG_SERVICE);
 
@@ -42,16 +58,33 @@ optionalServices.push(UUIDS.CONFIG_SERVICE);
  * @param {BluetoothDevice.id} webBluetoothId A DOMString that uniquely identifies a device.
  * @return {!Promise} A promise that resolves when the operation is complete.
  */
-const getCapabilities = async function (webBluetoothId) {
+export const getCapabilities = async function (webBluetoothId) {
   const thingsLog = getThingsLog();
   thingsLog('Reading Eddystone capabilities...', 'Eddystone', webBluetoothId);
   // Get the capabilities.
-  let capabilitiesArray = await read(
+  const capabilitiesArray = await read(
     webBluetoothId,
     UUIDS.CONFIG_SERVICE,
     UUIDS.CAPABILITIES_CHARACTERISTIC
   );
-  capabilitiesArray = new Int8Array(capabilitiesArray.buffer);
+  const capabilities = parseCapabilities(capabilitiesArray);
+
+  thingsLog(
[…]

### 2022-04-07 dist/thingBlocks/ble_rgb_led_controller/generators.js

@@ -14,7 +14,7 @@ import {
   throwError,
 } from './../../blast_interpreter.js';
 // eslint-disable-next-line node/no-missing-import
-import {encodeJson} from './../../things/bindings/binding-helpers.js';
+import {stringToReadble} from './../../things/bindings/binding-helpers.js';
 
 /**
  * Generates JavaScript code for the things_bleLedController block.
@@ -66,12 +66,9 @@ const switchLights = async function (
     return;
   }
   // convert data to json
-  const data = {
-    device: webBluetoothId,
-    value: '7e000503' + colour.substring(1, 7) + '00ef',
-  };
+  const data = '7e000503' + colour.substring(1, 7) + '00ef';
   // convert json to stream
-  const stream = encodeJson(data);
+  const stream = stringToReadble(data);
   // get thing instance of block
   const block = getWorkspace().getBlockById(blockId);
   const thing = await block.thing;

### 2022-04-07 dist/thingBlocks/bluetooth/blocks.js

@@ -11,6 +11,61 @@ import {implementedThings} from '../../blast_things.js';
 // eslint-disable-next-line node/no-missing-import
 import EddystoneDevice from '../../things/eddystone/EddystoneDevice.js';
 
+Blocks['things_eddyStoneDevice'] = {
+  /**
+   * Block representing an Eddystone device.
+   * @this {Blockly.Block}
+   */
+  init: function () {
+    this.appendDummyInput()
+      .appendField('Eddystone device')
+      .appendField(new FieldTextInput('Error getting name'), 'name');
+    this.appendDummyInput()
+      .appendField(new FieldTextInput('Error getting id'), 'id')
+      .setVisible(false);
+    this.setOutput(true, 'Thing');
+    this.setColour(60);
+    this.setTooltip('An Eddystone device.');
+    this.setHelpUrl(
+      'https://github.com/wintechis/blast/wiki/Eddystone-Devices'
+    );
+    this.getField('name').setEnabled(false);
+    this.firstTime = true;
+    this.webBluetoothId = '';
+    this.thing = null;
+  },
+  onchange: function () {
+    // on creating this block initialize new instance of BleRgbController
+    if (!this.isInFlyout && this.firstTime && this.rendered) {
+      this.webBluetoothId = this.getFieldValue('id');
+      this.firstTime = false;
+      new EddystoneDevice().init(this.webBluetoothId).then(thing => {
+        this.thing = thing;
+      });
+    }
+  },
+};
+
+Blocks['things_bluetoothGeneric'] = {
+  /**
+   * Block representing a generic Bluetooth device.
+   * @this {Blockly.Block}
+   */
+  init: function () {
+    this.appendDummyInput()
+      .appendField('generic Bluetooth device')
+      .appendField(new FieldTextInput('Error getting name'), 'name');
+    this.appendDummyInput()
+      .appendField(new FieldTextInput('Error getting id'), 'id')
+      .setVisible(false);
+    this.setOutput(true, 'Thing');
+    this.setColour(60);
+    this.setTooltip('A Generic Bluetooth device.');
+    this.getField('name').setEnabled(false);
+    this.firstTime = true;
+  },
+};
+
 Blocks['get_signal_strength_wb'] = {
   /**
    * Block for reading the strength of the signal (rssiValue property) sent by a ble device,
@@ -132,7 +187,7 @@ Blocks['read_eddystone_property'] = {
       .appendField(
         new FieldDropdown([
[…]

### 2022-04-07 dist/thingBlocks/joycon/generators.js

@@ -141,7 +141,6 @@ const handleJoyConButtons = async function (
   const thingsLog = getThingsLog();
 
   const handler = async function (data) {
-    console.log(data);
     if (data === button) {
       thingsLog(
         `Received <code>hidinput</code> event from Joy-Con: <code>${JSON.stringify(

### 2022-04-07 dist/things/bindings/binding-helpers.d.ts

@@ -1,11 +1,29 @@
 /**
- * Decodes a ReadableStream into JSON
+ * Decodes a ReadableStream into JSON.
  * @param data The ReadableStream to decode
  * @returns The decoded JSON
  */
-export declare const decodeReadableStream: (data: NodeJS.ReadableStream) => Promise<any>;
+export declare const readableStreamToJson: (data: NodeJS.ReadableStream) => Promise<any>;
+/**
+ * Converts a ReadableStream into a string.
+ * @param data The ReadableStream to convert
+ * @returns The converted string
+ */
+export declare const readableStreamToString: (data: NodeJS.ReadableStream) => Promise<string>;
 /**
  * Endocdes json data into a ReadableStream.
  * @param {JSON} data the data to encode
  */
-export declare const encodeJson: (data: JSON) => ReadableStream;
+export declare const jsonToReadble: (data: JSON) => ReadableStream;
+/**
+ * Converts a string into a ReadableStream.
+ * @param str The string to convert
+ * @returns The converted ReadableStream
+ */
+export declare const stringToReadble: (str: string) => ReadableStream;
+/**
+ * Converts a string into a NodeJS.ReadableStream.
+ * @param data The string to convert
+ * @returns The converted string as a ReadableStream
+ */
+export declare const stringToNodeReadable: (data: string) => NodeJS.ReadableStream;

### 2022-04-07 src/blast_webBluetooth.d.ts

@@ -76,7 +76,7 @@ export async function read(
   id: BluetoothDevice.id,
   serviceUUID: BluetoothServiceUUID,
   characteristicUUID: BluetoothCharacteristicUUID
-): Promise<string>;
+): Promise<DataView>;
 
 /**
  * Reads a text (UTF-8) characteristic value from a Bluetooth device.

### 2022-04-07 src/thingBlocks/blinkstick/generators.js

@@ -14,7 +14,7 @@ import {
   throwError,
 } from './../../blast_interpreter.js';
 // eslint-disable-next-line node/no-missing-import
-import {encodeJson} from './../../things/bindings/binding-helpers.js';
+import {jsonToReadble} from './../../things/bindings/binding-helpers.js';
 
 JavaScript['blinkstick_set_colors'] = function (block) {
   const colour =
@@ -80,7 +80,7 @@ const blinkstickSetColors = async function (
   // create report
   const reportId = 5;
   const report = [reportId, index, red, green, blue];
-  const stream = encodeJson({reportId, report});
+  const stream = jsonToReadble({reportId, report});
 
   const block = getWorkspace().getBlockById(blockId);
   const thing = block.thing;

### 2022-04-07 src/things/bindings/binding-helpers.ts

@@ -1,9 +1,11 @@
+import {Readable} from 'stream';
+
 /**
- * Decodes a ReadableStream into JSON
+ * Decodes a ReadableStream into JSON.
  * @param data The ReadableStream to decode
  * @returns The decoded JSON
  */
-export const decodeReadableStream = async function (
+export const readableStreamToJson = async function (
   data: NodeJS.ReadableStream
 ) {
   const chunks = [];
@@ -16,10 +18,26 @@ export const decodeReadableStream = async function (
 };
 
 /**
+ * Converts a ReadableStream into a string.
+ * @param data The ReadableStream to convert
+ * @returns The converted string
+ */
+export const readableStreamToString = async function (
+  data: NodeJS.ReadableStream
+) {
+  const chunks = [];
+  for await (const chunk of data) {
+    chunks.push(chunk as Buffer);
+  }
+  const buffer = Buffer.concat(chunks);
+  return new TextDecoder().decode(buffer);
+};
+
+/**
  * Endocdes json data into a ReadableStream.
  * @param {JSON} data the data to encode
  */
-export const encodeJson = function (data: JSON): ReadableStream {
+export const jsonToReadble = function (data: JSON): ReadableStream {
   const encoder = new TextEncoder();
   const jsonArr = encoder.encode(JSON.stringify(data));
 
@@ -29,4 +47,37 @@ export const encodeJson = function (data: JSON): ReadableStream {
       controller.close();
     },
   });
+};
+
+/**
+ * Converts a string into a ReadableStream.
+ * @param str The string to convert
+ * @returns The converted ReadableStream
+ */
+export const stringToReadble = function (str: string): ReadableStream {
+  const encoder = new TextEncoder();
+  const strArr = encoder.encode(str);
+
+  return new ReadableStream({
+    start(controller) {
+      controller.enqueue(strArr);
+      controller.close();
+    },
+  });
+};
+
+/**
+ * Converts a string into a NodeJS.ReadableStream.
+ * @param data The string to convert
+ * @returns The converted string as a ReadableStream
+ */
+export const stringToNodeReadable = function (
+  data: string
+): NodeJS.ReadableStream {
+  // create a new NodeJS.ReadableStream and push the data into it
+  const readable = new Readable();
+  readable.push(data);
+  readable.push(null);
+
+  return readable;
 };

### 2022-04-07 src/things/bindings/binding-webBluetooth/webBluetooth-client.ts

@@ -3,7 +3,6 @@
  */
 
 import {Content, ProtocolClient} from '@node-wot/core';
-import {Readable} from 'stream';
 import {Form, SecurityScheme} from '@node-wot/td-tools';
 import {
   readHex,
@@ -12,9 +11,17 @@ import {
   writeWithoutResponse,
   writeWithResponse,
 } from '../../../blast_webBluetooth.js';
+import {
+  eddystoneProperties,
+  readEddystoneProperty,
+  writeEddystoneProperty,
+} from './../../../blast_eddystone.js';
 import {Subscription} from 'rxjs/Subscription';
 import {WebBluetoothForm} from './webBluetooth.js';
-import {decodeReadableStream} from '../binding-helpers.js';
+import {
+  readableStreamToString,
+  stringToNodeReadable,
+} from '../binding-helpers.js';
 
 export default class WebBluetoothClient implements ProtocolClient {
   public toString(): string {
@@ -106,16 +113,41 @@ export default class WebBluetoothClient implements ProtocolClient {
     characteristicId: BluetoothCharacteristicUUID,
     operation = 'readText'
   ) {
-    const readable = new Readable();
+    let property: string;
+    let value = '';
     switch (operation) {
       case 'readText':
-        readable.push(await readText(deviceId, serviceId, characteristicId));
+        console.debug(
+          '[binding-webBluetooth]',
+          `invoking readText with serviceId ${serviceId} characteristicId ${characteristicId}`
+        );
+        value = await readText(deviceId, serviceId, characteristicId);
         break;
       case 'readNumber':
-        readable.push(await readNumber(deviceId, serviceId, characteristicId));
+        console.debug(
+          '[binding-webBluetooth]',
+          `invoking readNumber with serviceId ${serviceId} characteristicId ${characteristicId}`
+        );
+        value = (
+          await readNumber(deviceId, serviceId, characteristicId)
+        ).toString();
         break;
       case 'readHex':
-        readable.push(await readHex(deviceId, serviceId, characteristicId));
+        console.debug(
+          '[binding-webBluetooth]',
+          `invoking readHex with serviceId ${serviceId} characteristicId ${characteristicId}`
+        );
+        value = await readHex(deviceId, serviceId, characteristicId);
+        break;
+      case 'readEddystoneProperty':
+        property = eddystoneProperties.get(characteristicId) || '';
+        if (property) {
+          console.debug(
+            '[binding-webBluetooth]',
+            `invoking readEddystoneProperty with property ${property}`
+          );
[…]

### 2022-04-07 src/things/eddystone/EddystoneDevice.ts

@@ -1,174 +1,163 @@
 import * as WoT from 'wot-typescript-definitions';
-import {
-  getActiveSlot,
-  readEddystoneProperty,
-  setActiveSlot,
-  writeEddystoneProperty,
-} from '../../blast_eddystone.js';
-import {getThing, removeThing} from '../index.js';
+import {getWot} from '../index.js';
 
 export default class EddystoneDevice {
-  public thing: WoT.ExposedThing | null = null;
-  private td: WoT.ThingDescription | null = null;
-  private webBluetoothId: string;
-  private slot = -1;
+  public thing: WoT.ConsumedThing | null = null;
 
-  public thingModel: WoT.ThingDescription = {
-    '@context': ['https://www.w3.org/2019/wot/td/v1'],
-    '@type': ['Thing'],
-    id: 'blast:bluetooth:EddystoneDevice',
-    title: 'Eddystone Device',
-    description: 'A Bluetooth device implementing the Eddystone protocol',
-    securityDefinitions: {
-      nosec_sc: {
-        scheme: 'nosec',
+  public async init(webBluetoothId: string) {
+    const td: WoT.ThingDescription = {
+      '@context': ['https://www.w3.org/2019/wot/td/v1'],
+      '@type': ['Thing'],
+      id: 'blast:bluetooth:EddystoneDevice',
+      title: 'Eddystone Device',
+      description: 'A Bluetooth device implementing the Eddystone protocol',
+      securityDefinitions: {
+        nosec_sc: {
+          scheme: 'nosec',
+        },
       },
-    },
-    security: 'nosec_sc',
-    properties: {
-      advertisedTxPower: {
-        title: 'Advertised Tx Power',
-        description: 'The advertised TX power of the iBeacon',
-        unit: 'dBm',
-        type: 'integer',
-        readOnly: false,
-        forms: [
-          {
-            href: '',
-          },
-        ],
+      security: 'nosec_sc',
+      properties: {
+        activeSlot: {
+          title: 'Active Slot',
+          description: 'The active slot of the Eddystone device',
+          type: 'integer',
+          readOnly: false,
+          forms: [
+            {
+              op: 'readproperty',
+              href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87502-8ed3-4bdf-8a39-a01bebede295/readEddystoneProperty',
+              'wbt:id': webBluetoothId,
+            },
+            {
+              op: 'writeproperty',
[…]

### 2022-04-08 demo-eswc22/paper.tex
Update demo-eswc22/paper.tex
Co-authored-by: Thomas Wehr <derwehr@gmail.com>

@@
 None of the participants had background knowledge regarding the Web of Things, RDF, or SPARQL.
-Participants were first asked to solve four tasks using BLAST, these included a simple "Hello World!" program, periodic polling of RSSI data by using a loop, reading data from a connected IoT device, and as a final task, reading data and processing it using logical operators.
+Participants were first asked to solve four tasks using BLAST, these included a simple ``Hello World!'' program, periodic polling of RSSI data by using a loop, reading data from a connected IoT device, and as a final task, reading data and processing it using logical operators.
 After the successful completion of these tasks, the participants filled out the SUS questionnaires.

### 2022-04-08 demo-eswc22/paper.tex
Update demo-eswc22/paper.tex
Co-authored-by: Thomas Wehr <derwehr@gmail.com>

@@
 \section{Usability Evaluation }
-There is a large number of standardized questionnaires in the scientific literature that allow test users to evaluate the usability of a software product.
-We use the System Usability Scale (SUS) questionnaire to evaluate the user-friendliness of BLAST.
+For evaluating the usability of BLAST, we employ the System Usability Scale (SUS) questionnaire.
 According to Assila et al.

### 2022-04-08 demo-eswc22/paper/paper.tex
add exception to used Blockly guidelines

--- 2022-04-08 demo-eswc22/paper.tex
@@
 The editor uses the Blockly library and provides custom control and command blocks that make up the BLAST language.
-The custom blocks and the BLAST environment follow all the important design principles introduced by Fraser \cite{fraser}, such as a clear border style or the avoidance of transitive connections.
-Based on the user's arrangement of these blocks, the editor generates JavaScript code that can then be executed in the browser.
+The custom blocks and the BLAST environment follow almost all of the design principles introduced by Fraser \cite{fraser}, such as a clear border style or the avoidance of transitive connections.
+Not implemented, however, are the varying color choices for different loops.
+
+Based on the user's arrangement of the blocks, the editor generates JavaScript code that can then be executed in the browser.
 The system builds on the Web Bluetooth API\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/}} and the WebHID API\footnote{\url{https://wicg.github.io/webhid/}} to interact with devices.

### 2022-04-08 src/thingBlocks/bluetooth/generators.js
update HuskyDuino WoT implementation

@@ -8,7 +8,7 @@
 
 import {JavaScript} from 'blockly';
 import {
-  stringToReadble,
+  stringToReadable,
   readableStreamToString,
   // eslint-disable-next-line node/no-missing-import
 } from '../../things/bindings/binding-helpers.js';
@@ -129,10 +129,10 @@ const writeEddystoneProperty = async function (
   const block = getWorkspace().getBlockById(blockId);
   const thing = block.thing;
   // Set the active slot
-  const slotReadable = stringToReadble(slot);
+  const slotReadable = stringToReadable(slot);
   await thing.writeProperty('activeSlot', slotReadable);
   // Write the property
-  const valueReadable = stringToReadble(value);
+  const valueReadable = stringToReadable(value);
   await thing.writeProperty(property, valueReadable);
 
   callback();
@@ -201,7 +201,7 @@ const readEddystoneProperty = async function (
   const block = getWorkspace().getBlockById(blockId);
   const thing = block.thing;
   // Set the active slot
-  const slotReadable = stringToReadble(slot);
+  const slotReadable = stringToReadable(slot);
   await thing.writeProperty('activeSlot', slotReadable);
   // Read property data
   const interActionInput = await thing.readProperty(property);

### 2022-04-08 src/thingBlocks/huskyduino/blocks.js

@@ -37,8 +37,10 @@ Blocks['things_huskylens'] = {
     // on creating this block initialize new instance of BleRgbController
     if (!this.isInFlyout && this.firstTime && this.rendered) {
       this.webBluetoothId = this.getFieldValue('id');
-      this.thing = new HuskyDuino(this.webBluetoothId);
       this.firstTime = false;
+      new HuskyDuino().init(this.webBluetoothId).then(thing => {
+        this.thing = thing;
+      });
     }
   },
 };

### 2022-04-08 src/thingBlocks/huskyduino/generators.js

@@ -9,7 +9,8 @@
 
 import {JavaScript} from 'blockly';
 import {asyncApiFunctions, getWorkspace} from './../../blast_interpreter.js';
-import {optionalServices} from './../../blast_webBluetooth.js';
+// eslint-disable-next-line node/no-missing-import
+import {readableStreamToString, stringToReadable} from '../../things/bindings/binding-helpers.js';
 
 /**
  * Generates JavaScript code for the things_huskylens block.
@@ -96,10 +97,6 @@ JavaScript['huskylens_read_id'] = function (block) {
   return [code, JavaScript.ORDER_NONE];
 };
 
-// set the service UUID here， for all characteristics
-const HuskyServiceUUID = '5be35d20-f9b0-11eb-9a03-0242ac130003';
-optionalServices.push(HuskyServiceUUID);
-
 /**
  * Write the choosen algorithm value to Huskyduino via bluetooth
  * @param {Blockly.Block.id} blockId the things_bleLedController block's id.
@@ -107,9 +104,12 @@ optionalServices.push(HuskyServiceUUID);
  * @param {JSInterpreter.AsyncCallback} callback JS Interpreter callback.
  */
 const chooseAlgo = async function (blockId, value, callback) {
+  // Get thing instance of block.
   const block = getWorkspace().getBlockById(blockId);
   const thing = block.thing;
-  await thing.writeProperty('algorithm', value);
+  // Write face id to thing.
+  const valueReadable = stringToReadable(value);
+  await thing.writeProperty('algorithm', valueReadable);
   callback();
 };
 
@@ -122,9 +122,12 @@ asyncApiFunctions.push(['chooseAlgo', chooseAlgo]);
  * @param {JSInterpreter.AsyncCallback} callback JS Interpreter callback.
  */
 const learnID = async function (blockId, value, callback) {
+  // Get thing instance of block.
   const block = getWorkspace().getBlockById(blockId);
   const thing = block.thing;
-  await thing.writeProperty('id', value);
+  // Write face id to thing.
+  const valueReadable = stringToReadable(value);
+  await thing.writeProperty('id', valueReadable);
   callback();
 };
 
@@ -137,8 +140,10 @@ asyncApiFunctions.push(['learnID', learnID]);
  * @param {JSInterpreter.AsyncCallback} callback JS Interpreter callback.
  */
 const forgetAll = async function (blockId, callback) {
+  // Get thing instance of block.
   const block = getWorkspace().getBlockById(blockId);
   const thing = block.thing;
[…]

### 2022-04-08 src/things/bindings/binding-helpers.ts

@@ -54,7 +54,7 @@ export const jsonToReadble = function (data: JSON): ReadableStream {
  * @param str The string to convert
  * @returns The converted ReadableStream
  */
-export const stringToReadble = function (str: string): ReadableStream {
+export const stringToReadable = function (str: string): ReadableStream {
   const encoder = new TextEncoder();
   const strArr = encoder.encode(str);
 

### 2022-04-08 src/things/huskyDuino/HuskyDuino.ts

@@ -1,185 +1,80 @@
-import {ExposedThing} from '@node-wot/core';
 import * as WoT from 'wot-typescript-definitions';
-import {readText, writeWithoutResponse} from '../../blast_webBluetooth.js';
-import {getThing, removeThing} from '../index.js';
+import {getWot} from '../index.js';
 
 export default class HuskyDuino {
-  public thing: WoT.ExposedThing | null = null;
-  private td: WoT.ThingDescription | null = null;
-  private exposedThing: ExposedThing | null = null;
-  private webBluetoothId: string;
-  private HuskyServiceUUID = '5be35d20-f9b0-11eb-9a03-0242ac130003';
+  public thing: WoT.ConsumedThing | null = null;
 
-  public thingModel: WoT.ThingDescription = {
-    '@context': ['https://www.w3.org/2019/wot/td/v1'],
-    '@type': ['Thing'],
-    id: 'blast:bluetooth:HuskyDuino',
-    title: 'HuskyDuino',
-    description: 'A HuskyLens interface running on Arduino',
-    securityDefinitions: {
-      nosec_sc: {
-        scheme: 'nosec',
-      },
-    },
-    security: 'nosec_sc',
-    properties: {
-      algorithm: {
-        description: 'The currently active algorithm',
-        type: 'number',
-        readOnly: false,
-        writeOnly: false,
-        forms: [
-          {
-            href: '',
-          },
-        ],
-      },
-      id: {
-        description: 'The ID of the face or object',
-        type: 'number',
-        readOnly: false,
-        writeOnly: false,
-        forms: [
-          {
-            href: '',
-          },
-        ],
-      },
-    },
-    actions: {
-      forgetAll: {
-        title: 'Forget all faces and objects',
-        description: 'Forget all faces and objects',
-        input: {
-          type: 'null',
+  async init(webBluetoothId: string) {
+    const td: WoT.ThingDescription = {
+      '@context': ['https://www.w3.org/2019/wot/td/v1'],
+      '@type': ['Thing'],
+      id: 'blast:bluetooth:HuskyDuino',
+      title: 'HuskyDuino',
+      description: 'A HuskyLens interface running on Arduino',
+      securityDefinitions: {
+        nosec_sc: {
+          scheme: 'nosec',
         },
-        forms: [
-          {
-            href: '',
-          },
-        ],
       },
-    },
-  };
+      security: 'nosec_sc',
+      properties: {
+        algorithm: {
[…]

### 2022-04-08 src/thingBlocks/huskyduino/generators.js
statisfy linter

@@ -9,8 +9,11 @@
 
 import {JavaScript} from 'blockly';
 import {asyncApiFunctions, getWorkspace} from './../../blast_interpreter.js';
-// eslint-disable-next-line node/no-missing-import
-import {readableStreamToString, stringToReadable} from '../../things/bindings/binding-helpers.js';
+import {
+  readableStreamToString,
+  stringToReadable,
+  // eslint-disable-next-line node/no-missing-import
+} from '../../things/bindings/binding-helpers.js';
 
 /**
  * Generates JavaScript code for the things_huskylens block.

### 2022-04-08 dist/thingBlocks/ble_rgb_led_controller/blocks.js
update generic bluetooth WoT implementation

@@ -9,7 +9,7 @@
 
 import {Blocks, dialog, FieldTextInput} from 'blockly';
 // eslint-disable-next-line node/no-missing-import
-import BleRgbController from './../../things/bleRgbController/BleRgbController.js';
+import BleRgbController from './../../things/BleRgbController.js';
 import {implementedThings} from '../../blast_things.js';
 
 Blocks['things_bleLedController'] = {

### 2022-04-08 dist/thingBlocks/bluetooth/blocks.js

@@ -9,7 +9,9 @@
 import {Blocks, dialog, FieldDropdown, FieldTextInput} from 'blockly';
 import {implementedThings} from '../../blast_things.js';
 // eslint-disable-next-line node/no-missing-import
-import EddystoneDevice from '../../things/eddystone/EddystoneDevice.js';
+import EddystoneDevice from '../../things/EddystoneDevice.js';
+// eslint-disable-next-line node/no-missing-import
+import BluetoothGeneric from '../../things/BluetoothGeneric.js';
 
 Blocks['things_eddyStoneDevice'] = {
   /**
@@ -63,6 +65,19 @@ Blocks['things_bluetoothGeneric'] = {
     this.setTooltip('A Generic Bluetooth device.');
     this.getField('name').setEnabled(false);
     this.firstTime = true;
+    this.firstTime = true;
+    this.webBluetoothId = '';
+    this.thing = null;
+  },
+  onchange: function () {
+    // on creating this block initialize new instance of BleRgbController
+    if (!this.isInFlyout && this.firstTime && this.rendered) {
+      this.webBluetoothId = this.getFieldValue('id');
+      this.firstTime = false;
+      new BluetoothGeneric().init(this.webBluetoothId).then(thing => {
+        this.thing = thing;
+      });
+    }
   },
 };
 

### 2022-04-08 dist/thingBlocks/bluetooth/generators.js

@@ -8,7 +8,7 @@
 
 import {JavaScript} from 'blockly';
 import {
-  stringToReadble,
+  stringToReadable,
   readableStreamToString,
   // eslint-disable-next-line node/no-missing-import
 } from '../../things/bindings/binding-helpers.js';
@@ -17,7 +17,6 @@ import {
   getWorkspace,
   throwError,
 } from './../../blast_interpreter.js';
-import {readText} from './../../blast_webBluetooth.js';
 
 /**
  * Generates JavaScript code for the get_signal_strength block.
@@ -129,10 +128,10 @@ const writeEddystoneProperty = async function (
   const block = getWorkspace().getBlockById(blockId);
   const thing = block.thing;
   // Set the active slot
-  const slotReadable = stringToReadble(slot);
+  const slotReadable = stringToReadable(slot);
   await thing.writeProperty('activeSlot', slotReadable);
   // Write the property
-  const valueReadable = stringToReadble(value);
+  const valueReadable = stringToReadable(value);
   await thing.writeProperty(property, valueReadable);
 
   callback();
@@ -201,7 +200,7 @@ const readEddystoneProperty = async function (
   const block = getWorkspace().getBlockById(blockId);
   const thing = block.thing;
   // Set the active slot
-  const slotReadable = stringToReadble(slot);
+  const slotReadable = stringToReadable(slot);
   await thing.writeProperty('activeSlot', slotReadable);
   // Read property data
   const interActionInput = await thing.readProperty(property);
@@ -228,103 +227,26 @@ JavaScript['read_gatt_characteristic'] = function (block) {
   const characteristic = JavaScript.quote_(
     block.getFieldValue('characteristic')
   );
-  const code = `readBluetoothService(${thing}, ${characteristic})`;
+  let blockId = "''";
+  if (block.getInputTargetBlock('Thing')) {
+    blockId = JavaScript.quote_(block.getInputTargetBlock('Thing').id);
+  }
+  const code = `readBluetoothService(${blockId}, ${thing}, ${characteristic})`;
 
   return [code, JavaScript.ORDER_NONE];
 };
 
-const characteristics = {
-  barometricPressureTrend: {
-    service: '00001802-0000-1000-8000-00805f9b34fb',
[…]

### 2022-04-08 dist/thingBlocks/huskyduino/blocks.js

@@ -10,7 +10,7 @@
 import {Blocks, dialog, FieldDropdown, FieldTextInput} from 'blockly';
 import {implementedThings} from '../../blast_things.js';
 // eslint-disable-next-line node/no-missing-import
-import HuskyDuino from './../../things/huskyDuino/HuskyDuino.js';
+import HuskyDuino from './../../things/HuskyDuino.js';
 
 Blocks['things_huskylens'] = {
   /**
@@ -37,8 +37,10 @@ Blocks['things_huskylens'] = {
     // on creating this block initialize new instance of BleRgbController
     if (!this.isInFlyout && this.firstTime && this.rendered) {
       this.webBluetoothId = this.getFieldValue('id');
-      this.thing = new HuskyDuino(this.webBluetoothId);
       this.firstTime = false;
+      new HuskyDuino().init(this.webBluetoothId).then(thing => {
+        this.thing = thing;
+      });
     }
   },
 };

### 2022-04-08 dist/thingBlocks/huskyduino/generators.js

@@ -9,7 +9,11 @@
 
 import {JavaScript} from 'blockly';
 import {asyncApiFunctions, getWorkspace} from './../../blast_interpreter.js';
-import {optionalServices} from './../../blast_webBluetooth.js';
+import {
+  readableStreamToString,
+  stringToReadable,
+  // eslint-disable-next-line node/no-missing-import
+} from '../../things/bindings/binding-helpers.js';
 
 /**
  * Generates JavaScript code for the things_huskylens block.
@@ -96,10 +100,6 @@ JavaScript['huskylens_read_id'] = function (block) {
   return [code, JavaScript.ORDER_NONE];
 };
 
-// set the service UUID here， for all characteristics
-const HuskyServiceUUID = '5be35d20-f9b0-11eb-9a03-0242ac130003';
-optionalServices.push(HuskyServiceUUID);
-
 /**
  * Write the choosen algorithm value to Huskyduino via bluetooth
  * @param {Blockly.Block.id} blockId the things_bleLedController block's id.
@@ -107,9 +107,12 @@ optionalServices.push(HuskyServiceUUID);
  * @param {JSInterpreter.AsyncCallback} callback JS Interpreter callback.
  */
 const chooseAlgo = async function (blockId, value, callback) {
+  // Get thing instance of block.
   const block = getWorkspace().getBlockById(blockId);
   const thing = block.thing;
-  await thing.writeProperty('algorithm', value);
+  // Write face id to thing.
+  const valueReadable = stringToReadable(value);
+  await thing.writeProperty('algorithm', valueReadable);
   callback();
 };
 
@@ -122,9 +125,12 @@ asyncApiFunctions.push(['chooseAlgo', chooseAlgo]);
  * @param {JSInterpreter.AsyncCallback} callback JS Interpreter callback.
  */
 const learnID = async function (blockId, value, callback) {
+  // Get thing instance of block.
   const block = getWorkspace().getBlockById(blockId);
   const thing = block.thing;
-  await thing.writeProperty('id', value);
+  // Write face id to thing.
+  const valueReadable = stringToReadable(value);
+  await thing.writeProperty('id', valueReadable);
   callback();
 };
 
@@ -137,8 +143,10 @@ asyncApiFunctions.push(['learnID', learnID]);
  * @param {JSInterpreter.AsyncCallback} callback JS Interpreter callback.
  */
 const forgetAll = async function (blockId, callback) {
+  // Get thing instance of block.
   const block = getWorkspace().getBlockById(blockId);
[…]

### 2022-04-08 dist/things/BleRgbController.d.ts

@@ -1,0 +1,5 @@
+import * as WoT from 'wot-typescript-definitions';
+export default class BleRgbController {
+    thing: WoT.ConsumedThing | null;
+    init(webBluetoothId: string): Promise<WoT.ConsumedThing>;
+}

### 2022-04-08 dist/things/BleRgbController.js

@@ -1,0 +1,42 @@
+import { getWot } from './index.js';
+export default class BleRgbController {
+    constructor() {
+        this.thing = null;
+    }
+    async init(webBluetoothId) {
+        const td = {
+            '@context': ['https://www.w3.org/2019/wot/td/v1'],
+            '@type': ['Thing'],
+            id: 'blast:Bluetooth:ledController',
+            title: 'BLE RGB Controller',
+            description: 'A Bluetooth Low Energy (BLE) controller that can be used to control RGB LED lights.',
+            securityDefinitions: {
+                nosec_sc: {
+                    scheme: 'nosec',
+                },
+            },
+            security: 'nosec_sc',
+            properties: {
+                colour: {
+                    title: 'colour',
+                    description: 'The colour of the LED light.',
+                    unit: '',
+                    type: 'string',
+                    readOnly: false,
+                    writeOnly: true,
+                    forms: [
+                        {
+                            href: 'gatt://0000fff0-0000-1000-8000-00805f9b34fb/0000fff3-0000-1000-8000-00805f9b34fb/writeWithoutResponse',
+                            'wbt:id': webBluetoothId,
+                        },
+                    ],
+                },
+            },
+        };
+        const wot = await getWot();
+        const thing = await wot.consume(td);
+        this.thing = thing;
+        return thing;
+    }
+}
+//# sourceMappingURL=BleRgbController.js.map

### 2022-04-08 dist/things/Blinkstick.d.ts

@@ -1,0 +1,6 @@
+import * as WoT from 'wot-typescript-definitions';
+export default class Blinkstick {
+    private thing;
+    thingModel: WoT.ThingDescription | null;
+    init(webHidId: string): Promise<WoT.ConsumedThing>;
+}

### 2022-04-08 dist/things/Blinkstick.js

@@ -1,0 +1,101 @@
+import { getWot } from './index.js';
+export default class Blinkstick {
+    constructor() {
+        this.thing = null;
+        this.thingModel = null;
+    }
+    async init(webHidId) {
+        const td = {
+            '@context': ['https://www.w3.org/2019/wot/td/v1'],
+            '@type': ['Thing'],
+            id: 'blast:webhid:blinkstick',
+            title: 'Blinkstick',
+            description: 'The tulogic Blinkstick is a Smart LED controller with integrated USB firmware.',
+            securityDefinitions: {
+                nosec_sc: {
+                    scheme: 'nosec',
+                },
+            },
+            security: 'nosec_sc',
+            properties: {
+                colours: {
+                    title: 'colours',
+                    description: 'The colour of the LED at the given index',
+                    unit: '',
+                    type: 'object',
+                    properties: {
+                        0: {
+                            title: 'Colour 0',
+                            description: 'The colour of the LED at index 0',
+                            unit: '',
+                            type: 'string',
+                            writeOnly: true,
+                        },
+                        1: {
+                            title: 'Colour 1',
+                            description: 'The colour of the LED at index 1',
+                            unit: '',
+                            type: 'string',
+                            writeOnly: true,
+                        },
+                        2: {
+                            title: 'Colour 2',
+                            description: 'The colour of the LED at index 2',
+                            unit: '',
+                            type: 'string',
+                            writeOnly: true,
+                        },
+                        3: {
+                            title: 'Colour 3',
+                            description: 'The colour of the LED at index 3',
+                            unit: '',
+                            type: 'string',
+                            writeOnly: true,
+                        },
+                        4: {
+                            title: 'Colour 4',
+                            description: 'The colour of the LED at index 4',
+                            unit: '',
+                            type: 'string',
+                            writeOnly: true,
+                        },
+                        5: {
+                            title: 'Colour 5',
+                            description: 'The colour of the LED at index 5',
+                            unit: '',
+                            type: 'string',
+                            writeOnly: true,
+                        },
+                        6: {
+                            title: 'Colour 6',
+                            description: 'The colour of the LED at index 6',
+                            unit: '',
+                            type: 'string',
+                            writeOnly: true,
+                        },
+                        7: {
+                            title: 'Colour 7',
+                            description: 'The colour of the LED at index 7',
+                            unit: '',
+                            type: 'string',
+                            writeOnly: true,
[…]

### 2022-04-08 dist/things/BluetoothGeneric.d.ts

@@ -1,0 +1,5 @@
+import * as WoT from 'wot-typescript-definitions';
+export default class BluetoothGeneric {
+    thing: WoT.ConsumedThing | null;
+    init(webBluetoothId: string): Promise<WoT.ConsumedThing>;
+}

### 2022-04-08 dist/things/BluetoothGeneric.js

@@ -1,0 +1,270 @@
+import { getWot } from './index.js';
+export default class BluetoothGeneric {
+    constructor() {
+        this.thing = null;
+    }
+    async init(webBluetoothId) {
+        const td = {
+            '@context': ['https://www.w3.org/2019/wot/td/v1'],
+            '@type': ['Thing'],
+            id: 'blast:bluetooth:BluetoothGeneric',
+            title: 'Genereic Bluetooth device',
+            description: 'A generic Bluetooth device',
+            securityDefinitions: {
+                nosec_sc: {
+                    scheme: 'nosec',
+                },
+            },
+            security: 'nosec_sc',
+            properties: {
+                barometricPressureTrend: {
+                    title: 'Barometric pressure trend',
+                    description: 'The barometric pressure trend in hPa.',
+                    unit: 'hPa',
+                    type: 'number',
+                    readOnly: true,
+                    forms: [
+                        {
+                            href: 'gatt://00001802-0000-1000-8000-00805f9b34fb/00002a1c-0000-1000-8000-00805f9b34fb/readNumber',
+                            'wbt:id': webBluetoothId,
+                        },
+                    ],
+                },
+                batteryLevel: {
+                    title: 'Battery level',
+                    description: 'Battery level in %.',
+                    unit: '%',
+                    type: 'number',
+                    readOnly: true,
+                    forms: [
+                        {
+                            href: 'gatt://0000180f-0000-1000-8000-00805f9b34fb/00002a19-0000-1000-8000-00805f9b34fb/readNumber',
+                            'wbt:id': webBluetoothId,
+                        },
+                    ],
+                },
+                deviceName: {
+                    title: 'Device name',
+                    description: 'User defined name of the device',
+                    type: 'string',
+                    readOnly: false,
+                    forms: [
+                        {
+                            op: 'writeproperty',
+                            href: 'gatt://00001800-0000-1000-8000-00805f9b34fb/00002a00-0000-1000-8000-00805f9b34fb/writeWithoutResponse',
+                            'wbt:id': webBluetoothId,
+                        },
+                        {
+                            op: 'readproperty',
+                            href: 'gatt://00001800-0000-1000-8000-00805f9b34fb/00002a00-0000-1000-8000-00805f9b34fb/readText',
+                            'wbt:id': webBluetoothId,
+                        },
+                    ],
+                },
+                elevation: {
+                    title: 'Elevation',
+                    description: 'The elevation measured by the device.',
+                    type: 'number',
+                    readOnly: true,
[…]

### 2022-04-08 dist/things/EddystoneDevice.d.ts

@@ -1,0 +1,5 @@
+import * as WoT from 'wot-typescript-definitions';
+export default class EddystoneDevice {
+    thing: WoT.ConsumedThing | null;
+    init(webBluetoothId: string): Promise<WoT.ConsumedThing>;
+}

### 2022-04-08 dist/things/EddystoneDevice.js

@@ -1,0 +1,163 @@
+import { getWot } from './index.js';
+export default class EddystoneDevice {
+    constructor() {
+        this.thing = null;
+    }
+    async init(webBluetoothId) {
+        const td = {
+            '@context': ['https://www.w3.org/2019/wot/td/v1'],
+            '@type': ['Thing'],
+            id: 'blast:bluetooth:EddystoneDevice',
+            title: 'Eddystone Device',
+            description: 'A Bluetooth device implementing the Eddystone protocol',
+            securityDefinitions: {
+                nosec_sc: {
+                    scheme: 'nosec',
+                },
+            },
+            security: 'nosec_sc',
+            properties: {
+                activeSlot: {
+                    title: 'Active Slot',
+                    description: 'The active slot of the Eddystone device',
+                    type: 'integer',
+                    readOnly: false,
+                    forms: [
+                        {
+                            op: 'readproperty',
+                            href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87502-8ed3-4bdf-8a39-a01bebede295/readEddystoneProperty',
+                            'wbt:id': webBluetoothId,
+                        },
+                        {
+                            op: 'writeproperty',
+                            href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87502-8ed3-4bdf-8a39-a01bebede295/writeEddystoneProperty',
+                            'wbt:id': webBluetoothId,
+                        },
+                    ],
+                },
+                advertisedTxPower: {
+                    title: 'Advertised Tx Power',
+                    description: 'The advertised TX power of the iBeacon',
+                    unit: 'dBm',
+                    type: 'integer',
+                    readOnly: false,
+                    forms: [
+                        {
+                            op: 'readproperty',
+                            href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87505-8ed3-4bdf-8a39-a01bebede295/readEddystoneProperty',
+                            'wbt:id': webBluetoothId,
+                        },
+                        {
+                            op: 'writeproperty',
+                            href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87505-8ed3-4bdf-8a39-a01bebede295/writeEddystoneProperty',
+                            'wbt:id': webBluetoothId,
+                        },
+                    ],
+                },
+                advertisedData: {
+                    title: 'Advertised Data',
+                    description: 'The advertised data of the eddystone device',
[…]

### 2022-04-08 dist/things/HuskyDuino.d.ts

@@ -1,0 +1,5 @@
+import * as WoT from 'wot-typescript-definitions';
+export default class HuskyDuino {
+    thing: WoT.ConsumedThing | null;
+    init(webBluetoothId: string): Promise<WoT.ConsumedThing>;
+}

### 2022-04-08 dist/things/HuskyDuino.js

@@ -1,0 +1,79 @@
+import { getWot } from './index.js';
+export default class HuskyDuino {
+    constructor() {
+        this.thing = null;
+    }
+    async init(webBluetoothId) {
+        const td = {
+            '@context': ['https://www.w3.org/2019/wot/td/v1'],
+            '@type': ['Thing'],
+            id: 'blast:bluetooth:HuskyDuino',
+            title: 'HuskyDuino',
+            description: 'A HuskyLens interface running on Arduino',
+            securityDefinitions: {
+                nosec_sc: {
+                    scheme: 'nosec',
+                },
+            },
+            security: 'nosec_sc',
+            properties: {
+                algorithm: {
+                    description: 'The currently active algorithm',
+                    type: 'number',
+                    readOnly: false,
+                    writeOnly: false,
+                    forms: [
+                        {
+                            op: 'readproperty',
+                            href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35d26-f9b0-11eb-9a03-0242ac130003/writeWithoutResponse',
+                            'wbt:id': webBluetoothId,
+                        },
+                        {
+                            op: 'writeproperty',
+                            href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35d26-f9b0-11eb-9a03-0242ac130003/readNumber',
+                            'wbt:id': webBluetoothId,
+                        },
+                    ],
+                },
+                id: {
+                    description: 'The ID of the face or object',
+                    type: 'number',
+                    readOnly: false,
+                    writeOnly: false,
+                    forms: [
+                        {
+                            op: 'readproperty',
+                            href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35eca-f9b0-11eb-9a03-0242ac130003/writeWithoutResponse',
+                            'wbt:id': webBluetoothId,
+                        },
+                        {
+                            op: 'writeproperty',
+                            href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35eca-f9b0-11eb-9a03-0242ac130003/readText',
+                            'wbt:id': webBluetoothId,
+                        },
+                    ],
+                },
+            },
+            actions: {
+                forgetAll: {
+                    title: 'Forget all faces and objects',
+                    description: 'Forget all faces and objects',
+                    input: {
+                        type: 'null',
+                    },
+                    forms: [
[…]

### 2022-04-08 dist/things/bindings/binding-helpers.d.ts

@@ -20,7 +20,7 @@ export declare const jsonToReadble: (data: JSON) => ReadableStream;
  * @param str The string to convert
  * @returns The converted ReadableStream
  */
-export declare const stringToReadble: (str: string) => ReadableStream;
+export declare const stringToReadable: (str: string) => ReadableStream;
 /**
  * Converts a string into a NodeJS.ReadableStream.
  * @param data The string to convert

### 2022-04-08 dist/things/bindings/binding-helpers.js

@@ -45,7 +45,7 @@ export const jsonToReadble = function (data) {
  * @param str The string to convert
  * @returns The converted ReadableStream
  */
-export const stringToReadble = function (str) {
+export const stringToReadable = function (str) {
     const encoder = new TextEncoder();
     const strArr = encoder.encode(str);
     return new ReadableStream({

### 2022-04-08 dist/things/bleRgbController/BleRgbController.d.ts

@@ -1,5 +1,0 @@
-import * as WoT from 'wot-typescript-definitions';
-export default class BleRgbController {
-    thing: WoT.ConsumedThing | null;
-    init(webBluetoothId: string): Promise<WoT.ConsumedThing>;
-}

### 2022-04-08 dist/things/bleRgbController/BleRgbController.js

@@ -1,42 +1,0 @@
-import { getWot } from '../index.js';
-export default class BleRgbController {
-    constructor() {
-        this.thing = null;
-    }
-    async init(webBluetoothId) {
-        const td = {
-            '@context': ['https://www.w3.org/2019/wot/td/v1'],
-            '@type': ['Thing'],
-            id: 'blast:Bluetooth:ledController',
-            title: 'BLE RGB Controller',
-            description: 'A Bluetooth Low Energy (BLE) controller that can be used to control RGB LED lights.',
-            securityDefinitions: {
-                nosec_sc: {
-                    scheme: 'nosec',
-                },
-            },
-            security: 'nosec_sc',
-            properties: {
-                colour: {
-                    title: 'colour',
-                    description: 'The colour of the LED light.',
-                    unit: '',
-                    type: 'string',
-                    readOnly: false,
-                    writeOnly: true,
-                    forms: [
-                        {
-                            href: 'gatt://0000fff0-0000-1000-8000-00805f9b34fb/0000fff3-0000-1000-8000-00805f9b34fb/writeWithoutResponse',
-                            'wbt:id': webBluetoothId,
-                        },
-                    ],
-                },
-            },
-        };
-        const wot = await getWot();
-        const thing = await wot.consume(td);
-        this.thing = thing;
-        return thing;
-    }
-}
-//# sourceMappingURL=BleRgbController.js.map

### 2022-04-08 dist/things/blinkstick/Blinkstick.js

@@ -1,101 +1,0 @@
-import { getWot } from '../index.js';
-export default class Blinkstick {
-    constructor() {
-        this.thing = null;
-        this.thingModel = null;
-    }
-    async init(webHidId) {
-        const td = {
-            '@context': ['https://www.w3.org/2019/wot/td/v1'],
-            '@type': ['Thing'],
-            id: 'blast:webhid:blinkstick',
-            title: 'Blinkstick',
-            description: 'The tulogic Blinkstick is a Smart LED controller with integrated USB firmware.',
-            securityDefinitions: {
-                nosec_sc: {
-                    scheme: 'nosec',
-                },
-            },
-            security: 'nosec_sc',
-            properties: {
-                colours: {
-                    title: 'colours',
-                    description: 'The colour of the LED at the given index',
-                    unit: '',
-                    type: 'object',
-                    properties: {
-                        0: {
-                            title: 'Colour 0',
-                            description: 'The colour of the LED at index 0',
-                            unit: '',
-                            type: 'string',
-                            writeOnly: true,
-                        },
-                        1: {
-                            title: 'Colour 1',
-                            description: 'The colour of the LED at index 1',
-                            unit: '',
-                            type: 'string',
-                            writeOnly: true,
-                        },
-                        2: {
-                            title: 'Colour 2',
-                            description: 'The colour of the LED at index 2',
-                            unit: '',
-                            type: 'string',
-                            writeOnly: true,
-                        },
-                        3: {
-                            title: 'Colour 3',
-                            description: 'The colour of the LED at index 3',
-                            unit: '',
-                            type: 'string',
-                            writeOnly: true,
-                        },
-                        4: {
-                            title: 'Colour 4',
-                            description: 'The colour of the LED at index 4',
-                            unit: '',
-                            type: 'string',
-                            writeOnly: true,
-                        },
-                        5: {
-                            title: 'Colour 5',
-                            description: 'The colour of the LED at index 5',
-                            unit: '',
-                            type: 'string',
-                            writeOnly: true,
-                        },
-                        6: {
-                            title: 'Colour 6',
-                            description: 'The colour of the LED at index 6',
-                            unit: '',
-                            type: 'string',
-                            writeOnly: true,
-                        },
-                        7: {
-                            title: 'Colour 7',
-                            description: 'The colour of the LED at index 7',
-                            unit: '',
-                            type: 'string',
[…]

### 2022-04-08 dist/things/eddystone/EddystoneDevice.d.ts

@@ -1,5 +1,0 @@
-import * as WoT from 'wot-typescript-definitions';
-export default class EddystoneDevice {
-    thing: WoT.ConsumedThing | null;
-    init(webBluetoothId: string): Promise<WoT.ConsumedThing>;
-}

### 2022-04-08 dist/things/eddystone/EddystoneDevice.js

@@ -1,163 +1,0 @@
-import { getWot } from '../index.js';
-export default class EddystoneDevice {
-    constructor() {
-        this.thing = null;
-    }
-    async init(webBluetoothId) {
-        const td = {
-            '@context': ['https://www.w3.org/2019/wot/td/v1'],
-            '@type': ['Thing'],
-            id: 'blast:bluetooth:EddystoneDevice',
-            title: 'Eddystone Device',
-            description: 'A Bluetooth device implementing the Eddystone protocol',
-            securityDefinitions: {
-                nosec_sc: {
-                    scheme: 'nosec',
-                },
-            },
-            security: 'nosec_sc',
-            properties: {
-                activeSlot: {
-                    title: 'Active Slot',
-                    description: 'The active slot of the Eddystone device',
-                    type: 'integer',
-                    readOnly: false,
-                    forms: [
-                        {
-                            op: 'readproperty',
-                            href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87502-8ed3-4bdf-8a39-a01bebede295/readEddystoneProperty',
-                            'wbt:id': webBluetoothId,
-                        },
-                        {
-                            op: 'writeproperty',
-                            href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87502-8ed3-4bdf-8a39-a01bebede295/writeEddystoneProperty',
-                            'wbt:id': webBluetoothId,
-                        },
-                    ],
-                },
-                advertisedTxPower: {
-                    title: 'Advertised Tx Power',
-                    description: 'The advertised TX power of the iBeacon',
-                    unit: 'dBm',
-                    type: 'integer',
-                    readOnly: false,
-                    forms: [
-                        {
-                            op: 'readproperty',
-                            href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87505-8ed3-4bdf-8a39-a01bebede295/readEddystoneProperty',
-                            'wbt:id': webBluetoothId,
-                        },
-                        {
-                            op: 'writeproperty',
-                            href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87505-8ed3-4bdf-8a39-a01bebede295/writeEddystoneProperty',
-                            'wbt:id': webBluetoothId,
-                        },
-                    ],
-                },
-                advertisedData: {
-                    title: 'Advertised Data',
-                    description: 'The advertised data of the eddystone device',
[…]

### 2022-04-08 dist/things/huskyDuino/HuskyDuino.d.ts

@@ -1,35 +1,0 @@
-import * as WoT from 'wot-typescript-definitions';
-export default class HuskyDuino {
-    thing: WoT.ExposedThing | null;
-    private td;
-    private exposedThing;
-    private webBluetoothId;
-    private HuskyServiceUUID;
-    thingModel: WoT.ThingDescription;
-    constructor(webBluetoothId: string);
-    private setPropertyHandlers;
-    private setActionHandlers;
-    /**
-     * Set algorithm the Huskylens should use.
-     * @param alg the algorithm to use
-     */
-    private setAlgorithm;
-    /**
-     * Learn a face or object.
-     * @param id the ID of the face or object
-     */
-    private learn;
-    /**
-     * Get the ID of the face or object.
-     */
-    getId(): Promise<string>;
-    /**
-     * Forget all faces and objects.
-     */
-    private forgetAll;
-    writeProperty(property: string, value: any): Promise<void>;
-    readProperty(property: string): Promise<any>;
-    invokeAction(action: string, parameters: any): Promise<any>;
-    getThingDescription(): Promise<WoT.ThingDescription | null>;
-    destroy(): Promise<void>;
-}

### 2022-04-08 dist/things/huskyDuino/HuskyDuino.js

@@ -1,152 +1,0 @@
-import { readText, writeWithoutResponse } from '../../blast_webBluetooth.js';
-import { getThing, removeThing } from '../index.js';
-export default class HuskyDuino {
-    constructor(webBluetoothId) {
-        this.thing = null;
-        this.td = null;
-        this.exposedThing = null;
-        this.HuskyServiceUUID = '5be35d20-f9b0-11eb-9a03-0242ac130003';
-        this.thingModel = {
-            '@context': ['https://www.w3.org/2019/wot/td/v1'],
-            '@type': ['Thing'],
-            id: 'blast:bluetooth:HuskyDuino',
-            title: 'HuskyDuino',
-            description: 'A HuskyLens interface running on Arduino',
-            securityDefinitions: {
-                nosec_sc: {
-                    scheme: 'nosec',
-                },
-            },
-            security: 'nosec_sc',
-            properties: {
-                algorithm: {
-                    description: 'The currently active algorithm',
-                    type: 'number',
-                    readOnly: false,
-                    writeOnly: false,
-                    forms: [
-                        {
-                            href: '',
-                        },
-                    ],
-                },
-                id: {
-                    description: 'The ID of the face or object',
-                    type: 'number',
-                    readOnly: false,
-                    writeOnly: false,
-                    forms: [
-                        {
-                            href: '',
-                        },
-                    ],
-                },
-            },
-            actions: {
-                forgetAll: {
-                    title: 'Forget all faces and objects',
-                    description: 'Forget all faces and objects',
-                    input: {
-                        type: 'null',
-                    },
-                    forms: [
-                        {
-                            href: '',
-                        },
-                    ],
-                },
-            },
-        };
-        this.webBluetoothId = webBluetoothId;
-        getThing(this.thingModel).then(thing => {
-            this.thing = thing;
-            this.exposedThing = thing;
-            this.td = thing.getThingDescription();
-            this.setPropertyHandlers();
-            this.setActionHandlers();
-            this.thing.expose();
-        });
-    }
-    setPropertyHandlers() {
-        var _a, _b, _c;
[…]

### 2022-04-08 src/thingBlocks/ble_rgb_led_controller/generators.js

@@ -14,7 +14,7 @@ import {
   throwError,
 } from './../../blast_interpreter.js';
 // eslint-disable-next-line node/no-missing-import
-import {stringToReadble} from './../../things/bindings/binding-helpers.js';
+import {stringToReadable} from './../../things/bindings/binding-helpers.js';
 
 /**
  * Generates JavaScript code for the things_bleLedController block.
@@ -68,7 +68,7 @@ const switchLights = async function (
   // convert data to json
   const data = '7e000503' + colour.substring(1, 7) + '00ef';
   // convert json to stream
-  const stream = stringToReadble(data);
+  const stream = stringToReadable(data);
   // get thing instance of block
   const block = getWorkspace().getBlockById(blockId);
   const thing = await block.thing;

### 2022-04-08 src/thingBlocks/blinkstick/blocks.js

@@ -9,7 +9,7 @@
 
 import {Blocks, FieldTextInput} from 'blockly';
 // eslint-disable-next-line node/no-missing-import
-import Blinkstick from './../../things/blinkstick/Blinkstick.js';
+import Blinkstick from './../../things/Blinkstick.js';
 import {implementedThings} from '../../blast_things.js';
 
 /**

### 2022-04-08 src/thingBlocks/bluetooth/generators.js

@@ -17,7 +17,6 @@ import {
   getWorkspace,
   throwError,
 } from './../../blast_interpreter.js';
-import {readText} from './../../blast_webBluetooth.js';
 
 /**
  * Generates JavaScript code for the get_signal_strength block.
@@ -228,103 +227,26 @@ JavaScript['read_gatt_characteristic'] = function (block) {
   const characteristic = JavaScript.quote_(
     block.getFieldValue('characteristic')
   );
-  const code = `readBluetoothService(${thing}, ${characteristic})`;
+  let blockId = "''";
+  if (block.getInputTargetBlock('Thing')) {
+    blockId = JavaScript.quote_(block.getInputTargetBlock('Thing').id);
+  }
+  const code = `readBluetoothService(${blockId}, ${thing}, ${characteristic})`;
 
   return [code, JavaScript.ORDER_NONE];
 };
 
-const characteristics = {
-  barometricPressureTrend: {
-    service: '00001802-0000-1000-8000-00805f9b34fb',
-    characteristic: '00002a1c-0000-1000-8000-00805f9b34fb',
-  },
-  batteryLevel: {
-    service: '0000180f-0000-1000-8000-00805f9b34fb',
-    characteristic: '00002a19-0000-1000-8000-00805f9b34fb',
-  },
-  deviceName: {
-    service: '00001800-0000-1000-8000-00805f9b34fb',
-    characteristic: '00002a00-0000-1000-8000-00805f9b34fb',
-  },
-  elevation: {
-    service: '00001803-0000-1000-8000-00805f9b34fb',
-    characteristic: '00002a6c-0000-1000-8000-00805f9b34fb',
-  },
-  firmwareRevision: {
-    service: '0000180a-0000-1000-8000-00805f9b34fb',
-    characteristic: '00002a26-0000-1000-8000-00805f9b34fb',
-  },
-  hardwareRevision: {
-    service: '0000180a-0000-1000-8000-00805f9b34fb',
-    characteristic: '00002a27-0000-1000-8000-00805f9b34fb',
-  },
-  humidity: {
-    service: '00001803-0000-1000-8000-00805f9b34fb',
-    characteristic: '00002a6f-0000-1000-8000-00805f9b34fb',
-  },
-  irradiance: {
-    service: '00001803-0000-1000-8000-00805f9b34fb',
-    characteristic: '00002a77-0000-1000-8000-00805f9b34fb',
-  },
-  intermediateTemperature: {
-    service: '00001809-0000-1000-8000-00805f9b34fb',
[…]

### 2022-04-08 src/thingBlocks/huskyduino/blocks.js

@@ -10,7 +10,7 @@
 import {Blocks, dialog, FieldDropdown, FieldTextInput} from 'blockly';
 import {implementedThings} from '../../blast_things.js';
 // eslint-disable-next-line node/no-missing-import
-import HuskyDuino from './../../things/huskyDuino/HuskyDuino.js';
+import HuskyDuino from './../../things/HuskyDuino.js';
 
 Blocks['things_huskylens'] = {
   /**

### 2022-04-08 src/things/BleRgbController.ts

@@ -1,0 +1,43 @@
+import * as WoT from 'wot-typescript-definitions';
+import {getWot} from './index.js';
+
+export default class BleRgbController {
+  public thing: WoT.ConsumedThing | null = null;
+
+  async init(webBluetoothId: string): Promise<WoT.ConsumedThing> {
+    const td: WoT.ThingDescription = {
+      '@context': ['https://www.w3.org/2019/wot/td/v1'],
+      '@type': ['Thing'],
+      id: 'blast:Bluetooth:ledController',
+      title: 'BLE RGB Controller',
+      description:
+        'A Bluetooth Low Energy (BLE) controller that can be used to control RGB LED lights.',
+      securityDefinitions: {
+        nosec_sc: {
+          scheme: 'nosec',
+        },
+      },
+      security: 'nosec_sc',
+      properties: {
+        colour: {
+          title: 'colour',
+          description: 'The colour of the LED light.',
+          unit: '',
+          type: 'string',
+          readOnly: false,
+          writeOnly: true,
+          forms: [
+            {
+              href: 'gatt://0000fff0-0000-1000-8000-00805f9b34fb/0000fff3-0000-1000-8000-00805f9b34fb/writeWithoutResponse',
+              'wbt:id': webBluetoothId,
+            },
+          ],
+        },
+      },
+    };
+    const wot = await getWot();
+    const thing = await wot.consume(td);
+    this.thing = thing;
+    return thing;
+  }
+}

### 2022-04-08 src/things/Blinkstick.ts

@@ -1,0 +1,103 @@
+import * as WoT from 'wot-typescript-definitions';
+import {getWot} from './index.js';
+
+export default class Blinkstick {
+  private thing: WoT.ConsumedThing | null = null;
+
+  public thingModel: WoT.ThingDescription | null = null;
+
+  public async init(webHidId: string): Promise<WoT.ConsumedThing> {
+    const td: WoT.ThingDescription = {
+      '@context': ['https://www.w3.org/2019/wot/td/v1'],
+      '@type': ['Thing'],
+      id: 'blast:webhid:blinkstick',
+      title: 'Blinkstick',
+      description:
+        'The tulogic Blinkstick is a Smart LED controller with integrated USB firmware.',
+      securityDefinitions: {
+        nosec_sc: {
+          scheme: 'nosec',
+        },
+      },
+      security: 'nosec_sc',
+      properties: {
+        colours: {
+          title: 'colours',
+          description: 'The colour of the LED at the given index',
+          unit: '',
+          type: 'object',
+          properties: {
+            0: {
+              title: 'Colour 0',
+              description: 'The colour of the LED at index 0',
+              unit: '',
+              type: 'string',
+              writeOnly: true,
+            },
+            1: {
+              title: 'Colour 1',
+              description: 'The colour of the LED at index 1',
+              unit: '',
+              type: 'string',
+              writeOnly: true,
+            },
+            2: {
+              title: 'Colour 2',
+              description: 'The colour of the LED at index 2',
+              unit: '',
+              type: 'string',
+              writeOnly: true,
+            },
+            3: {
+              title: 'Colour 3',
+              description: 'The colour of the LED at index 3',
+              unit: '',
+              type: 'string',
+              writeOnly: true,
+            },
+            4: {
+              title: 'Colour 4',
+              description: 'The colour of the LED at index 4',
+              unit: '',
+              type: 'string',
+              writeOnly: true,
+            },
+            5: {
+              title: 'Colour 5',
+              description: 'The colour of the LED at index 5',
+              unit: '',
+              type: 'string',
+              writeOnly: true,
+            },
+            6: {
+              title: 'Colour 6',
+              description: 'The colour of the LED at index 6',
+              unit: '',
+              type: 'string',
+              writeOnly: true,
+            },
+            7: {
+              title: 'Colour 7',
+              description: 'The colour of the LED at index 7',
+              unit: '',
+              type: 'string',
[…]

### 2022-04-08 src/things/BluetoothGeneric.ts

@@ -1,0 +1,271 @@
+import * as WoT from 'wot-typescript-definitions';
+import {getWot} from './index.js';
+
+export default class BluetoothGeneric {
+  public thing: WoT.ConsumedThing | null = null;
+
+  public async init(webBluetoothId: string) {
+    const td: WoT.ThingDescription = {
+      '@context': ['https://www.w3.org/2019/wot/td/v1'],
+      '@type': ['Thing'],
+      id: 'blast:bluetooth:BluetoothGeneric',
+      title: 'Genereic Bluetooth device',
+      description: 'A generic Bluetooth device',
+      securityDefinitions: {
+        nosec_sc: {
+          scheme: 'nosec',
+        },
+      },
+      security: 'nosec_sc',
+      properties: {
+        barometricPressureTrend: {
+          title: 'Barometric pressure trend',
+          description: 'The barometric pressure trend in hPa.',
+          unit: 'hPa',
+          type: 'number',
+          readOnly: true,
+          forms: [
+            {
+              href: 'gatt://00001802-0000-1000-8000-00805f9b34fb/00002a1c-0000-1000-8000-00805f9b34fb/readNumber',
+              'wbt:id': webBluetoothId,
+            },
+          ],
+        },
+        batteryLevel: {
+          title: 'Battery level',
+          description: 'Battery level in %.',
+          unit: '%',
+          type: 'number',
+          readOnly: true,
+          forms: [
+            {
+              href: 'gatt://0000180f-0000-1000-8000-00805f9b34fb/00002a19-0000-1000-8000-00805f9b34fb/readNumber',
+              'wbt:id': webBluetoothId,
+            },
+          ],
+        },
+        deviceName: {
+          title: 'Device name',
+          description: 'User defined name of the device',
+          type: 'string',
+          readOnly: false,
+          forms: [
+            {
+              op: 'writeproperty',
+              href: 'gatt://00001800-0000-1000-8000-00805f9b34fb/00002a00-0000-1000-8000-00805f9b34fb/writeWithoutResponse',
+              'wbt:id': webBluetoothId,
+            },
+            {
+              op: 'readproperty',
+              href: 'gatt://00001800-0000-1000-8000-00805f9b34fb/00002a00-0000-1000-8000-00805f9b34fb/readText',
+              'wbt:id': webBluetoothId,
+            },
+          ],
+        },
+        elevation: {
+          title: 'Elevation',
+          description: 'The elevation measured by the device.',
+          type: 'number',
[…]

### 2022-04-08 src/things/EddystoneDevice.ts

@@ -1,0 +1,163 @@
+import * as WoT from 'wot-typescript-definitions';
+import {getWot} from './index.js';
+
+export default class EddystoneDevice {
+  public thing: WoT.ConsumedThing | null = null;
+
+  public async init(webBluetoothId: string) {
+    const td: WoT.ThingDescription = {
+      '@context': ['https://www.w3.org/2019/wot/td/v1'],
+      '@type': ['Thing'],
+      id: 'blast:bluetooth:EddystoneDevice',
+      title: 'Eddystone Device',
+      description: 'A Bluetooth device implementing the Eddystone protocol',
+      securityDefinitions: {
+        nosec_sc: {
+          scheme: 'nosec',
+        },
+      },
+      security: 'nosec_sc',
+      properties: {
+        activeSlot: {
+          title: 'Active Slot',
+          description: 'The active slot of the Eddystone device',
+          type: 'integer',
+          readOnly: false,
+          forms: [
+            {
+              op: 'readproperty',
+              href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87502-8ed3-4bdf-8a39-a01bebede295/readEddystoneProperty',
+              'wbt:id': webBluetoothId,
+            },
+            {
+              op: 'writeproperty',
+              href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87502-8ed3-4bdf-8a39-a01bebede295/writeEddystoneProperty',
+              'wbt:id': webBluetoothId,
+            },
+          ],
+        },
+        advertisedTxPower: {
+          title: 'Advertised Tx Power',
+          description: 'The advertised TX power of the iBeacon',
+          unit: 'dBm',
+          type: 'integer',
+          readOnly: false,
+          forms: [
+            {
+              op: 'readproperty',
+              href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87505-8ed3-4bdf-8a39-a01bebede295/readEddystoneProperty',
+              'wbt:id': webBluetoothId,
+            },
+            {
+              op: 'writeproperty',
+              href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87505-8ed3-4bdf-8a39-a01bebede295/writeEddystoneProperty',
+              'wbt:id': webBluetoothId,
+            },
+          ],
+        },
+        advertisedData: {
+          title: 'Advertised Data',
[…]

### 2022-04-08 src/things/HuskyDuino.ts

@@ -1,0 +1,80 @@
+import * as WoT from 'wot-typescript-definitions';
+import {getWot} from './index.js';
+
+export default class HuskyDuino {
+  public thing: WoT.ConsumedThing | null = null;
+
+  async init(webBluetoothId: string) {
+    const td: WoT.ThingDescription = {
+      '@context': ['https://www.w3.org/2019/wot/td/v1'],
+      '@type': ['Thing'],
+      id: 'blast:bluetooth:HuskyDuino',
+      title: 'HuskyDuino',
+      description: 'A HuskyLens interface running on Arduino',
+      securityDefinitions: {
+        nosec_sc: {
+          scheme: 'nosec',
+        },
+      },
+      security: 'nosec_sc',
+      properties: {
+        algorithm: {
+          description: 'The currently active algorithm',
+          type: 'number',
+          readOnly: false,
+          writeOnly: false,
+          forms: [
+            {
+              op: 'readproperty',
+              href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35d26-f9b0-11eb-9a03-0242ac130003/writeWithoutResponse',
+              'wbt:id': webBluetoothId,
+            },
+            {
+              op: 'writeproperty',
+              href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35d26-f9b0-11eb-9a03-0242ac130003/readNumber',
+              'wbt:id': webBluetoothId,
+            },
+          ],
+        },
+        id: {
+          description: 'The ID of the face or object',
+          type: 'number',
+          readOnly: false,
+          writeOnly: false,
+          forms: [
+            {
+              op: 'readproperty',
+              href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35eca-f9b0-11eb-9a03-0242ac130003/writeWithoutResponse',
+              'wbt:id': webBluetoothId,
+            },
+            {
+              op: 'writeproperty',
+              href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35eca-f9b0-11eb-9a03-0242ac130003/readText',
+              'wbt:id': webBluetoothId,
+            },
+          ],
+        },
+      },
+      actions: {
+        forgetAll: {
+          title: 'Forget all faces and objects',
+          description: 'Forget all faces and objects',
+          input: {
+            type: 'null',
+          },
+          forms: [
+            {
[…]

### 2022-04-08 src/things/bleRgbController/BleRgbController.ts

@@ -1,43 +1,0 @@
-import * as WoT from 'wot-typescript-definitions';
-import {getWot} from '../index.js';
-
-export default class BleRgbController {
-  public thing: WoT.ConsumedThing | null = null;
-
-  async init(webBluetoothId: string): Promise<WoT.ConsumedThing> {
-    const td: WoT.ThingDescription = {
-      '@context': ['https://www.w3.org/2019/wot/td/v1'],
-      '@type': ['Thing'],
-      id: 'blast:Bluetooth:ledController',
-      title: 'BLE RGB Controller',
-      description:
-        'A Bluetooth Low Energy (BLE) controller that can be used to control RGB LED lights.',
-      securityDefinitions: {
-        nosec_sc: {
-          scheme: 'nosec',
-        },
-      },
-      security: 'nosec_sc',
-      properties: {
-        colour: {
-          title: 'colour',
-          description: 'The colour of the LED light.',
-          unit: '',
-          type: 'string',
-          readOnly: false,
-          writeOnly: true,
-          forms: [
-            {
-              href: 'gatt://0000fff0-0000-1000-8000-00805f9b34fb/0000fff3-0000-1000-8000-00805f9b34fb/writeWithoutResponse',
-              'wbt:id': webBluetoothId,
-            },
-          ],
-        },
-      },
-    };
-    const wot = await getWot();
-    const thing = await wot.consume(td);
-    this.thing = thing;
-    return thing;
-  }
-}

### 2022-04-08 src/things/blinkstick/Blinkstick.ts

@@ -1,103 +1,0 @@
-import * as WoT from 'wot-typescript-definitions';
-import {getWot} from '../index.js';
-
-export default class Blinkstick {
-  private thing: WoT.ConsumedThing | null = null;
-
-  public thingModel: WoT.ThingDescription | null = null;
-
-  public async init(webHidId: string): Promise<WoT.ConsumedThing> {
-    const td: WoT.ThingDescription = {
-      '@context': ['https://www.w3.org/2019/wot/td/v1'],
-      '@type': ['Thing'],
-      id: 'blast:webhid:blinkstick',
-      title: 'Blinkstick',
-      description:
-        'The tulogic Blinkstick is a Smart LED controller with integrated USB firmware.',
-      securityDefinitions: {
-        nosec_sc: {
-          scheme: 'nosec',
-        },
-      },
-      security: 'nosec_sc',
-      properties: {
-        colours: {
-          title: 'colours',
-          description: 'The colour of the LED at the given index',
-          unit: '',
-          type: 'object',
-          properties: {
-            0: {
-              title: 'Colour 0',
-              description: 'The colour of the LED at index 0',
-              unit: '',
-              type: 'string',
-              writeOnly: true,
-            },
-            1: {
-              title: 'Colour 1',
-              description: 'The colour of the LED at index 1',
-              unit: '',
-              type: 'string',
-              writeOnly: true,
-            },
-            2: {
-              title: 'Colour 2',
-              description: 'The colour of the LED at index 2',
-              unit: '',
-              type: 'string',
-              writeOnly: true,
-            },
-            3: {
-              title: 'Colour 3',
-              description: 'The colour of the LED at index 3',
-              unit: '',
-              type: 'string',
-              writeOnly: true,
-            },
-            4: {
-              title: 'Colour 4',
-              description: 'The colour of the LED at index 4',
-              unit: '',
-              type: 'string',
-              writeOnly: true,
-            },
-            5: {
-              title: 'Colour 5',
-              description: 'The colour of the LED at index 5',
-              unit: '',
-              type: 'string',
-              writeOnly: true,
-            },
-            6: {
-              title: 'Colour 6',
-              description: 'The colour of the LED at index 6',
-              unit: '',
-              type: 'string',
-              writeOnly: true,
-            },
-            7: {
-              title: 'Colour 7',
-              description: 'The colour of the LED at index 7',
-              unit: '',
-              type: 'string',
[…]

### 2022-04-08 src/things/eddystone/EddystoneDevice.ts

@@ -1,163 +1,0 @@
-import * as WoT from 'wot-typescript-definitions';
-import {getWot} from '../index.js';
-
-export default class EddystoneDevice {
-  public thing: WoT.ConsumedThing | null = null;
-
-  public async init(webBluetoothId: string) {
-    const td: WoT.ThingDescription = {
-      '@context': ['https://www.w3.org/2019/wot/td/v1'],
-      '@type': ['Thing'],
-      id: 'blast:bluetooth:EddystoneDevice',
-      title: 'Eddystone Device',
-      description: 'A Bluetooth device implementing the Eddystone protocol',
-      securityDefinitions: {
-        nosec_sc: {
-          scheme: 'nosec',
-        },
-      },
-      security: 'nosec_sc',
-      properties: {
-        activeSlot: {
-          title: 'Active Slot',
-          description: 'The active slot of the Eddystone device',
-          type: 'integer',
-          readOnly: false,
-          forms: [
-            {
-              op: 'readproperty',
-              href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87502-8ed3-4bdf-8a39-a01bebede295/readEddystoneProperty',
-              'wbt:id': webBluetoothId,
-            },
-            {
-              op: 'writeproperty',
-              href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87502-8ed3-4bdf-8a39-a01bebede295/writeEddystoneProperty',
-              'wbt:id': webBluetoothId,
-            },
-          ],
-        },
-        advertisedTxPower: {
-          title: 'Advertised Tx Power',
-          description: 'The advertised TX power of the iBeacon',
-          unit: 'dBm',
-          type: 'integer',
-          readOnly: false,
-          forms: [
-            {
-              op: 'readproperty',
-              href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87505-8ed3-4bdf-8a39-a01bebede295/readEddystoneProperty',
-              'wbt:id': webBluetoothId,
-            },
-            {
-              op: 'writeproperty',
-              href: 'gatt://a3c87500-8ed3-4bdf-8a39-a01bebede295/a3c87505-8ed3-4bdf-8a39-a01bebede295/writeEddystoneProperty',
-              'wbt:id': webBluetoothId,
-            },
-          ],
-        },
-        advertisedData: {
-          title: 'Advertised Data',
[…]

### 2022-04-08 src/things/huskyDuino/HuskyDuino.ts

@@ -1,80 +1,0 @@
-import * as WoT from 'wot-typescript-definitions';
-import {getWot} from '../index.js';
-
-export default class HuskyDuino {
-  public thing: WoT.ConsumedThing | null = null;
-
-  async init(webBluetoothId: string) {
-    const td: WoT.ThingDescription = {
-      '@context': ['https://www.w3.org/2019/wot/td/v1'],
-      '@type': ['Thing'],
-      id: 'blast:bluetooth:HuskyDuino',
-      title: 'HuskyDuino',
-      description: 'A HuskyLens interface running on Arduino',
-      securityDefinitions: {
-        nosec_sc: {
-          scheme: 'nosec',
-        },
-      },
-      security: 'nosec_sc',
-      properties: {
-        algorithm: {
-          description: 'The currently active algorithm',
-          type: 'number',
-          readOnly: false,
-          writeOnly: false,
-          forms: [
-            {
-              op: 'readproperty',
-              href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35d26-f9b0-11eb-9a03-0242ac130003/writeWithoutResponse',
-              'wbt:id': webBluetoothId,
-            },
-            {
-              op: 'writeproperty',
-              href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35d26-f9b0-11eb-9a03-0242ac130003/readNumber',
-              'wbt:id': webBluetoothId,
-            },
-          ],
-        },
-        id: {
-          description: 'The ID of the face or object',
-          type: 'number',
-          readOnly: false,
-          writeOnly: false,
-          forms: [
-            {
-              op: 'readproperty',
-              href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35eca-f9b0-11eb-9a03-0242ac130003/writeWithoutResponse',
-              'wbt:id': webBluetoothId,
-            },
-            {
-              op: 'writeproperty',
-              href: 'gatt://5be35d20-f9b0-11eb-9a03-0242ac130003/5be35eca-f9b0-11eb-9a03-0242ac130003/readText',
-              'wbt:id': webBluetoothId,
-            },
-          ],
-        },
-      },
-      actions: {
-        forgetAll: {
-          title: 'Forget all faces and objects',
-          description: 'Forget all faces and objects',
-          input: {
-            type: 'null',
-          },
-          forms: [
-            {
[…]

### 2022-04-13 demo-eswc22/paper/paper.tex
add examples for use cases

@@
 The functionality to issue HTTP requests is based on the Fetch API\footnote{\url{https://fetch.spec.whatwg.org/}}, Social Linked Data (Solid) authentication is based on the Inrupt client libraries\footnote{\url{https://docs.inrupt.com/developer-tools/javascript/client-libraries/}}, and SPARQL query support is based on µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
-Next to the presented small scenario around geofences, we have also developed BLAST programs to accomplish five use cases\footnote{TODO: URI to videos} with varying complexity.
+Next to the presented small scenario around geofences, we have developed BLAST programs to accomplish five use cases with varying complexity.
+These use cases include switching on a light, temperature monitoring, and movement detection.
 Each use case introduces a different challenge that requires the use of programming patterns in combination with the built-in blocks for properties, actions, events, requests, and queries.

### 2022-04-13 dist/thingBlocks/solid/blocks.js
fix upload_image block not being displayed

@@ -7,7 +7,7 @@
 'use strict';
 
 import {Blocks} from 'blockly';
-import {addBlock} from './../../../src/blast_toolbox.js';
+import {addBlock} from './../../blast_toolbox.js';
 
 Blocks['upload_image'] = {
   /**

### 2022-04-18 dist/blocks/control_flow.js
clean up control flow blocks, change conditional_statement colour

@@ -14,6 +14,7 @@ Blockly.Blocks['repeat'] = Blockly.Blocks['controls_repeat_ext'];
 Blockly.Blocks['for'] = Blockly.Blocks['controls_for'];
 Blockly.Blocks['while_until'] = Blockly.Blocks['controls_whileUntil'];
 Blockly.Blocks['break_continue'] = Blockly.Blocks['controls_flow_statements'];
+Blockly.Blocks['conditional_statement'] = Blockly.Blocks['controls_if'];
 
 // add changed names to Loops constant to ensure correct execution.
 Blockly.blocks.all.loops.loopTypes.add('repeat');
@@ -56,250 +57,6 @@ const FOR_XML = `
 // Add for block to the toolbox.
 addBlock('for', 'Control Flow', FOR_XML);
 
-Blockly.Blocks['conditional_statement'] = {
-  /**
-   * Block representing a conditional statement.
-   * @this {Blockly.Block}
-   */
-  init: function () {
-    this.appendValueInput('IF0')
-      .appendField('%{BKY_CONTROLS_IF_MSG_IF}')
-      .setCheck('Boolean');
-    this.appendStatementInput('DO0').appendField('%{BKY_CONTROLS_IF_MSG_THEN}');
-    this.setPreviousStatement(true, null);
-    this.setNextStatement(true, null);
-    this.setHelpUrl('%{BKY_CONTROLS_IF_HELPURL}');
-    this.setColour(120);
-    this.setMutator(
-      new Blockly.Mutator(['controls_if_elseif', 'controls_if_else'])
-    );
-    this.setTooltip(() => {
-      if (!this.elseifCount_ && !this.elseCount_) {
-        return Blockly.Msg['CONTROLS_IF_TOOLTIP_1'];
-      } else if (!this.elseifCount_ && this.elseCount_) {
-        return Blockly.Msg['CONTROLS_IF_TOOLTIP_2'];
-      } else if (this.elseifCount_ && !this.elseCount_) {
-        return Blockly.Msg['CONTROLS_IF_TOOLTIP_3'];
-      } else if (this.elseifCount_ && this.elseCount_) {
-        return Blockly.Msg['CONTROLS_IF_TOOLTIP_4'];
-      }
-      return '';
-    });
-  },
-
-  elseifCount_: 0,
-  elseCount_: 0,
-
-  /**
-   * Don't automatically add STATEMENT_PREFIX and STATEMENT_SUFFIX to generated
[…]

### 2022-04-18 demo-eswc22/paper/paper.tex

@@
 
-In the following we first introduce the BLAST language using a geofencing scenario, next describe the browser-based editor and execution environment for BLAST programs and then conclude.
+In the following we first introduce the BLAST language using a geofencing scenario, next describe the browser-based editor and execution environment for BLAST programs, followed by a short usability evaluation, and then conclude.
 
@@
 The custom blocks and the BLAST environment follow almost all of the design principles introduced by Fraser \cite{fraser}, such as a clear border style or the avoidance of transitive connections.
-Not implemented, however, are the varying color choices for different loops.
+Not implemented, however, are the varying color choices for different loop types.
 
@@
 According to Assila et al.
-\cite{assila2016standardized}, SUS provides reliable results over different sample sizes and converges fast to the correct conclusion.
+\cite{assila2016standardized}, SUS provides reliable results for  different sample sizes and converges quickly to the correct conclusion.
 
@@
 None of the participants had background knowledge regarding the Web of Things, RDF, or SPARQL.
-Participants were first asked to solve four tasks using BLAST, these included a simple ``Hello World!'' program, periodic polling of RSSI data by using a loop, reading data from a connected IoT device, and as a final task, reading data and processing it using logical operators.
-After the successful completion of these tasks, the participants filled out the SUS questionnaires.
-The achieved SUS score across all questionnaires is 81.4 out of 100 possible points, which corresponds to good usability.
+Participants were asked to solve four tasks using BLAST, these included a simple ``Hello World!'' program, periodic polling of RSSI data by using a loop, reading data from a connected IoT device, and as a final task, reading data and processing it using logical operators.
+After the completion of these tasks, the participants filled out the SUS questionnaire.
+The achieved SUS score across all questionnaires is 81.4 out of 100  points, which corresponds to good usability.
 
-It should be noted that the survey was conducted with an older version of BLAST. However, the user interface has changed only minimally since then, which is why the results are still relevant.
+It must be noted that the survey was conducted with an older version of BLAST.
+This is due to the fact that BLAST is under constant development.
+Since the user interface has undergone only minor changes since the evaluation, the results are still relevant.
 

### 2022-04-18 examples/web/src/index.js
update Blockly to 8.0.0, closes #139

@@ -79,8 +79,10 @@ const init = function () {
     };
     menuOptions.push(screenshotOption);
 
+    console.log(Blockly.ContextMenu.workspaceCommentOption(workspace, e));
+
     // // Adds a default-sized workspace comment to the workspace.
-    // menuOptions.push(Blockly.ContextMenu.workspaceCommentOption(workspace, e));
+    menuOptions.push(Blockly.ContextMenu.workspaceCommentOption(workspace, e));
   }
 
   initInterpreter(workspace);

### 2022-04-18 examples/web/sw.js

@@ -25,7 +25,7 @@ registerRoute(
     new CacheFirst(),
 );
 
-precacheAndRoute([{"revision":"c818dccbf511504d84d0fefdb0dc2873","url":"src/blocks.js"},{"revision":"2d92f1d9567e48bbafea96b00334da30","url":"src/generators.js"},{"revision":"73368e7cc96d0887f89d2a7171c5e76c","url":"src/index.js"},{"revision":"3e07a041289aa1782c5f26fe22a87dcc","url":"src/screenshot.js"},{"revision":"91fd40a68b979b9e053f8f921094a2f7","url":"src/web.js"}]);
+precacheAndRoute([{"revision":"c818dccbf511504d84d0fefdb0dc2873","url":"src/blocks.js"},{"revision":"2d92f1d9567e48bbafea96b00334da30","url":"src/generators.js"},{"revision":"55b1a46092792848e7b3e93a5893c45c","url":"src/index.js"},{"revision":"3e07a041289aa1782c5f26fe22a87dcc","url":"src/screenshot.js"},{"revision":"91fd40a68b979b9e053f8f921094a2f7","url":"src/web.js"}]);
 
 // Cache CSS, JS, and Web Worker requests with a Stale While Revalidate strategy
 registerRoute(

### 2022-04-18 src/blocks/control_flow.js

@@ -7,19 +7,19 @@
 'use strict';
 
 import {addBlock} from './../blast_toolbox.js';
-import Blockly from 'blockly';
+import {Blocks, libraryBlocks} from 'blockly';
 
 // Remap blockly blocks to improve naming in xml.
-Blockly.Blocks['repeat'] = Blockly.Blocks['controls_repeat_ext'];
-Blockly.Blocks['for'] = Blockly.Blocks['controls_for'];
-Blockly.Blocks['while_until'] = Blockly.Blocks['controls_whileUntil'];
-Blockly.Blocks['break_continue'] = Blockly.Blocks['controls_flow_statements'];
-Blockly.Blocks['conditional_statement'] = Blockly.Blocks['controls_if'];
+Blocks['repeat'] = Blocks['controls_repeat_ext'];
+Blocks['for'] = Blocks['controls_for'];
+Blocks['while_until'] = Blocks['controls_whileUntil'];
+Blocks['break_continue'] = Blocks['controls_flow_statements'];
+Blocks['conditional_statement'] = Blocks['controls_if'];
 
 // add changed names to Loops constant to ensure correct execution.
-Blockly.blocks.all.loops.loopTypes.add('repeat');
-Blockly.blocks.all.loops.loopTypes.add('while_until');
-Blockly.blocks.all.loops.loopTypes.add('for');
+libraryBlocks.loops.loopTypes.add('repeat');
+libraryBlocks.loops.loopTypes.add('while_until');
+libraryBlocks.loops.loopTypes.add('for');
 
 // Define inner block XML for the repeat block.
 const REPEAT_XML = `
@@ -57,7 +57,7 @@ const FOR_XML = `
 // Add for block to the toolbox.
 addBlock('for', 'Control Flow', FOR_XML);
 
-Blockly.Blocks['wait_seconds'] = {
+Blocks['wait_seconds'] = {
   /**
    * Block for executing a sleep/timeout command.
    * @this {Blockly.Block}

### 2023-01-13 packages/core/src/wot/index.ts
Add basic security

@@ -12,7 +12,7 @@ let wot: typeof WoT;
 
 declare const Wot: any;
 
-const getServient = function (bluetoothAdapter: BluetoothAdapter): Servient {
+export const getServient = function (bluetoothAdapter: BluetoothAdapter): Servient {
   const httpConfig = {
     allowSelfSigned: true, // client configuration
   };

### 2023-01-13 packages/web/src/assets/js/things.js

@@ -608,6 +608,19 @@ export const addDevice = function (deviceName, deviceId, type) {
     }
     generateThingCode(deviceName);
 
+    // Supported is only none_sc and basic_sc
+    if (td.security === 'basic_sc') {
+      //TODO: generate basic sc block
+      td.id = td.id ?? deviceId;
+      generateSecurityBlock(deviceName, td);
+      generateSecurityCode(deviceName, td);
+
+      // Add to implementedThingsBlockList
+      implementedThingsBlockList.push({
+        type: `${deviceName}_SecurityBlock`,
+        category: 'Security',
+      });
+    }
     // get property names
     for (const [propertyName, _] of Object.entries(td.properties ?? {})) {
       propertiesObj[propertyName] = [];
@@ -771,7 +784,11 @@ function generateThingBlock(deviceName, deviceDescription, td) {
 
   // Generate description depending on available information
   let description = '';
-  description += td.descriptions[langTag] ?? td.description;
+  if (td.descriptions !== undefined) {
+    description += td.descriptions[langTag] ?? deviceDescription;
+  } else {
+    description += deviceDescription;
+  }
   if (td.version !== undefined) {
     description += ` | version: ${td.version}`;
   }
@@ -902,7 +919,7 @@ function generateReadPropertyBlock(propertyName, deviceName) {
           'label'
         );
       this.setOutput(true, null);
-      this.setColour(230);
+      this.setColour(255);
       this.setTooltip(`Read the ${propertyName} property of a ${deviceName}`);
       this.setHelpUrl('');
     },
@@ -1007,7 +1024,8 @@ function generateInvokeActionBlock(actionName, deviceName, input, output) {
         inputValueType = 'Array';
         break;
       case 'object':
-        throwError('Objects are currently not supportet');
+        //throwError('Objects are currently not supportet');
+        console.log('Objects are currently not supportet');
         break;
       default:
         inputValueType = null;
@@ -1027,7 +1045,7 @@ function generateInvokeActionBlock(actionName, deviceName, input, output) {
         this.setInputsInline(true);
         this.setPreviousStatement(true, null);
         this.setNextStatement(true, null);
-        this.setColour(255);
+        this.setColour(0);
         this.setTooltip(`Invoke the ${actionName} action of a ${deviceName}`);
         this.setHelpUrl('');
       },
[…]

### 2023-01-13 packages/web/src/assets/js/toolbox.js

@@ -49,6 +49,17 @@ const defaultToolbox = {
       colour: '180',
     },
     {
+      kind: 'CATEGORY',
+      contents: [
+        {
+          kind: 'label',
+          text: '(Connect things to see device dependent blocks)',
+        },
+      ],
+      name: 'Security',
+      colour: '40',
+    },
+    {
       kind: 'sep',
       gap: '32',
     },

### 2023-01-13 docs/evaluation march 2021/main.tex
added exercises sheet from praxistag march 2021

\documentclass[12pt,twoside,a4paper]{article}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{array,tabularx}
\usepackage[a4paper,left=3cm,right=2cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{authblk}

\setlist[enumerate,1]{labelindent=0pt, leftmargin=*}
\pagestyle{empty}

\newcolumntype{P}{>{\centering\arraybackslash}p{0.75cm}}
\newcolumntype{L}{>{\raggedright\arraybackslash}m{0.2\textwidth}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}m{0.2\textwidth}}

\newcommand{\usetbl}{%
  \begin{tabular}{@{}|*5{P|}@{}}
    \hline
    1 & 2 & 3 & 4 & 5 \\
    \hline
  \end{tabular}
}

\newcommand\prop[1]{%
  \item
  \parbox[t]{0.5\textwidth}{#1}%
  \qquad
  \parbox[t]{0.5\textwidth}{\usetbl}%
}

\graphicspath{{images/}}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    citecolor=black,
}

\title{BLAST: Hands-On Workshop}
\author[1]{Wehr, Thomas}
\author[2]{Fleiner, Christian}
\affil[1]{Supply-Chain-Services (SCS), Fraunhofer IIS}
\affil[2]{Chair of Technical Information Systems, FAU Erlangen-Nürnberg}
\date{June 15, 2021}

\renewcommand\Authands{ and }

\begin{document}

\maketitle

\section{Prerequisites}
Open BLAST (\href{https://paul.ti.rw.fau.de/~qa60fyri/campus/blast/}{https://paul.ti.rw.fau.de/~qa60fyri/campus/blast/}) in your favorite Browser.

\noindent BLAST is a visual programming environment used to create IoT-Applications by arranging blocks.

\begin{center}
  \includegraphics[width=\textwidth]{screenshot.png}
\end{center}

\section{Introductory exercises}
Solve the following exercises using the blocks provided by BLAST.
\subsection{Hello World!}
Create and execute a block-program displaying the message ``Hello, world!''.

Hint: You need the \textbf{display text} block to display messages and a \textbf{string} block to define a text.

\subsection{Variables}\label{sub:variables}
Create and execute a block-program, that successively displays the messages ``Hello, 1'', ``Hello, 2'' and ``Hello, 3''. Use a variable for the number.

Hint: Use arithmetic operations from the \textbf{Numbers} category to increment the variable.

\subsection{Loops}\label{sub:loops}
Extent the program of ~\ref{sub:variables}, but display messages for the numbers 1 to 10 and use only 1 \textbf{display text} block by adding a block from the \textbf{Control Flow} category.

\subsection{If clauses}
Skip each even number in the output of ~\ref{sub:loops} by using an \textbf{if} block.

Hint: The \href{https://en.wikipedia.org/wiki/Modulo_operation}{modulo operation}(\%) can be used to determine even numbers.

\end{document}
